### 2018-05-19 doc/ms.tex
A place to write

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{natbib}

\newcommand{\bell}{\boldsymbol{\ell}}
\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\given}{\,|\,}

\title{TwinPeaks2018}
\author{Brendon J. Brewer}
%\date{}

\begin{document}
\maketitle

%\abstract{\noindent Abstract}

% Need this after the abstract
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

The prior is $\pi(\btheta)$ and the scalars are
$\left\{ f_i(\btheta) \right\}$
for $i \in \{1, 2, ..., M\}$. In most examples $M$ will be 2.
Consider a family of thresholded distributions, indexed by threshold
values $\bell=\left\{\ell_i\right\}$, proportional to
\begin{align}
p(\btheta; \bell) &\propto
    \pi(\btheta)
    \prod_{i=1}^M \mathds{1}\left(f_i(\btheta) > \ell_i\right).
\end{align}
The normalising constant is the probability in the `upper right corner'
(in 2D):
\begin{align}
X(\bell) &= \int_{f_i(\btheta) > \ell_i, \forall_i} \pi(\btheta) \, d\btheta
\end{align}

\end{document}

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Save particle to disk

@@ -6,12 +6,69 @@
 
 {-# LANGUAGE RecordWildCards #-}
 
-module TwinPeaks2018.Algorithm where
+module TwinPeaks2018.Algorithm (update) where
 
 -- Imports
+import Control.Monad
+import Control.Monad.Primitive
+import qualified Data.Text.IO as TIO
 import qualified Data.Vector as V
+import System.IO
+import System.Random.MWC
+import TwinPeaks2018.Model
 import TwinPeaks2018.Sampler
+import TwinPeaks2018.Utils
 
 -- Find the index of the worst particle
 findWorst :: SamplerState a -> Int
 findWorst SamplerState {..} = V.maxIndex nsParticleUccs
+
+
+
+
+
+-- One iteration of Nested Sampling
+update :: SamplerState a
+       -> Gen RealWorld
+       -> IO (SamplerState a)
+update sampler@SamplerState {..} rng = do
+
+    -- Update iteration number, print message
+    let iteration' = iteration + 1
+    putStrLn $ "Iteration " ++ show iteration' ++ "..."
+    hFlush stdout
+
+    -- Which particle to kill
+    let iKill = findWorst sampler
+    let  kill = particles nsParticles V.! iKill
+
+    -- Open the output file
+    h <- openFile "output/output.csv" $ if iteration==0
+                                        then WriteMode
+                                        else AppendMode
+    -- Write CSV header
+    when (iteration == 0) $ TIO.hPutStrLn h (header theModel)
+
+    -- Write that particle to disk
+    saveParticle kill theModel h
+    saveParticle kill theModel h
+
+
+    -- Choose copy to replace it with
+    copy <- chooseCopy iKill numParticles rng
+
+    -- Close output file
+    hClose h
+    putStrLn "done.\n"
+
+    return $! sampler
+
+
+
+-- Write a particle to disk
+saveParticle :: a
+             -> Model a
+             -> Handle
+             -> IO ()
+saveParticle particle Model {..} h = TIO.hPutStrLn h $ render particle
+

### 2018-05-23 haskell/lib/TwinPeaks2018/Model.hs

@@ -27,7 +27,7 @@ data Model a = Model
                    render    :: !(a -> T.Text),
 
                    -- Header for CSV output
-                   header    :: !(T.Text)
+                   header    :: !T.Text
                }
 
 

### 2018-05-23 haskell/lib/TwinPeaks2018/Sampler.hs

@@ -5,6 +5,7 @@
 {-# LANGUAGE RecordWildCards #-}
 
 module TwinPeaks2018.Sampler (generateSampler,
+                              particles,
                               samplerStateToText,
                               SamplerState(..)) where
 
@@ -35,6 +36,9 @@ data Particles a = Particles
 -- with two collections of particles
 data SamplerState a = SamplerState
                       {
+                          theModel        :: !(Model a),
+                          iteration       :: !Int,
+                          numParticles    :: !Int,
                           nsParticles     :: !(Particles a),
                           shadowParticles :: !(Particles a),
                           nsParticleUccs  :: !(V.Vector Scalar)
@@ -76,11 +80,14 @@ generateSampler numParticles Model {..} rng
     | otherwise         = lift $ do
 
         -- Create and print message
-        let message = "Generating initial sampler state\nwith "
+        putStrLn "Generating initial sampler state..."
+        putStr $ "    Generating "
                          ++ show numParticles ++ " NS particles and "
                          ++ show numParticles ++ " shadow particles..."
-        putStr message
         hFlush stdout
+
+        let iteration = 0
+        let theModel = Model {..}
 
         nsParticles     <- generateParticles numParticles Model {..} rng
         shadowParticles <- generateParticles numParticles Model {..} rng
@@ -94,6 +101,7 @@ generateSampler numParticles Model {..} rng
         let nsParticleUccs = V.zip rawUccs tieBreakers
 
         putStrLn "done."
+        putStrLn "done.\n"
         return $! SamplerState {..}
 
 

### 2018-05-23 haskell/src/Main.hs

@@ -2,8 +2,8 @@ module Main where
 
 -- Imports
 import Control.Monad.Trans.Maybe
-import qualified Data.Text.IO as TIO
 import System.Random.MWC
+import TwinPeaks2018.Algorithm
 import TwinPeaks2018.Sampler
 import TwinPeaks2018.Model
 
@@ -17,6 +17,8 @@ main = withSystemRandom . asGenIO $ \rng -> do
     -- If it succeeded, print particle scalars
     case maybeSampler of
         Nothing -> putStrLn "Error creating sampler."
-        Just s  -> TIO.putStrLn $ samplerStateToText s
+        Just s  -> do
+                     _ <- update s rng
+                     return ()
     return ()
 

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Working on it

@@ -13,6 +13,7 @@ import Control.Monad
 import Control.Monad.Primitive
 import qualified Data.Text.IO as TIO
 import qualified Data.Vector as V
+import qualified Data.Vector.Mutable as VM
 import System.IO
 import System.Random.MWC
 import TwinPeaks2018.Model
@@ -22,10 +23,6 @@ import TwinPeaks2018.Utils
 -- Find the index of the worst particle
 findWorst :: SamplerState a -> Int
 findWorst SamplerState {..} = V.maxIndex nsParticleUccs
-
-
-
-
 
 -- One iteration of Nested Sampling
 update :: SamplerState a
@@ -51,11 +48,12 @@ update sampler@SamplerState {..} rng = do
 
     -- Write that particle to disk
     saveParticle kill theModel h
-    saveParticle kill theModel h
-
 
     -- Choose copy to replace it with
     copy <- chooseCopy iKill numParticles rng
+
+    -- Generate replacement particle
+    replacement <- refresh nsparticles rng
 
     -- Close output file
     hClose h

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Restructured particle type

@@ -37,7 +37,7 @@ update sampler@SamplerState {..} rng = do
 
     -- Which particle to kill
     let iKill = findWorst sampler
-    let  kill = particles nsParticles V.! iKill
+    let  kill = nsParticles V.! iKill
 
     -- Open the output file
     h <- openFile "output/output.csv" $ if iteration==0
@@ -53,7 +53,7 @@ update sampler@SamplerState {..} rng = do
     copy <- chooseCopy iKill numParticles rng
 
     -- Generate replacement particle
-    replacement <- refresh nsparticles rng
+--    replacement <- refresh nsparticles rng
 
     -- Close output file
     hClose h
@@ -64,9 +64,9 @@ update sampler@SamplerState {..} rng = do
 
 
 -- Write a particle to disk
-saveParticle :: a
+saveParticle :: Particle a
              -> Model a
              -> Handle
              -> IO ()
-saveParticle particle Model {..} h = TIO.hPutStrLn h $ render particle
+saveParticle Particle {..} Model {..} h = TIO.hPutStrLn h $ render coords
 

### 2018-05-23 haskell/lib/TwinPeaks2018/Sampler.hs

@@ -5,8 +5,8 @@
 {-# LANGUAGE RecordWildCards #-}
 
 module TwinPeaks2018.Sampler (generateSampler,
-                              particles,
                               samplerStateToText,
+                              Particle(..),
                               SamplerState(..)) where
 
 -- Imports
@@ -23,14 +23,16 @@ import TwinPeaks2018.Scalar
 
 -- TYPES ------------------------
 
--- Represents a collection of particles and their metadata
-data Particles a = Particles
-                   {
-                       particles :: !(V.Vector a),
-                       fs        :: !(V.Vector Scalar),
-                       gs        :: !(V.Vector Scalar)
-                   }
+-- Represents a single particle and its metadata
+data Particle a = Particle
+                  {
+                      coords :: !a,
+                      fValue :: !Scalar,
+                      gValue :: !Scalar
+                  }
 
+-- A collection of particles
+type Particles a = V.Vector (Particle a)
 
 -- Represents the state of the sampler,
 -- with two collections of particles
@@ -47,27 +49,62 @@ data SamplerState a = SamplerState
 
 -- FUNCTIONS AND ACTIONS ---------------------------
 
+-- Extraction of scalars from a collection of particles
+getFValues :: Particles a
+           -> V.Vector Scalar
+getFValues = V.map (\(Particle _ f _ ) -> f)
+
+getGValues :: Particles a
+           -> V.Vector Scalar
+getGValues = V.map (\(Particle _ _ g ) -> g)
+
+
 -- Generate a bunch of particles from the prior
 generateParticles :: Int
                   -> Model a
                   -> Gen RealWorld
                   -> IO (Particles a)
-generateParticles numParticles Model {..} rng = do
+generateParticles num Model {..} rng = do
 
-    -- Generate the particles and evaluate the scalars
-    particles <- V.replicateM numParticles (fromPrior rng)
-    let fEvals = V.map f particles
-    let gEvals = V.map g particles
+    -- Generate the coordinates and evaluate the scalars
+    coords <- V.replicateM num (fromPrior rng)
+    let fEvals = V.map f coords
+    let gEvals = V.map g coords
 
     -- Need tiebreakers to pair with the scalars
-    us1 <- V.replicateM numParticles (uniform rng :: IO Double)
[…]

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Preparing for MCMC

@@ -4,6 +4,7 @@
     that update a SamplerState, and so on.
 -}
 
+{-# LANGUAGE BangPatterns #-}
 {-# LANGUAGE RecordWildCards #-}
 
 module TwinPeaks2018.Algorithm (update) where
@@ -50,10 +51,11 @@ update sampler@SamplerState {..} rng = do
     saveParticle kill theModel h
 
     -- Choose copy to replace it with
-    copy <- chooseCopy iKill numParticles rng
+    iCopy <- chooseCopy iKill numParticles rng
 
     -- Generate replacement particle
---    replacement <- refresh nsparticles rng
+    replacement <- refresh 1000 (nsParticles V.! iCopy)
+                                theModel rng
 
     -- Close output file
     hClose h
@@ -69,4 +71,16 @@ saveParticle :: Particle a
              -> Handle
              -> IO ()
 saveParticle Particle {..} Model {..} h = TIO.hPutStrLn h $ render coords
+
+
+-- Refresh a particle
+refresh :: Int
+        -> Particle a
+        -> Model a
+        -> Gen RealWorld
+        -> IO (Particle a)
+refresh steps !particle theModel rng
+    | steps == 0 = return particle
+    | otherwise  = do
+                     refresh (steps-1) particle theModel rng
 

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Metropolis runs

@@ -14,7 +14,7 @@ import Control.Monad
 import Control.Monad.Primitive
 import qualified Data.Text.IO as TIO
 import qualified Data.Vector as V
-import qualified Data.Vector.Mutable as VM
+--import qualified Data.Vector.Mutable as VM
 import System.IO
 import System.Random.MWC
 import TwinPeaks2018.Model
@@ -54,8 +54,10 @@ update sampler@SamplerState {..} rng = do
     iCopy <- chooseCopy iKill numParticles rng
 
     -- Generate replacement particle
-    replacement <- refresh 1000 (nsParticles V.! iCopy)
-                                theModel rng
+    putStr "    Doing MCMC..."
+    hFlush stdout
+    replacement <- refresh 10000 iKill (nsParticles V.! iCopy) sampler rng
+    putStrLn "done."
 
     -- Close output file
     hClose h
@@ -73,14 +75,48 @@ saveParticle :: Particle a
 saveParticle Particle {..} Model {..} h = TIO.hPutStrLn h $ render coords
 
 
--- Refresh a particle
+-- Refresh a particle using 'steps' metropolis steps
 refresh :: Int
+        -> Int
         -> Particle a
-        -> Model a
+        -> SamplerState a
         -> Gen RealWorld
         -> IO (Particle a)
-refresh steps !particle theModel rng
+refresh steps iKill !particle@(Particle coords fValue gValue uccTb)
+        SamplerState {..} rng
     | steps == 0 = return particle
     | otherwise  = do
-                     refresh (steps-1) particle theModel rng
+                     -- Single ' denotes proposed
+                     -- Double '' denotes actual new state
+                     (coords', logH) <- perturb theModel coords rng
+                     u <- uniform rng :: IO Double
+                     if u >= exp logH then return particle -- Pre-reject
+                     else do
+                            -- Getter for the UCC tiebreaker of a particle
+                            let getUccTiebreaker (Particle _ _ _ t) = t
+
+                            -- Tiebreaker proposals
+                            tbf' <- trivialExampleWrap . (snd fValue + )
+                                                    <$> randh rng
+                            tbg' <- trivialExampleWrap . (snd gValue + )
+                                                    <$> randh rng
+                            tbucc' <- trivialExampleWrap . (uccTb + )
+                                                    <$> randh rng
+                            let fValue' = (f theModel coords', tbf')
+                            let gValue' = (g theModel coords', tbg')
+                            let ucc' = particleUcc
[…]

### 2018-05-23 haskell/lib/TwinPeaks2018/Sampler.hs

@@ -7,6 +7,7 @@
 module TwinPeaks2018.Sampler (generateSampler,
                               samplerStateToText,
                               Particle(..),
+                              particleUcc,
                               SamplerState(..)) where
 
 -- Imports
@@ -28,7 +29,8 @@ data Particle a = Particle
                   {
                       coords :: !a,
                       fValue :: !Scalar,
-                      gValue :: !Scalar
+                      gValue :: !Scalar,
+                      uccTiebreaker :: !Double
                   }
 
 -- A collection of particles
@@ -43,7 +45,7 @@ data SamplerState a = SamplerState
                           numParticles    :: !Int,
                           nsParticles     :: !(Particles a),
                           shadowParticles :: !(Particles a),
-                          nsParticleUccs  :: !(V.Vector Scalar)
+                          nsParticleUccs  :: !(V.Vector Int)
                       }
 
 
@@ -52,11 +54,11 @@ data SamplerState a = SamplerState
 -- Extraction of scalars from a collection of particles
 getFValues :: Particles a
            -> V.Vector Scalar
-getFValues = V.map (\(Particle _ f _ ) -> f)
+getFValues = V.map (\(Particle _ f _ _) -> f)
 
 getGValues :: Particles a
            -> V.Vector Scalar
-getGValues = V.map (\(Particle _ _ g ) -> g)
+getGValues = V.map (\(Particle _ _ g _) -> g)
 
 
 -- Generate a bunch of particles from the prior
@@ -71,16 +73,17 @@ generateParticles num Model {..} rng = do
     let fEvals = V.map f coords
     let gEvals = V.map g coords
 
-    -- Need tiebreakers to pair with the scalars
+    -- Need tiebreakers to pair with the scalars and the UCCs
     us1 <- V.replicateM num (uniform rng :: IO Double)
     us2 <- V.replicateM num (uniform rng :: IO Double)
+    tbs <- V.replicateM num (uniform rng :: IO Double)
 
     -- Do the pairing
     let fs = V.zip fEvals us1
     let gs = V.zip gEvals us2
 
-    return $! V.zipWith3 (\c fVal gVal -> Particle c fVal gVal)
-                         coords fs gs
+    return $! V.zipWith4 (\c fVal gVal tb -> Particle c fVal gVal tb)
+              coords fs gs tbs
 
 
 
@@ -88,7 +91,7 @@ generateParticles num Model {..} rng = do
[…]

### 2018-05-23 haskell/lib/TwinPeaks2018/Algorithm.hs
Runs but seems broken

@@ -7,14 +7,14 @@
 {-# LANGUAGE BangPatterns #-}
 {-# LANGUAGE RecordWildCards #-}
 
-module TwinPeaks2018.Algorithm (update) where
+module TwinPeaks2018.Algorithm (nestedSampling) where
 
 -- Imports
 import Control.Monad
 import Control.Monad.Primitive
 import qualified Data.Text.IO as TIO
 import qualified Data.Vector as V
---import qualified Data.Vector.Mutable as VM
+import qualified Data.Vector.Mutable as VM
 import System.IO
 import System.Random.MWC
 import TwinPeaks2018.Model
@@ -24,6 +24,13 @@ import TwinPeaks2018.Utils
 -- Find the index of the worst particle
 findWorst :: SamplerState a -> Int
 findWorst SamplerState {..} = V.maxIndex nsParticleUccs
+
+nestedSampling :: Int -> SamplerState a -> Gen RealWorld -> IO (SamplerState a)
+nestedSampling steps sampler rng
+    | steps == 0 = return sampler
+    | otherwise  = do
+                       sampler' <- update sampler rng
+                       nestedSampling (steps-1) sampler' rng
 
 -- One iteration of Nested Sampling
 update :: SamplerState a
@@ -59,11 +66,26 @@ update sampler@SamplerState {..} rng = do
     replacement <- refresh 10000 iKill (nsParticles V.! iCopy) sampler rng
     putStrLn "done."
 
+    -- Do the replacement
+    mvec <- V.unsafeThaw nsParticles
+    _ <- VM.write mvec iKill replacement
+    nsParticles' <- V.unsafeFreeze mvec
+
+    -- Do replacement of Particle UCC
+    mvec2 <- V.unsafeThaw nsParticleUccs
+    let uccOf (Particle _ f g _) = particleUcc f g shadowParticles
+    _ <- VM.write mvec2 iKill $ uccOf replacement
+    nsParticleUccs' <- V.unsafeFreeze mvec2
+
+    -- Create new sampler
+    let sampler' = SamplerState theModel iteration' numParticles
+                                nsParticles' shadowParticles nsParticleUccs'
+
     -- Close output file
     hClose h
     putStrLn "done.\n"
 
-    return $! sampler
+    return $! sampler'
 
 
 

### 2018-05-23 haskell/src/Main.hs

@@ -1,6 +1,7 @@
 module Main where
 
 -- Imports
+import Control.Monad
 import Control.Monad.Trans.Maybe
 import System.Random.MWC
 import TwinPeaks2018.Algorithm
@@ -18,7 +19,7 @@ main = withSystemRandom . asGenIO $ \rng -> do
     case maybeSampler of
         Nothing -> putStrLn "Error creating sampler."
         Just s  -> do
-                     _ <- update s rng
+                     _ <- nestedSampling 2000 s rng
                      return ()
     return ()
 

### 2018-05-23 prototype/prototype.py
New prototype

@@ -1,79 +1,127 @@
 """
 A sandbox for testing ideas
 """
+import dnest4
 import matplotlib.pyplot as plt
 from numba import jit
 import numpy as np
 import numpy.random as rng
 
-def generate(n):
+class Sampler:
     """
-    Generate some initial particles.
+    The current state of a sampler.
     """
-    return { "xs": rng.rand(n), "ys": rng.rand(n),
-             "us": rng.rand(n) }
 
-@jit
-def compute_particle_uccs(particles):
-    """
-    Compute the non-integer UCCs.
-    """
-    uccs = np.empty(len(particles["xs"]), dtype="float64")
-    for i in range(len(particles["xs"])):
-        uccs[i] = compute_ucc(particles["xs"][i],
-                              particles["ys"][i],
-                              particles)
-    uccs += particles["us"]
-    return uccs
+    def __init__(self, num_particles=1000):
+        self.num_particles = num_particles
+
+    def from_prior(self):
+        self.particles = rng.rand(self.num_particles, 2)
+        self.tbs = rng.rand(self.num_particles)
+
+        self.shadow_particles = rng.rand(self.num_particles, 2)
+        self.shadow_tbs = rng.rand(self.num_particles)
+        self.calculate_uccs()
 
 
+    def calculate_ucc(self, x, y):
+        """
+        Calculate the UCC at the given position.
+        """
+        ucc = 0
+        for i in range(self.shadow_particles.shape[0]):
+            if (x < self.shadow_particles[i, 0]) &\
+               (y < self.shadow_particles[i, 1]):
+                ucc += 1
+        return ucc
 
-def compute_ucc(x, y, particles):
-    """
-    Compute the integer UCC at the given position
-    """
-    above = (particles["xs"] > x) & \
-            (particles["ys"] > y)
-    return np.sum(above)
+    def calculate_uccs(self):
+        self.uccs = np.empty(self.num_particles)
+        for i in range(self.num_particles):
+            self.uccs[i] = self.calculate_ucc(self.particles[i, 0],
+                                              self.particles[i, 1])
 
-@jit
-def ucc_grid(particles):
-    """
-    Evaluate integer UCC on a grid
-    """
-    # The grid
-    xx = np.linspace(0.0, 1.0, 201)
-    yy = np.linspace(0.0, 1.0, 201)
-    [xx, yy] = np.meshgrid(xx, yy[::-1])
+    def update(self):
 
-    # Compute uccs
[…]

### 2018-05-23 prototype/prototype.py
Looks pretty cool TBH

@@ -93,11 +93,13 @@ class Sampler:
             self.shadow_particles[i, :] = particle
             self.shadow_tbs[i] = tb
 
+        self.calculate_uccs()
+
         return result
 
     def explore(self, particle, tb, ucc, threshold):
 
-        for i in range(1000):
+        for i in range(100):
             proposal = particle.copy()
             proposal[0] = dnest4.wrap(proposal[0] + dnest4.randh(), 0.0, 1.0)
             proposal[1] = dnest4.wrap(proposal[1] + dnest4.randh(), 0.0, 1.0)
@@ -117,7 +119,7 @@ if __name__ == "__main__":
 
 #    plt.scatter(sampler.shadow_particles[:,0], sampler.shadow_particles[:,1],
 #                marker="o", color="k", alpha=0.2)
-    for i in range(0, 500):
+    for i in range(0, 1000):
         result = sampler.update()
         plt.scatter(result[0], result[1], marker=".", color="r", alpha=0.3)
         print(i+1)

### 2018-05-23 doc/ms.tex
Working on the doc

@@
 The prior is $\pi(\btheta)$ and the scalars are
-$\left\{ f_i(\btheta) \right\}$
-for $i \in \{1, 2, ..., M\}$. In most examples $M$ will be 2.
+$f(\btheta)$ and $g(\btheta)$. Letting $x=f(\btheta)$ and $y=g(\btheta)$,
+the implied prior for $x$ and $y$ will be written $\pi(x, y)$.
+
 Consider a family of thresholded distributions, indexed by threshold
-values $\bell=\left\{\ell_i\right\}$, proportional to
+values $(x^*, y^*)$, given by
 \begin{align}
-p(\btheta; \bell) &\propto
-    \pi(\btheta)
-    \prod_{i=1}^M \mathds{1}\left(f_i(\btheta) > \ell_i\right).
+p(x, y; x^*, y^*) &= \frac{\pi(x, y)\mathds{1}(x > x^*, y > y^*)}
+                          {X(x^*, y^*)}
 \end{align}
-The normalising constant is the probability in the `upper right corner'
-(in 2D):
+The normalising constant is the probability in the `upper right corner':
 \begin{align}
-X(\bell) &= \int_{f_i(\btheta) > \ell_i, \forall_i} \pi(\btheta) \, d\btheta
+X(x^*, y^*) &= \int_{y^*}^{\infty} \int_{x^*}^{\infty} \pi(x, y) \, dx \, dy.
+\end{align}
+
+The Kullback-Leibler divergence from the prior to a thresholded distribution
+is
+\begin{align}
+D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, \pi(x, y)\right) &=
+    \log X(x^*, y^*).
+\end{align}
+
+\section{Nested Sampling distribution}
+Consider the following distribution:
+\begin{align}
+p_{\rm NS}(x, y) &= \frac{\pi(x, y)}{C X(x, y)}.
+\end{align}
+Compared to the prior $\pi$, this puts more weight at high values of
+$x$ and $y$.
+
+The KL divergence from $p_{\rm NS}$ to $p(x, y ; x^*, y^*)$ is
+\begin{align}
+D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, p_{\rm NS}(x, y)\right)
+&=
+\int_{y^*}^{\infty} \int_{x^*}^{\infty}
+    \frac{\pi(x, y)}{X(x^*, y^*)}
+    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
+    \, dx \, dy \\
+&=
+\frac{1}{X(x^*, y^*)}
+\int_{y^*}^{\infty} \int_{x^*}^{\infty}
+    \pi(x, y)
+    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
+    \, dx \, dy \\
+&=
+\frac{\int_{y^*}^{\infty} \int_{x^*}^{\infty}
+     \pi(x, y)
+     \log \left[C X(x, y)\right]
+     \, dx \, dy - X(x^*, y^*)\log X(x^*, y^*)}
+     {X(x^*, y^*)}
 \end{align}

### 2018-05-23 doc/ms.tex
Do standard NS case

@@
 \section{Nested Sampling distribution}
+Consider the one-scalar situation (i.e., $f(x) \equiv$ log likelihood),
+which is the case in standard NS. The Nested Sampling distribution is
+\begin{align}
+p_{\rm NS}(x) &= \frac{\pi(x)}{C X(x)}.
+\end{align}
+This is the distribution that `stretches out' the prior (which is a
+reflected exponential for $\ln X$) into a uniform distribution for $\ln X$.
+\begin{align}
+p_{\rm NS}(x) &= \frac{\pi(x)}{C X(x)}.
+\end{align}
+
+The KL divergence from $p_{\rm NS}$ to a constrained distribution
+$p(x; x^*) = \pi(x)\mathds{1}(x > x^*)/X(x^*)$ is
+\begin{align}
+D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
+    &= \int p(x; x^*)
+            \log \left[\frac{p_{\rm NS}}{p_{\rm NS}}\right] \, dx \\
+    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
+            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
+                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
+    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
+            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
+                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
+    &= \log C + \int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
+            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx
+\end{align}
+
+Do a change of variables to make $X$ the integrand. Its prior is uniform
+because $X$ is a cumulative probability.
+
+\section{Nested Sampling distribution --- TwinPeaks case}
+
 Consider the following distribution:

### 2018-05-24 doc/ms.tex
The change of variables
Do it with differentiation

@@
     &= \log C + \int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
-            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx
+            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx.
 \end{align}
 
-Do a change of variables to make $X$ the integrand. Its prior is uniform
-because $X$ is a cumulative probability.
+Let's see how this varies as you change the thresholded distribution
+by varying $x^*$:
+\begin{align}
+\frac{d}{dx^*} D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
+    &= \frac{d}{dx^*} \log C +
+        \frac{d}{dx^*}\int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
+            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx \\
+    &= \frac{d}{dx^*}\int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
+            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx \\
+    &= \frac{\pi(x^*)}{X(x^*)}
+            \log \left[\frac{X(x^*)}{X(x^*)}\right] \, dx \\
+    &= 0.
+\end{align}
+That is, it doesn't change! The KL divergence
+{\em from the distribution actually sampled} to
+{\em any thresholded distribution} is the same!
 

### 2018-05-29 include/SwitchSamplerImpl.h
Only use completed reps

@@ -259,6 +259,13 @@ void SwitchSampler<T>::run_to_depth(double depth, RNG& rng)
     unsigned int iterations = depth*num_particles;
     for(unsigned int i=0; i<iterations; ++i)
         do_iteration(rng, i != (iterations-1));
+
+    files_mutex.lock();
+    std::fstream fout("output/completed_reps.txt",
+                                            std::ios::out | std::ios::app);
+    fout << id << std::endl;
+    fout.close();
+    files_mutex.unlock();
 }
 
 template<typename T>
@@ -321,6 +328,9 @@ void prepare_output_files()
     auto desc = T::description();
     if(desc.size() > 0)
         fout << desc << std::endl;
+    fout.close();
+
+    fout.open("output/completed_reps.txt", std::ios::out);
     fout.close();
 }
 

### 2018-05-29 python/canonical.py

@@ -9,10 +9,32 @@ import numpy.random as rng
 import pandas as pd
 from utils import logsumexp
 
-# Load and plot trajectories
-particles_info = pd.read_csv("../output/particles_info.csv")
 
-def plot_particle_scalars(scalars=[0, 1]):
+def load_particles_info(filename="../output/particles_info.csv"):
+    """
+    Load all the particles_info file, and return a data frame containing
+    only complete runs (unless there aren't any, in which case it just
+    returns whatever it's got).
+    """
+
+    particles_info = pd.read_csv(filename)
+
+    completed_reps = np.loadtxt("../output/completed_reps.txt")
+    if len(completed_reps) == 0:
+        print("There are no completed reps.")
+        return particles_info
+
+    print("Found {n} completed reps.".format(n=len(completed_reps)))
+
+    # Mark completed reps for keeping
+    keep = np.zeros(particles_info.shape[0], dtype="bool")
+    for r in completed_reps:
+        keep[particles_info["run_id"] == r] = True
+    indices = np.nonzero(keep)[0]
+    return particles_info.iloc[keep, :]
+
+
+def plot_particle_scalars(particles_info, scalars=[0, 1]):
     """
     Plot particle scalars
     """
@@ -39,24 +61,18 @@ def plot_particle_scalars(scalars=[0, 1]):
 
 
 
-def get_canonical(temperatures=[1.0, 1.0], plot=False):
+def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     """
     Obtain the properties of a single canonical distribution.
     """
-
-    subset = particles_info # Might need to remove incomplete reps though
-
     rep_ids = np.arange(min(particles_info["run_id"]),
                         max(particles_info["run_id"] + 1))
 
-    print("Found {reps} switch sampler reps."\
-                    .format(reps=np.max(rep_ids)))
-
-    ln_w = subset["ln_prior_mass"]\
-                   - logsumexp(subset["ln_prior_mass"])
-    ln_s = np.zeros(subset.shape[0])
+    ln_w = particles_info["ln_prior_mass"]\
+                   - logsumexp(particles_info["ln_prior_mass"])
+    ln_s = np.zeros(particles_info.shape[0])
     for i in range(len(temperatures)):
-        ln_s += subset["scalars[{i}]".format(i=i)]/temperatures[i]
[…]

### 2018-05-29 python/canonical.py
Working on temperature grid function

@@ -117,6 +117,29 @@ def create_canonical(particles_info,
     indices = np.sort(np.array(indices))
 
 
+def evaluate_temperature_grid(particles_info, T_min, T_max):
+    """
+    Evaluate logZ and H on a temperature grid.
+    """
+    ln_Z = np.empty((51, 51))
+    H = np.empty((51, 51))
+
+    T0 = 10.0**np.linspace(np.log10(T_min[0]),
+                                        np.log10(T_max[0]), ln_Z.shape[0])
+    T1 = 10.0**np.linspace(np.log10(T_min[1]),
+                                        np.log10(T_max[1]), ln_Z.shape[1])
+    [T0, T1] = np.meshgrid(T0, T1)
+
+    for i in ln_Z.shape[0]:
+        for j in ln_Z.shape[1]:
+            results = get_canonical(particles_info,
+                                    temperatures=[T0[i, j], T1[i, j]])
+            ln_Z[i, j] = results["ln_Z"]
+            H[i, j] = results["H"]
+
+    plt.imshow(ln_Z, origin="lower")
+    plt.show()
+
 
 if __name__ == "__main__":
 

### 2018-05-29 python/canonical.py
Temperature grids

@@ -60,7 +60,6 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     return h
 
 
-
 def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     """
     Obtain the properties of a single canonical distribution.
@@ -91,6 +90,7 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
 
     return result
 
+
 def create_canonical(particles_info,
                      result, outfile="../output/canonical_particles.csv"):
     """
@@ -117,27 +117,42 @@ def create_canonical(particles_info,
     indices = np.sort(np.array(indices))
 
 
-def evaluate_temperature_grid(particles_info, T_min, T_max):
+def evaluate_temperature_grid(particles_info, limits):
     """
     Evaluate logZ and H on a temperature grid.
     """
-    ln_Z = np.empty((51, 51))
-    H = np.empty((51, 51))
+    T0_min, T0_max, T1_min, T1_max = limits
 
-    T0 = 10.0**np.linspace(np.log10(T_min[0]),
-                                        np.log10(T_max[0]), ln_Z.shape[0])
-    T1 = 10.0**np.linspace(np.log10(T_min[1]),
-                                        np.log10(T_max[1]), ln_Z.shape[1])
+    # Set up results grids
+    ln_Z = np.empty((21, 21))
+    H = np.empty((21, 21))
+
+    # Temperature grids
+    T0 = 10.0**np.linspace(np.log10(T0_min),
+                                        np.log10(T0_max), ln_Z.shape[0])
+    T1 = 10.0**np.linspace(np.log10(T0_min),
+                                        np.log10(T0_max), ln_Z.shape[1])
     [T0, T1] = np.meshgrid(T0, T1)
 
-    for i in ln_Z.shape[0]:
-        for j in ln_Z.shape[1]:
+    for i in range(ln_Z.shape[0]):
+        for j in range(ln_Z.shape[1]):
             results = get_canonical(particles_info,
                                     temperatures=[T0[i, j], T1[i, j]])
             ln_Z[i, j] = results["ln_Z"]
             H[i, j] = results["H"]
+        print(i+1)
 
-    plt.imshow(ln_Z, origin="lower")
+    plt.subplot(1, 2, 1)
[…]

### 2018-05-29 python/canonical.py
Improved grid plots

@@ -24,7 +24,7 @@ def load_particles_info(filename="../output/particles_info.csv"):
         print("There are no completed reps.")
         return particles_info
 
-    print("Found {n} completed reps.".format(n=len(completed_reps)))
+    print("Found {n} completed reps.\n".format(n=len(completed_reps)))
 
     # Mark completed reps for keeping
     keep = np.zeros(particles_info.shape[0], dtype="bool")
@@ -124,8 +124,11 @@ def evaluate_temperature_grid(particles_info, limits):
     T0_min, T0_max, T1_min, T1_max = limits
 
     # Set up results grids
-    ln_Z = np.empty((21, 21))
-    H = np.empty((21, 21))
+    ln_Z = np.empty((51, 51))
+    H = np.empty((51, 51))
+
+    print("Computing temperature grid. It takes a long time", end="",
+          flush=True)
 
     # Temperature grids
     T0 = 10.0**np.linspace(np.log10(T0_min),
@@ -134,14 +137,16 @@ def evaluate_temperature_grid(particles_info, limits):
                                         np.log10(T0_max), ln_Z.shape[1])
     [T0, T1] = np.meshgrid(T0, T1)
 
+    # Compute over the grid
     for i in range(ln_Z.shape[0]):
         for j in range(ln_Z.shape[1]):
             results = get_canonical(particles_info,
                                     temperatures=[T0[i, j], T1[i, j]])
             ln_Z[i, j] = results["ln_Z"]
             H[i, j] = results["H"]
-        print(i+1)
+            print(".", end="", flush=True)
 
+    # Plot the results
     plt.subplot(1, 2, 1)
     plt.imshow(ln_Z, origin="lower", extent=np.log10(limits))
     plt.xlabel("log10(T_0)")
@@ -166,10 +171,10 @@ if __name__ == "__main__":
 
     print("ln(Z) = {ln_Z}.".format(ln_Z=result["ln_Z"]))
     print("H = {H} nats.".format(H=result["H"]))
-    print("ESS = {ESS}.".format(ESS=result["ESS"]))
+    print("ESS = {ESS}.\n".format(ESS=result["ESS"]))
 
-    print("\nFor the example, the true value of ln(Z) is " + \
-          "-8073.72, and H is 63.7246 nats.")
+    print("For the example, the true value of ln(Z) is " + \
+          "-8073.72, and H is 63.7246 nats.\n")
 
     h = plot_particle_scalars(particles_info)
     plt.show()

### 2018-05-30 python/canonical.py
Scalars as well

@@ -91,30 +91,30 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     return result
 
 
-def create_canonical(particles_info,
-                     result, outfile="../output/canonical_particles.csv"):
-    """
-    Create and save samples from the canonical distribution.
-    Argument: a dictionary as output by get_canonical().
-    """
-    ln_W = result["ln_W"]
-    max_ln_W = np.max(ln_W)
+#def create_canonical(particles_info,
+#                     result, outfile="../output/canonical_particles.csv"):
+#    """
+#    Create and save samples from the canonical distribution.
+#    Argument: a dictionary as output by get_canonical().
+#    """
+#    ln_W = result["ln_W"]
+#    max_ln_W = np.max(ln_W)
 
-    # Indices of particles
-    indices = []
-    attempts = 0
-    while True:
-        attempts += 1
-        print(attempts)
+#    # Indices of particles
+#    indices = []
+#    attempts = 0
+#    while True:
+#        attempts += 1
+#        print(attempts)
 
-        k = rng.randint(len(ln_W))
-        p = np.exp(ln_W[k] - max_ln_W)
-        if rng.rand() <= p:
-            indices.append(k)
-        if len(indices) >= int(result["ESS"]):
-            break
+#        k = rng.randint(len(ln_W))
+#        p = np.exp(ln_W[k] - max_ln_W)
+#        if rng.rand() <= p:
+#            indices.append(k)
+#        if len(indices) >= int(result["ESS"]):
+#            break
 
-    indices = np.sort(np.array(indices))
+#    indices = np.sort(np.array(indices))
 
 
 def evaluate_temperature_grid(particles_info, limits):
@@ -126,9 +126,11 @@ def evaluate_temperature_grid(particles_info, limits):
     # Set up results grids
     ln_Z = np.empty((51, 51))
     H = np.empty((51, 51))
+    S0 = np.empty((51, 51))
+    S1 = np.empty((51, 51))
 
-    print("Computing temperature grid. It takes a long time", end="",
-          flush=True)
+    print("Computing temperature grid. It takes a while (one dot=one pixel)",
+          end="", flush=True)
 
     # Temperature grids
[…]

### 2018-05-30 python/canonical.py
Compute expectation properly

@@ -150,10 +150,9 @@ def evaluate_temperature_grid(particles_info, limits):
             H[i, j] = results["H"]
 
             # Compute expectations
-            ln_W = results["ln_W"]
-            S0[i, j] = logsumexp(ln_W + particles_info["scalars[0]"])
-            S1[i, j] = logsumexp(ln_W + particles_info["scalars[1]"])
-
+            W = np.exp(results["ln_W"])
+            S0[i, j] = np.sum(W*particles_info["scalars[0]"])
+            S1[i, j] = np.sum(W*particles_info["scalars[1]"])
             print(".", end="", flush=True)
     print("")
 

### 2018-05-30 examples/All.h
Atoms example

@@ -1,6 +1,7 @@
 #ifndef TwinPeaks2018_All_h
 #define TwinPeaks2018_All_h
 
+#include "Atoms.h"
 #include "Potts.h"
 #include "SpikeSlab.h"
 #include "TwoScalars.h"

### 2018-05-30 examples/Atoms.cpp

@@ -1,0 +1,136 @@
+#include "Atoms.h"
+#include "Utils.h"
+#include <cmath>
+#include <sstream>
+
+namespace TwinPeaks2018
+{
+
+Atoms::Atoms()
+:x(num_atoms), y(num_atoms), z(num_atoms)
+{
+
+}
+
+void Atoms::from_prior(RNG& rng)
+{
+    for(size_t i=0; i<x.size(); i++)
+    {
+        x[i] = L*rng.rand();
+        y[i] = L*rng.rand();
+        z[i] = L*rng.rand();
+    }
+}
+
+std::vector<double> Atoms::scalars() const
+{
+    // Scalars
+    std::vector<double> ss(2, 0.0);
+    for(int i=0; i<num_atoms; ++i)
+    {
+        for(int j=(i+1); j<num_atoms; ++j)
+        {
+            double rsq = pow(x[i] - x[j], 2) + pow(z[i] - z[j], 2);
+            ss[0] += -4*(pow(1./rsq, 6) - 2.0*pow(1.0/rsq, 3));
+        }
+    }
+
+    // Polymer potential
+    double k = 36*pow(2.0, 2.0/3);
+    double c = pow(2.0, 1.0/6);
+    double r;
+    // First sum
+    for(int i=0; i<(num_atoms-1); ++i)
+    {
+        r = sqrt(pow(x[i] - x[i+1], 2) + pow(y[i] - y[i+1], 2)
+                        + pow(z[i] - z[i+1], 2));
+        ss[1] += -0.5*k*pow(r - c, 2);
+    }
+
+    // Second sum
+    double dotprod;
+    for(int i=1; i<(num_atoms-1); ++i)
+    {
+        dotprod = (x[i] - x[i-1])*(x[i+1] - x[i])
+                    + (y[i] - y[i-1])*(y[i+1] - y[i])
+                    + (z[i] - z[i-1])*(z[i+1] - z[i]);
+        ss[1] += -0.5*k*pow(dotprod - 1., 2);
+    }
+
+    return ss;
+}
+
+double Atoms::perturb(RNG& rng)
+{
+    int reps = 1;
+    if(rng.rand() <= 0.5)
+        reps = (int)pow((double)num_atoms*3, rng.rand());
+
+    for(int rep=0; rep<reps; ++rep)
+    {
+        int i = rng.rand_int(num_atoms);
+
+        int which_coord = rng.rand_int(3);
+        double* coord = nullptr;
[…]

### 2018-05-30 examples/Atoms.h

@@ -1,0 +1,48 @@
+#ifndef TwinPeaks2018_Atoms_h
+#define TwinPeaks2018_Atoms_h
+
+#include <ostream>
+#include <string>
+#include <vector>
+#include "RNG.h"
+
+namespace TwinPeaks2018
+{
+
+class Atoms
+{
+    public:
+        static constexpr size_t num_scalars = 2;
+
+    private:
+        static constexpr int num_atoms = 30;
+        static constexpr double L = 100.0;
+
+        // Positions
+        std::vector<double> x, y, z;
+
+    public:
+        Atoms();
+
+        // Generate the point from the prior
+        void from_prior(RNG& rng);
+
+        // Metropolis-Hastings proposals
+        double perturb(RNG& rng);
+
+        // Getter
+        std::vector<double> scalars() const;
+
+        // For CSV header
+        static std::string description();
+
+        friend std::ostream& operator << (std::ostream& out, const Atoms& a);
+};
+
+// Output to stream
+std::ostream& operator << (std::ostream& out, const Atoms& a);
+
+} // namespace TwinPeaks2018
+
+#endif
+

### 2018-05-30 doc/ms.tex
Looks like it might not work out :(
Copied old draft over

--- 2018-05-23 doc/ms.tex
@@
-\documentclass[a4paper, 12pt]{article}
+%  LaTeX support: latex@mdpi.com
+%  In case you need support, please attach any log files that you could have, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+
+%=================================================================
+
+% LaTeX Class File and Rendering Mode (choose one)
+% You will need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+
+%=================================================================
+
+\documentclass[journal,article,accept,moreauthors,pdftex,12pt,a4paper]{mdpi}
+%--------------------
+% Class Options:
+%--------------------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% actuators, administrativesciences, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, appliedsciences, arts, atmosphere, atoms, axioms, batteries, behavioralsciences, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsciences, buildings, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, cosmetics, crystals, data, dentistryjournal, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, inorganics, insects, ijerph, ijfs, ijms, ijns, ijgi, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, joi, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, lubricants, machines, marinedrugs, materials, mathematics, medicalsciences, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, nanomaterials, ncrna, nutrients, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, sinusitis, socialsciences, societies, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, vaccines, veterinarysciences, viruses, water
+%---------
+% article
+%---------
+% The default type of manuscript is article, but could be replaced by using one of the class options:
+% article, review, communication, commentary, bookreview, correction, addendum, editorial, changes, supfile, casereport, comment, conceptpaper, conferencereport, meetingreport, discussion, essay, letter, newbookreceived, opinion, projectreport, reply, retraction, shortnote, technicalnote, creative, datadescriptor (for journal Data), briefreport, hypothesis, interestingimage
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g.
+the logo of the journal will get visible), the headings, and the copyright information.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+% Please insert a blank line is before and after all equation and eqnarray environments to ensure proper line numbering when option submit is chosen
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%---------
+% pdftex
+%---------
+% The option "pdftex" is for use with pdfLaTeX only. If eps figure are used, use the optioin "dvipdfm", with LaTeX and dvi2pdf only.
+
+%=================================================================
+\setcounter{page}{1}
+\lastpage{x}
+\doinum{10.3390/------}
+\pubvolume{xx}
+\pubyear{2016}
+%\externaleditor{Academic Editor: xx}
+\history{Received: xx / Accepted: xx / Published: xx}
+
+\usepackage[utf8]{inputenc}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
 \usepackage{amsmath}
@@
 \usepackage{dsfont}
-\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
 \usepackage{graphicx}
-\usepackage[utf8]{inputenc}
 \usepackage{microtype}
@@
 
-\newcommand{\bell}{\boldsymbol{\ell}}
-\newcommand{\btheta}{\boldsymbol{\theta}}
-\newcommand{\given}{\,|\,}
+\DeclareUnicodeCharacter{00A0}{ }
+\newcommand{\xx}{\boldsymbol{\theta}}
+\newcommand{\dx}{d\boldsymbol{\theta}}
+\newcommand{\data}{\boldsymbol{D}}
+\newcommand{\II}{\boldsymbol{I}}
 
-\title{TwinPeaks2018}
-\author{Brendon J. Brewer}
-%\date{}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+
+% Add packages and commands to include here
+% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are loaded by the MDPI class.
+%\usepackage{graphicx}
+%\usepackage{subfigure,psfig}
+
+%=================================================================
+%% Please use the following mathematics environments:
+% \theoremstyle{mdpi}
+% \newcounter{thm}
+% \setcounter{thm}{0}
+% \newcounter{ex}
+% \setcounter{ex}{0}
+% \newcounter{re}
+% \setcounter{re}{0}
+%
+% \newtheorem{Theorem}[thm]{Theorem}
+% \newtheorem{Lemma}[thm]{Lemma}
+% \newtheorem{Corollary}[thm]{Corollary}
+% \newtheorem{Proposition}[thm]{Proposition}
+%
+% \theoremstyle{mdpidefinition}
+% \newtheorem{Characterization}[thm]{Characterization}
+% \newtheorem{Property}[thm]{Property}
+% \newtheorem{Problem}[thm]{Problem}
+% \newtheorem{Example}[ex]{Example}
+% \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
+% \newtheorem{Remark}[re]{Remark}
+% \newtheorem{Definition}[thm]{Definition}
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+
+% Full title of the paper (Capitalized)
+\Title{Nested sampling with two objective functions}
+
+% Authors (Add full first names)
+\Author{Brendon J. Brewer$^{1,}$*,
+        Robert J. N. Baldock$^{2}$,
+        Ewan Cameron$^{3}$}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ Department of Statistics, The University of Auckland, Private Bag 92019,
+Auckland 1142, New Zealand \\
+$^{2}$ Cavendish, University of Cambridge, Cambridge, UK \\
+$^{3}$ Spatial Ecology and Epidemiology Group, Tinbergen Building, Department
+of Zoology, University of Oxford, South Parks Road, Oxford, UK\\}
+
+%\contributed{$^\dagger$ These authors contributed equally to this work.}
+
+% Contact information of the corresponding author (Add [2] after \corres if there are more than one corresponding author.)
+\corres{{\tt bj.brewer@auckland.ac.nz}}
+
+% Abstract (Do not use inserted blank lines, i.e. \\)
+\abstract{We present a generalization of the Nested Sampling algorithm
+that estimates
+the partition function $Z(\beta_1, \beta_2)$ for a family of
+probability distributions indexed by two hyperparameters, $\beta_1$ and
+$\beta_2$. Problems like this arise frequently in statistical mechanics and
+occasionally in Bayesian inference.
+We demonstrate the algorithm on three example problems.
+The first is a toy problem whose structure allows us
+to accurately calculate $Z(\beta_1, \beta_2)$ numerically using non-Monte-Carlo
+methods.
+We show empirically how the accuracy of TwinPeaks
+improves as a function of the number of particles used, $N$. We also
+calculate the partition function for a collection of atoms with a potential
+that is `intermediate' between a Lennard-Jones form and a polymer form.
+Finally, we present a Bayesian image reconstruction example,
+where we can infer the value of a hyperparameter even though its prior
+distribution contains an `intractable' normalizing constant.}
+
+% Keywords: add 3 to 10 keywords
+\keyword{nested sampling; bayesian computation; statistical mechanics}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{}
+%\MSC{}
+%\JEL{}
+
+% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
+%\conference{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% For journal Data:
+
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-\maketitle
 
-%\abstract{\noindent Abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Need this after the abstract
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{8pt}
+\section{Introduction}
 
-The prior is $\pi(\btheta)$ and the scalars are
-$f(\btheta)$ and $g(\btheta)$. Letting $x=f(\btheta)$ and $y=g(\btheta)$,
-the implied prior for $x$ and $y$ will be written $\pi(x, y)$.
+Nested Sampling \citep[NS][]{skilling} is popular general
+Monte Carlo algorithm that can solve a wide range of problems in Bayesian
+computation and statistical mechanics
+\citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
+Its key strength its ability to cope with phase transitions which cause
+problems for many other methods \citep{skilling}.
+In a Bayesian inference problem with unknown parameters denoted collectively
+by a vector $\xx$, the
+posterior distribution for the parameters given data $\data$ (and prior
+information $\II$) is:
+\begin{eqnarray}
+p(\xx | \data, \II) &=&
+\frac{p(\xx | \II)p(\data | \xx, \II)}{p(\data | \II)}\\
+&=& \frac{\pi(\xx)L(\xx)}{Z}
+\end{eqnarray}
+where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
+function, and $Z$ is the normalising constant, usually known as the
+`marginal likelihood' or the `evidence':
+\begin{eqnarray}
+Z &=& \int \pi(\xx) L(\xx) \, \dx.\label{eqn:evidence}
+\end{eqnarray}
 
-Consider a family of thresholded distributions, indexed by threshold
-values $(x^*, y^*)$, given by
-\begin{align}
-p(x, y; x^*, y^*) &= \frac{\pi(x, y)\mathds{1}(x > x^*, y > y^*)}
-                          {X(x^*, y^*)}
-\end{align}
-The normalising constant is the probability in the `upper right corner':
-\begin{align}
-X(x^*, y^*) &= \int_{y^*}^{\infty} \int_{x^*}^{\infty} \pi(x, y) \, dx \, dy.
-\end{align}
+$Z$ is useful because it is the (prior) probability of the data given that
+$\xx$ is {\em one of}
+the possibilities in the space being integrated over, and thus plays the role
+of a likelihood for the parameter space as a whole.
+The main goal of NS is to approximate $Z$, but it can also be used to make
+Monte Carlo approximations of the posterior distribution, and to
+calculate the `information',
+or Kullback-Leibler divergence from the prior to the posterior:
+\begin{eqnarray}
+H &=& \int p(\xx | \data, \II) \ln
+\left[\frac{p(\xx | \data, \II)}{p(\xx | \II)}\right] \, d\xx \\
+&=& \int \frac{\pi(\xx) L(\xx)}{Z} \ln
+\left[\frac{L(\xx)}{Z}\right] \, d\xx.
+\end{eqnarray}
+$H$ quantifies how compressed the posterior distribution is with
+respect to the prior. For example, $H = 10$ implies (loosely speaking)
+that the posterior occupies a fraction $e^{-10}$ of the prior mass.
+$H$ can be interpreted quite literally as a measure of how much
+the data $\data$ told you about $\xx$.
 
-The Kullback-Leibler divergence from the prior to a thresholded distribution
-is
-\begin{align}
-D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, \pi(x, y)\right) &=
-    \log X(x^*, y^*).
-\end{align}
+NS works by drawing particles from the
+prior $\pi(\xx)$ and successively imposing constraints on the value of
+the likelihood $L(\xx)$ that compress the prior mass by a (roughly) known
+and constant factor. Like related algorithms such as those
+based on `annealing' or `tempering', NS
+moves through a sequence of probability distributions beginning from the
+prior. This sequence of distributions is defined by
+\begin{eqnarray}
+p(\xx; \ell) &=& \frac{1}{X(\ell)}\pi(\xx)\mathds{1}\left(L(\xx) > \ell\right).
+\label{eq:constrained_prior}
+\end{eqnarray}
+and the marginal likelihood can be computed by numerically integrating the
+function $L(X)$:
+\begin{eqnarray}
+Z &=& \int_0^1 L(X)\, dX.
+\end{eqnarray}
+Throughout this paper we use the popular `overloaded' notation for some
+functions and probability distributions.
+For example, $L(\xx)$ is the likelihood function, and $L(X)$ is the likelihood
+as a function of the enclosed prior mass $X$. These cannot literally be the
+same function as the inputs typically don't have the same dimensionality
+($\xx$ is usually a collection of quantities and $X$ is a single real number
+in $[0, 1]$).
+Therefore the symbol $L$ implies the output of the function is a
+likelihood value; so $L(\xx)$ represents a likelihood value computed from
+the parameters $\xx$, and $L(X)$ represents a likelihood value that
+corresponds to an amount $X$ of prior mass.
 
-\section{Nested Sampling distribution}
-Consider the following distribution:
-\begin{align}
-p_{\rm NS}(x, y) &= \frac{\pi(x, y)}{C X(x, y)}.
-\end{align}
-Compared to the prior $\pi$, this puts more weight at high values of
-$x$ and $y$.
+Naively, Equation~\ref{eqn:evidence} appears straightforward to compute because
+it is a simple expectation of $L$ with respect to the distribution $\pi$.
+However,
+NS is required because Equation~\ref{eqn:evidence}
+is the expected value of $L$ with respect to a very heavy-tailed distribution
+(the prior for the $L$ value implied by $\pi(\xx)$). Hence, there is a strong
+connection between NS and ideas from rare event simulation. \citet{walter} has
+explicitly explored this connection.
 
-The KL divergence from $p_{\rm NS}$ to $p(x, y ; x^*, y^*)$ is
-\begin{align}
-D_{\rm KL}\left(p(x, y; x^*, y^*) \,||\, p_{\rm NS}(x, y)\right)
-&=
-\int_{y^*}^{\infty} \int_{x^*}^{\infty}
-    \frac{\pi(x, y)}{X(x^*, y^*)}
-    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
-    \, dx \, dy \\
-&=
-\frac{1}{X(x^*, y^*)}
-\int_{y^*}^{\infty} \int_{x^*}^{\infty}
-    \pi(x, y)
-    \log \left[\frac{C X(x, y)}{X(x^*, y^*)}\right]
-    \, dx \, dy \\
-&=
-\frac{\int_{y^*}^{\infty} \int_{x^*}^{\infty}
-     \pi(x, y)
-     \log \left[C X(x, y)\right]
-     \, dx \, dy - X(x^*, y^*)\log X(x^*, y^*)}
-     {X(x^*, y^*)}
-\end{align}
+Using a single NS run, we can also calculate the properties of any other distribution that
+is (in some sense which we do not make precise) {\em intermediate}
+between the prior and the posterior. For example, we might be interested in
+a `power posterior' where the likelihood is raised to a power $\beta$
+(this is also the family of distributions used in `annealing' or `tempering'
+methods):
+\begin{eqnarray}
+p(\xx; \beta) &=& \frac{\pi(\xx)L(\xx)^\beta}{Z(\beta)}\label{eqn:power_posterior}
+\end{eqnarray}
+The normalisation and posterior samples from this distribution can be obtained
+from the original NS run by re-weighting the output according to $L(\xx)^\beta$
+instead of the usual $L(\xx)$ used to obtain the posterior.
+Bayesian inference problems with `gaussian noise' likelihood assumptions
+provide an example of where power posteriors might be useful.
+Computing $p(\xx; \beta)$ for $\beta \neq 1$ allows us to explore what the
+posterior distribution would have been if the noise variance had been greater,
+without having to re-run the algorithm.
+This is different from including an extra parameter to allow the noise variance
+to be greater, because NS allows you to test the consequences of values of the
+variance that are very implausible given the data, i.e. that do not have
+a high posterior probability.
+
+Alternatives to NS include methods based on `annealing', where a sequence of
+distributions of the form of Equation~\ref{eqn:power_posterior} is used.
+There are many different methods based on this idea, such as the popular
+parallel tempering method \citep{pt, gregory}.
+However, unlike annealing methods, NS requires only a small number of
+tuning parameters (just the number of particles $N$ is inherent to NS, although
+most NS implementations have additional tuning parameters related to their
+methods for sampling Equation~\ref{eq:constrained_prior}). Annealing methods
+also tend to fail on phase change problems \citep{skilling} which can arise
+in data analysis \citep{rjobject, exoplanet} as well as in statistical
+mechanics, where they are more familiar.
+
+In statistical mechanics, Equation~\ref{eqn:power_posterior} defines the
+family of {\it canonical distributions}, usually written as:
+\begin{eqnarray}
+p(\xx; \beta) &=& \frac{\pi(\xx)\exp[-\beta E(\xx)]}{Z(\beta)}
+\end{eqnarray}
+where $E(\xx)$ is the energy function (analogous to minus the log likelihood
+in the Bayesian case), and $\pi(\xx)$ is often uniform over
+phase space (the set of possible positions and momenta of a collection of
+particles) or configuration space (the set of possible positions of a collection
+of particles). In this context we usually want to
+compute $Z(\beta)$ as a function of $\beta$, which is called the
+{\it partition function}. The quantity $\mathcal{I}(\beta)$ is, up to a sign
+change and an additive constant, the Gibbs entropy.
+NS can achieve this, allowing the study of
+the properties of materials from first principles, based on hypotheses about
+the atoms or molecules that make them up \citep[e.g.][]{2009arXiv0906.3544P,
+2014PhRvE..89b2302P, 2015arXiv150303404B}. The NS algorithm is invariant under
+monotonic transformations of $L$ or $E$ and therefore there we can discuss the
+algorithm in Bayesian or statistical mechanical terms without loss of
+generality.
+
+Throughout this paper we will refer to $L(\xx)$ or
+$-E(\xx)$ as `objective functions',
+by analogy with the terminology used when
+discussing optimization methods. Although we are interested in sampling rather
+than optimization, we still want to increase the values of $L$ or decrease
+the values of $E$ relative to what is typical of the prior.
+
+In some inference and
+statistical mechanics problems, there are two or more scalar functions of
+$\xx$ that are relevant. Suppose our prior is $\pi(\xx)$ as before, and
+we obtain information that fixes the expected values of two scalar
+functions of $\xx$, $L_1(\xx)$ and $L_2(\xx)$.
+It is well known that the
+updated probability distribution that takes into account the constraints is
+of the canonical form:
+\begin{eqnarray}
+p(\xx; \beta_1, \beta_2) &=& \frac{\pi(\xx)\exp\left[\beta_1L_1(\xx)+\beta_2L_2(\xx)\right]}
+{Z(\beta_1, \beta_2)}
+\end{eqnarray}
+where $\beta_1$ and $\beta_2$ are two `inverse temperatures' (the temperatures
+themselves are $T_1 = \beta_1^{-1}$ and $T_2 = \beta_2^{-1}$).
+In a Bayesian
+context, this distribution (when $\beta_1 = \beta_2 = 1$) could be the
+posterior distribution for parameters $\xx$
+given two datasets, where $L_1$ and $L_2$ are the
+likelihood functions for each dataset. In statistical mechanics, $L_1$ might
+be $\exp\left(-\textnormal{energy}\right)$ and $L_2$ might be the total
+angular momentum, or be a term depending on an external field (so $\beta_2$
+would then describe the strength of the external field).
+
+If we are only interested in a single canonical distribution, for example
+with $\beta_1 = 0.3$ and $\beta_2 = 0.7$, we can estimate its normalising
+constant and by running standard Nested Sampling with objective function
+$L(\xx) = \exp\left[0.3L_1(\xx) + 0.7L_2(\xx)\right]$. However, usually we
+are interested in a range of values for $\beta_1$ and $\beta_2$, and we
+want to know the entire partition function $Z(\beta_1, \beta_2)$.
+This work describes
+progress towards solving this class of problems while maintaining the benefits
+of Nested Sampling, such as the ability to cope with first-order phase
+transitions. The algorithm is designed for problems with two objective
+functions, but may generalize to problems with more than two (though perhaps
+not more than a few).
+
+The prior $\pi(\xx)$ implies a certain prior for $L_1$ and $L_2$, which we
+denote $\pi(L_1, L_2)$. An example of a prior is shown as the
+probability density in Figure~\ref{fig:joint1}. The partition function
+$Z(\beta_1, \beta_2)$ is a set of expected values with respect to this density.
+Simple Monte Carlo sampling from $\pi$ will not work except for values of
+$(\beta_1, \beta_2)$ where the canonical distribution remains similar to $\pi$.
+We need a sampler that explores regions where $L_1$ and $L_2$ are high in order
+to accurately estimate $Z(\beta_1, \beta_2)$.
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.5]{figures/joint1.pdf}
+%\caption{\it An example of a prior for $L_1$ and $L_2$, which is implied by
+%the prior $\pi(\xx)$. We have overplotted 25 points drawn from this prior.
+%The estimated prior mass in the shaded rectangle is
+%$\hat{X}(2, 1.5) = 5/25 = 0.2$.
+%\label{fig:joint1}}
+%\end{figure}
+
+%Our proposed algorithm (introduced in Section~\ref{sec:algorithm}) makes use
+%of the (two dimensional) cumulative distribution of the objective functions.
+%For any values $(\ell_1, \ell_2)$ of the objective functions,
+%the prior mass for which both $L_1 \geq \ell_1$ {\em and} $L_2 \geq \ell_2$ is:
+%\begin{eqnarray}
+%X(\ell_1, \ell_2) &=& \int \pi(L_1, L_2)
+%\mathds{1}\left[L_1 \geq \ell_1, L_2 \geq \ell_2 \right]
+% \, dL_1 \, dL_2.
+%\end{eqnarray}
+%Since $X$ is a probability, it must satisfy a product rule:
+%\begin{eqnarray}
+%X(\ell_1, \ell_2) = X(\ell_1)X(\ell_2 | \ell_1) = X(\ell_2)X(\ell_1 | \ell_2).
+%\end{eqnarray}
+
+%When the prior $\pi$ is approximated with a set of $N$
+%particles $\{\xx_i\}_{i=1}^N$
+%(Monte Carlo samples ``drawn from'' $\pi$),
+%$X(\ell_1, \ell_2)$ can be approximated by:
+%\begin{eqnarray}
+%\hat{X}(\ell_1, \ell_2) &=&
+%\frac{1}{N}
+%\sum_{i=1}^N \mathds{1}\left[L_1(\xx_i) \geq \ell_1,
+%L_2(\xx_i) \geq \ell_2\right].\label{eqn:corner_count}
+%\end{eqnarray}
+%Graphically, on a plot of $L_2$ vs. $L_1$, $\hat{X}(\ell_1, \ell_2)$
+%is the fraction of particles in the rectangle whose upper right corner is at
+%$\left(\ell_1, \ell_2\right)$. See Figure~\ref{fig:joint1} for an
+%example.
+
+\section{Properties of Nested sampling}
+
+We seek an algorithm for computing the partition function
+$Z(\beta_1, \beta_2)$ for a range of values of the $\beta$s, from a single
+run. To be a variant of Nested Sampling, the algorithm should satisfy
+the following properties:
+\begin{enumerate}
+\item It should begin with $N$ points drawn from the prior $\pi(\xx)$.
+\item It should seek to explore regions where the values of
+$L_1(\xx)$ and $L_2(\xx)$ are higher than the prior $\pi(L_1, L_2)$
+would typically imply.
+\item The algorithm should consider a sequence of probability
+distributions proportional to $\pi$, but restricted to smaller and smaller
+domains for which the enclosed prior mass shrinks by a (roughly) constant and
+known factor at each iteration.
+\item The algorithm should be invariant to monotonic transformations of
+$L_1$ and $L_2$, i.e. it should only depend on rankings of $L_1$ and $L_2$
+values and not the values themselves.
+\end{enumerate}
+The standard Nested Sampling algorithm has these properties but for a
+single objective function. The same is true of variants such as
+Diffusive Nested Sampling \citep{dnest}.
+
+%\section{Rationale}\label{sec:rationale}
+
+%Consider the following proposal, which we label the `turn-the-corner idea'.
+%Imagine running standard NS with $N$ particles
+%using the objective function $L_1(\xx)$.
+%After $M_1$ iterations, we'd be able to approximate
+%the function $X(\ell_1) = \int \pi(\xx) \, d\xx$
+%from $X\approx e^{-M_1/N}$ to $X=1$. Defining $Y=-\ln(X)$, we could also
+%construct an approximation to the function
+%$L_1(Y)$, a non-decreasing function of $Y$, from $Y=0$ to $Y\approx M_1/N$.
+%After $M$ iterations, we keep the last value of $L_1(\xx)$ obtained
+%(call it $L_1^*$), and continue to impose the constraint $L_1(\xx) > L_1^*$.
+
+%Subject to the constraint $L_1(\xx) > L_1^*$, standard NS can continue but
+%attempting to increase $L_2$ instead of $L_1$. This is what we mean by
+%`turning the corner'. After $M_2$ such iterations,
+%the algorithm would have compressed the prior by a factor
+%$e^{(M_1 + M_2)/N}$ and therefore ended at a point in the $(L_1, L_2)$ plane
+%where $X(L_1, L_2) \approx e^{-(M_1 + M_2)/N}$. Any such run consisting of
+%$M_1 + M_2$ iterations will therefore appoximately finish on a contour line
+%of the function $X(L_1, L_2)$.
+%We have explored the idea of using multiple turn-the-corner runs, with
+%the corner being turned at different times (i.e. using different values of
+%$M_1$), and combining the results using biased sampling
+%\citep{vardi, cameron} in order to estimate $Z(\beta_1, \beta_2)$. However,
+%this was very computationally intensive. We presented the turn-the-corner idea
+%here in order to provide an intuitive rationale for our actual algorithm given in
+%Section~\ref{sec:algorithm}.
+
+%Figure~\ref{fig:contours} shows the contour lines of $X(L_1, L_2)$ for the
+%prior in Figure~\ref{fig:joint1}. Each contour line encloses half of the
+%prior mass of the previous one. The fact that contours of $X(L_1, L_2)$ are
+%relevant suggests that a standard NS run with objective function
+%$X(L_1(\xx), L_2(\xx))$ would achieve a similar effect to the turn-the-corner
+%idea.
+
+%%\begin{figure}[ht!]
+%%\centering
+%%\includegraphics[scale=0.5]{figures/contours.pdf}
+%%\caption{\it The joint prior for the objective functions, and fifteen
+%%contours of the cumulative distribution $X(L_1, L_2)$, each enclosing half
+%%the prior mass of the previous one. \label{fig:contours}}
+%%\end{figure}
+
+%{\bf Try to relate this to \citet{vertical}}.
+
+%\section{Proposed algorithm}\label{sec:algorithm}
+
+%The basic idea of our algorithm is to try to mimic a standard NS run, where the
+%objective function being increased is
+%\begin{eqnarray}
+%Y(\xx) &=& 1/X\left(L_1(\xx), L_2(\xx)\right).
+%\end{eqnarray}
+%Standard NS cannot be applied simply because we cannot evaluate $X(L_1, L_2)$ and
+%therefore cannot restrict the parameter space based on the value of $X$ (or
+%equivalently, $Y$). However, given a number of Monte Carlo samples, we
+%can {\em approximate} $X$ by $\hat{X}(L_1, L_2)$, and restrict the parameter
+%space based on a contour of that approximation.
+%The algorithm is presented in detail below.
+
+%\begin{algorithm}[ht!]
+%\begin{algorithmic}
+%\State 1) Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
+%$N$ should quite large (typically 1000 or greater), and the algorithm is
+%slightly more elegant if $N$ is odd.
+%\State 2) Initialise the {\em remaining prior mass} to be $M=1$.
+%\State 3) Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
+%$\emptyset$.
+%\While{more iterations desired}
+%	\State i) Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
+%			and sort the $\hat{X}$ values observed.
+%	\State ii) Find the median $\hat{X}$ value, $\hat{X}_{(k)}$.
+%	\State iii) Classify all particles as either ``interior'', ``boundary'', or
+%			``exterior'', based on whether their $\hat{X}$ values are
+%			greater than, equal to, or less than $\hat{X}_{(k)}$ respectively.
+%	\State iv) If the number of interior particles $n_{\rm interior}$ or the number
+%			of exterior particles $n_{\rm exterior}$ is zero, replace $k$ by
+%			$(k-1)$ (to try a percentile other than the median)
+%			and go to step iii) (if $k=1$ then set $k=N$ instead of zero).
+%	\State v) Save all ``interior'' particles to disk, assigning each a prior weight of $n_{\rm interior}/(n_{\rm interior} + n_{\rm exterior})$.
+%	\State vi) Exclude the region in the $L_1$-$L_2$ plane where
+%$\hat{X} \geq \hat{X}_{(k)}$. That is, set
+%	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
+%	\State vii) Update the remaining prior mass to $M \leftarrow M n_{\rm exterior}/N$.
+%	\State viii) Replace all interior and boundary particles by new
+%			particles generated from $\pi(\xx)$, subject to the constraint
+%			of not being in the excluded region.
+%\EndWhile
+%\end{algorithmic}
+%\caption{\label{alg:algorithm}}
+%\end{algorithm}
+
+%Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.5]{figures/joint2.pdf}
+%\caption{\it The joint prior for the objective functions, and Monte Carlo
+%samples, as in Figure~\ref{fig:joint1}. The shaded region imposes a
+%constraint on the value of $\hat{X}$. Its boundary approximates a contour
+%of $X(L_1, L_2)$.
+%\label{fig:joint2}}
+%\end{figure}
+
+\section{Example 1: Known solution}
+We tested the algorithm on a simple 20-dimensional example, where the
+prior is a uniform distribution between 0 and 1 for each coordinate:
+\begin{eqnarray}
+\pi(\xx) &=& \prod_{i=1}^{20}
+\left\{
+\begin{array}{lr}
+1, & x_i \in [0, 1]\\
+0, & \textnormal{otherwise.}
+\end{array}
+\right.
+\end{eqnarray}
+The first objective function is quadratic in form, such that the canonical
+distribution is an iid gaussian centered at $(0.5, 0.5, ..., 0.5)$:
+\begin{eqnarray}
+L_1(\xx) &=& -\frac{1}{2} \sum_{i=1}^{20} \left(\frac{x_i - 0.5}{0.01}\right)^2.
+\end{eqnarray}
+
+The second objective function upweights states where coordinates $\{x_i\}$
+are close to 0, 0.25, 0.5, 0.75, or 1:
+\begin{eqnarray} 
+L_2(\xx) &=& -\sum_{i=1}^{100} \sin^2(4\pi x_i)
+\end{eqnarray}
+
+The true partition function (computed numerically) and the Kullback-Leibler
+divergence from the prior to the canonical distribution are shown in
+Figure~\ref{fig:truth} as a function of two temperatures.
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.75]{figures/truth.pdf}
+%\caption{The true partition function and KL divergence (from the prior to
+%the canonical distribution) as a function of two temperatures for the
+%test problem.\label{fig:truth}}
+%\end{figure}
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{figures/output.png}
+%\caption{The sequence of discarded particles (yellow) and
+%points representing the canonical distribution at temperatures
+%$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
+%\end{figure}
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.5]{figures/results.pdf}
+%\caption{Numerical results for the test problem. These compare well with the
+%true partition function and KL divergence given in Figure~\ref{fig:truth}.
+%\label{fig:results}}
+%\end{figure}
+
+\section{Example 2: Lennard-Jones/Polymer Example}
+
+Consider $n$ Lennard-Jones atoms confined to the unit cube $[0, 1]^3$.
+The position of each atom is given by a vector
+$\boldsymbol{r}_i = (x_i, y_i, z_i)$.
+The potential energy of any configuration of the atoms is given by
+a sum over all pairs of atoms:
+\begin{eqnarray}
+U_{\rm LJ} &=& \sum_{i=1}^n\sum_{j=(i+1)}^n U_{\rm LJ}
+(\boldsymbol{r}_i, \boldsymbol{r}_j)
+\end{eqnarray}
+where the inter-atomic potential energy is given by:
+
+\begin{eqnarray}
+U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)
+&=& 4\epsilon
+\left[
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^12 -
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^6
+\right].
+\end{eqnarray}
+We adopted the Lennard Jones units by setting $\epsilon=1$ and $\sigma=1$.
+
+In terms of the Lennard Jones parameters $\epsilon$ and $\sigma$, the
+``polymer'' potential is
+\begin{eqnarray}
+U_{\rm polymer} &=&
+\sum_{i=1}^{n-1} \phi^{(1)}_{i,i+1} + \sum_{i=2}^{n-1} \phi^{(2)}_{i-1, i, i+1}
+\end{eqnarray}
+where
+
+\begin{eqnarray}
+\phi^{(1)}_{i,i+1} &=& \frac{k}{2}\left(|\boldsymbol{r}_i - \boldsymbol{r}_{i+1}|- 2^{1/6}\sigma\right)^2,\\
+\phi^{(2)}_{i-1, i, i+1} &=& \frac{k}{2}
+\left((\boldsymbol{r}_i - \boldsymbol{r}_{i-1})\cdot(\boldsymbol{r}_{i-1} - \boldsymbol{r}_{i}) - 1\right)^2,
+\end{eqnarray}
+and $k=\frac{36 \times 2^{2/3}\epsilon}{\sigma^2}$ has been chosen to match
+the curvature of $U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)$.
+
+\section{Example 3: ``MaxEnt'' image deconvolution example}
+
+Problems with more than one objective function can also arise in data
+analysis. Consider, for example, the problem of deblurring a noisy
+image. A common approach to these problems is regularized inversion,
+such as the ``maximum entropy'' technique of \citet{gull}. It is important
+to distinguish between this method and the maximum entropy principle used
+to update or assign probabilities \citep{caticha}.
+
+The unknown parameters are a set of pixel intensities
+$\{x_i\}_{i=1}^n$ where $n$ is the number of pixels and $x_i \geq 0$.
+The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
+The prior for the dataset given the parameters is a normal distribution
+with mean given by the underlying image $\{xi\}$ convolved by
+a point spread function. The standard deviation of each pixel is
+$\sigma$, assumed known. This is usually written as
+
+\begin{eqnarray}
+\boldsymbol{D} = \boldsymbol{M}\boldsymbol{x} + \boldsymbol{n}
+\end{eqnarray}
+where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{M}$ is
+the blurring operator written in matrix form.
+
+The prior for the pixel intensities $\{x_i\}$ has an ``entropic'' form,
+where images are upweighted (relative to a uniform prior) if the pixel
+intensities have a low dynamic range. The prior density is defined conditional
+on a hyperparameter $\lambda$:
+\begin{eqnarray}
+p(\boldsymbol{x} | \lambda) &=&
+\frac{\exp\left[\lambda S(\xx)\right]}{\int \exp\left[\lambda S(\xx)\right] \, d\xx}
+\label{eq:entropy_prior}
+\end{eqnarray}
+where
+\begin{eqnarray}
+S(\xx) &=& -\sum_{i=1}^n x_i \ln x_i
+\end{eqnarray}
+is the ``configurational entropy'' of the image (crucially, this is a function of
+an image, and not a function of a probability distribution).
+The denominator in Equation~\ref{eq:entropy_prior} ensures the conditional prior
+is normalized.
+
+In the 1980s, this prior was thought to have a fundamental status, but this
+is no longer the case \citep{massinf}, although the function $S(\xx)$ does
+have special properties when its argument is a measure \citep{knuth_skilling}.
+However, it is still a prior whose
+consequences we might be interested in.
+
+Instead, we can consider the configurational
+entropy $S(\xx)$ as simply a function of an image that may
+be relevant somehow, and that we are uncertain about. The joint posterior
+for $\xx$ and $\lambda$ is:
+\begin{eqnarray}
+p(\lambda, \xx | \data) &=&
+\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+{p(\data)}\\
+&=&
+\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+{p(\data)}
+\end{eqnarray}
+
+The posterior for the underlying image given the data is
+\begin{eqnarray}
+p(\boldsymbol{x} | \boldsymbol{D}, \lambda)
+&=& \frac{p(\boldsymbol{x} | \lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda)}
+{\int p(\boldsymbol{x}|\lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda) \,d^n\boldsymbol{m}}\\
+&=& \frac{\exp\left[-\lambda \sum_i x_i\ln x_i
+-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]}
+{\int \exp\left[-\lambda \sum_i x_i\ln x_i
+-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]\, d^n\boldsymbol{m}}
+\end{eqnarray}
+
+This is a `doubly intractable' problem \citep{murray}, since an integral, whose
+result is a function of the parameters, appears in the {\em denominator} of the
+target density. However, in our case the integral in the
+denominator arises from the prior for the parameters, rather than from the
+likelihood function.
+
+\section{What kind of accuracy can we expect?}
+
+Imagine computing $Z(\beta_1, \beta_2)$ by looping over a grid of $\beta_2$
+values and doing an NS run with respect to $L_1$ for each. For each
+value of $\beta_1$ and $\beta_2$ that we're interested in, we can expect
+a (marginal) `one-sigma' accuracy in
+$\ln\left[Z(\beta_1, \beta_2)\right]$ of $\pm \sqrt{H(\beta_1, \beta_2)/N}$,
+for a computational cost proportional to...
+
+\section{What kind of accuracy do we need?}
+
+The following argument is due to John Skilling. Consider Bayesian model selection
+between two models $M_1$ and $M_2$. The Bayes Factor is the ratio of the
+two marginal likelihoods:
+\begin{eqnarray}
+B = \frac{P(D | M_1)}{P(D | M_2)} = \frac{Z_1}{Z_2}
+\end{eqnarray}
+where $Z_1 = \int \pi(\xx_1)L(\xx_1) \, d\xx_1$ and
+$Z_2 = \int \pi(\xx_2)L(\xx_2) \, d\xx_2$.
+In large problems, the log of the Bayes Factor is usually more convenient:
+\begin{eqnarray}
+\Delta := \ln B = \ln Z_1 - \ln Z_2.
+\end{eqnarray}
+Naively, we want $\Delta$ to an accuracy of about 0.1, so that we can reliably
+quantify the strength of the evidence when the two models are similarly
+supported by the data. But is this a realistic situation?
+
+Prior to knowing the data $D$, we don't know how much information we will get
+about the question of $M_1$ vs. $M_2$, quantified by the KL divergence:
+\begin{eqnarray}
+H &=& \sum_{i=1}^2 P(M_i | D)
+\ln\left[
+\frac{P(M_i | D)}{P(M_i)}
+\right].
+\end{eqnarray}
+
+The expected value of $H$ (with respect to the prior over datasets)
+is the mutual information:
+\begin{eqnarray}
+\mathcal{I} &=& \mathds{E}\left[H\right]\\
+&=&
+\sum_{i=1}^2 \int P(M_i, D)
+\ln\left[
+\frac{P(M_i, D)}{P(M_i)P(D)}
+\right] \, dD.
+\end{eqnarray}
+
+\section{Failure modes}\label{sec:failure_modes}
+
+If $L_1(\xx)$ and $L_2(\xx)$ are inversely and strongly dependent...
+
+%Use Skilling's argument about the prior distribution of a log Bayes factor.
+%Even though the performance of this algorithm won't be great for high $H$, it
+%will be good enough. I think the probability it won't give enough accuracy will
+%be ``exponentially small''.
+
+\acknowledgments{Acknowledgements}
+
+It is a pleasure to thank Rob Salamone (QUT),
+Gábor Csányi (Cambridge), Livia B. Pártay (Cambridge),
+and Will Handley (Cambridge) for valuable conversations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\authorcontributions{Author Contributions}
+
+BJB initiated the project and explored various ideas which did not work.
+EC worked on the biased sampling suggestion in Section~\ref{sec:rationale},
+discovered the failure mode in Section~\ref{sec:failure_modes}, and was involved
+in many other discussions about the project. RB suggested the statistical
+mechanics example and helped BJB to get it working and to interpret the results.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\conflictofinterests{Conflicts of Interest}
+The authors declare no conflict of interest.
+
+%=================================================================
+% References: Variant A
+%=================================================================
+% Back Matter (References and Notes)
+%----------------------------------------------------------
+% Style and layout of the references
+\bibliographystyle{mdpi}
+\makeatletter
+\renewcommand\@biblabel[1]{#1. }
+\makeatother
+
+\begin{thebibliography}{999} % if there are less than 10 entries, enter a one digit number
+
+\bibitem[Baldock et al.(2015)]{2015arXiv150303404B} Baldock, R.~J.~N., 
+P{\'a}rtay, L.~v.~B., Bart{\'o}k, A.~P., Payne, M.~C., Cs{\'a}nyi, G.\ 
+2015.\ Determining pressure-temperature phase diagrams of materials.\ ArXiv 
+e-prints arXiv: 1503.03404.
+
+\bibitem[Brewer and Donovan(2015)]{exoplanet} Brewer, B.~J., 
+Donovan, C.~P.\ 2015.\ Fast Bayesian inference for exoplanet discovery in 
+radial velocity data.\ Monthly Notices of the Royal Astronomical Society 
+448, 3206-3214.
+
+\bibitem[Brewer(2014)]{rjobject} Brewer, B.~J.\ 2014.\ Inference 
+for Trans-dimensional Bayesian Models with Diffusive Nested Sampling.\ 
+ArXiv e-prints arXiv:1411.3921.
+
+\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
+\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
+Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
+
+\bibitem[Cameron and Pettitt(2014)]{cameron} Cameron, E., and Pettitt, A., 2014,
+``Recursive pathways to marginal likelihood estimation with
+prior-sensitivity analysis.'' Statistical Science 29.3 (2014): 397-419.
+
+\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
+on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
+arXiv:0808.0012.
+
+\bibitem[\protect\citeauthoryear{Gregory}{2005}]{gregory}
+Gregory, Phil. Bayesian Logical Data Analysis for the Physical Sciences: A Comparative Approach with Mathematica® Support. Cambridge University Press, 2005.
+
+\bibitem[Gull and Daniell(1978)]{gull} Gull, Stephen F., and Daniell, G., 1978
+Image reconstruction from incomplete and noisy data. Nature (1978): 686-690.
+
+\bibitem[Hansmann(1997)]{pt} Hansmann, Ulrich HE., 1997, ``Parallel tempering algorithm for conformational studies of biological molecules.'', Chemical Physics Letters 281, no. 1 (1997): 140-150.
+
+\bibitem[Knuth and Skilling(2010)]{knuth_skilling} Knuth, K.~H., 
+Skilling, J.\ 2010.\ Foundations of Inference.\
+Axioms 1.1 (2012): 38-73.\
+ArXiv e-prints arXiv:1008.4831.
+
+\bibitem[Murray(2012)]{murray} Murray, Iain, Ghahramani, Zoubin, and MacKay, David.
+``MCMC for doubly-intractable distributions.'' arXiv preprint arXiv:1206.6848 (2012).
+
+\bibitem[P{\'a}rtay et al.(2014)]{2014PhRvE..89b2302P} P{\'a}rtay, L.~B., 
+Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2014.\ Nested sampling for materials: 
+The case of hard spheres.\ Physical Review E 89, 022302.
+
+\bibitem[P{\'a}rtay et al.(2009)]{2009arXiv0906.3544P} P{\'a}rtay, L.~B., 
+Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2009.\ Efficient sampling of atomic 
+configurational spaces.\ ArXiv e-prints arXiv: 0906.3544.
+
+\bibitem[Polson and Scott(2014)]{vertical}
+Polson, Nicholas G., and James G. Scott. ``Vertical-likelihood Monte Carlo
+Integration.'' arXiv preprint arXiv:1409.3601 (2014).
+
+\bibitem[\protect\citeauthoryear{Skilling}{1998}]{massinf}
+Skilling J., 1998, Massive Inference and Maximum Entropy, in Maximum Entropy
+and Bayesian Methods, Kluwer Academic Publishers, Dordrecht/Boston/London p.14
+
+\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, J., 2006, Nested Sampling for General Bayesian Computation, Bayesian Analysis 4, pp. 833-860.
+
+\bibitem[Vardi (1985)]{vardi}
+Vardi, Yehuda. ``Empirical distributions in selection bias models.'', The Annals of Statistics (1985): 178-203.
+
+\bibitem[Walter(2015)]{walter}
+Walter, C.\ Point Process-based Monte Carlo estimation.\ arXiv: 1412.6368.
+%% Reference 1
+%\bibitem{ref-journal}
+%Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
+
+%% Reference 2
+%\bibitem{ref-book}
+%Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
+
+\end{thebibliography}
+
+%=================================================================
+% References:  Variant B
+%=================================================================
+% Use the following option to include external BibTeX files:
+%\bibliography{lite}
+%\bibliographystyle{mdpi}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\abbreviations{Abbreviations/Nomenclature}
+%
+%Main text.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\appendix
+%\section{Appendix 1: Fast computation of upper corner counts}
+%The upper corner count of particle $i$ is defined as the value of
+%$\hat{X}$ at the position of particle $i$. Less formally, it is the number
+%of other particles that are `up and to the right' of particle $i$ in
+%a plot like Figure~\ref{fig:joint1}, plus one.
+
+%\begin{eqnarray}
+%C_i &=& \sum_{j=1}^N
+%\mathds{1}\left[L_1(\xx_j) \geq L_1(\xx_i), L_2(\xx_j) \geq L_2(\xx_i)\right]\\
+%&=& \sum_{j=1}^N
+%\mathds{1}\left[L_1(\xx_j) \geq L_1(\xx_i)\right]
+%\mathds{1}\left[L_2(\xx_j) \geq L_2(\xx_i)\right]
+%\end{eqnarray}
 

### 2018-05-30 examples/SpikeSlab.cpp
Shift

@@ -28,7 +28,7 @@ double SpikeSlab::perturb(RNG& rng)
 double SpikeSlab::log_likelihood() const
 {
     // A bunch of constants
-    static constexpr double shift = 0.0;
+    static constexpr double shift = 0.031;
     static constexpr double center = 0.5;
     static constexpr double u = 0.01;
     static constexpr double inv_u = 1.0/u;

### 2018-05-30 examples/TwoScalars.cpp
Cooler example

@@ -19,22 +19,28 @@ void TwoScalars::from_prior(RNG& rng)
 
 double TwoScalars::perturb(RNG& rng)
 {
-    int which = rng.rand_int(xs.size());
-    xs[which] += rng.randh();
-    wrap(xs[which], 0.0, 1.0);
+    int which;
+
+    int num;
+    if(rng.rand() <= 0.5)
+        num = 1;
+    else
+        num = (int)pow((double)N, rng.rand());
+    for(int i=0; i<num; ++i)
+    {
+        which = rng.rand_int(xs.size());
+        xs[which] += rng.randh();
+        wrap(xs[which], 0.0, 1.0);
+    }
+
     return 0.0;
 }
 
 double TwoScalars::f() const
 {
-    static constexpr double center = 0.3;
-    static constexpr double width = 0.01;
-    static constexpr double inv_width = 1.0/width;
-
     double result = 0.0;
     for(double x: xs)
-        result += -0.5*pow((x - center)*inv_width, 2);
-
+        result += -pow((x - 0.5)/0.1, 2);
     return result;
 }
 
@@ -42,7 +48,7 @@ double TwoScalars::g() const
 {
     double result = 0.0;
     for(double x: xs)
-        result += -2000*x;
+        result += -pow(sin(10*M_PI*x), 2);
     return result;
 }
 

### 2018-05-30 examples/TwoScalars.h

@@ -18,7 +18,7 @@ class TwoScalars
     private:
 
         // Dimensionality
-        static constexpr size_t N = 20;
+        static constexpr size_t N = 100;
 
         // The coordinates
         std::vector<double> xs;

### 2018-05-30 python/canonical.py

@@ -195,10 +195,10 @@ if __name__ == "__main__":
     print("ESS = {ESS}.\n".format(ESS=result["ESS"]))
 
     print("For the example, the true value of ln(Z) is " + \
-          "-8073.72, and H is 63.7246 nats.\n")
+          "-216.865, and H is 129.017 nats.\n")
 
     h = plot_particle_scalars(particles_info)
     plt.show()
 
-    evaluate_temperature_grid(particles_info, [0.1, 10.0, 0.1, 10.0])
+    evaluate_temperature_grid(particles_info, [0.1, 100.0, 0.1, 100.0])
 

### 2018-05-30 python/canonical.py
Size of grid is a parameter

@@ -117,17 +117,17 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
 #    indices = np.sort(np.array(indices))
 
 
-def evaluate_temperature_grid(particles_info, limits):
+def evaluate_temperature_grid(particles_info, limits, n=51):
     """
     Evaluate logZ and H on a temperature grid.
     """
     T0_min, T0_max, T1_min, T1_max = limits
 
     # Set up results grids
-    ln_Z = np.empty((51, 51))
-    H = np.empty((51, 51))
-    S0 = np.empty((51, 51))
-    S1 = np.empty((51, 51))
+    ln_Z = np.empty((n, n))
+    H = np.empty((n, n))
+    S0 = np.empty((n, n))
+    S1 = np.empty((n, n))
 
     print("Computing temperature grid. It takes a while (one dot=one pixel)",
           end="", flush=True)

### 2018-05-31 python/twinpeaks2018/canonical.py
Moved files

@@ -10,7 +10,7 @@ import pandas as pd
 from utils import logsumexp
 
 
-def load_particles_info(filename="../output/particles_info.csv"):
+def load_particles_info(filename="../../output/particles_info.csv"):
     """
     Load all the particles_info file, and return a data frame containing
     only complete runs (unless there aren't any, in which case it just
@@ -19,7 +19,7 @@ def load_particles_info(filename="../output/particles_info.csv"):
 
     particles_info = pd.read_csv(filename)
 
-    completed_reps = np.loadtxt("../output/completed_reps.txt")
+    completed_reps = np.loadtxt("../../output/completed_reps.txt")
     if len(completed_reps) == 0:
         print("There are no completed reps.")
         return particles_info
@@ -92,7 +92,7 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
 
 
 #def create_canonical(particles_info,
-#                     result, outfile="../output/canonical_particles.csv"):
+#                     result, outfile="../../output/canonical_particles.csv"):
 #    """
 #    Create and save samples from the canonical distribution.
 #    Argument: a dictionary as output by get_canonical().

### 2018-05-31 python/setup.py
Python packaging crap

@@ -1,0 +1,20 @@
+import setuptools
+
+setuptools.setup(
+    name="twinpeaks2018",
+    version="0.0.1",
+    author="Brendon J. Brewer",
+    author_email="brendon.brewer@gmail.com",
+    description="The Python package accompanying TwinPeaks2018",
+    long_description="The Python package accompanying TwinPeaks2018",
+    long_description_content_type="text/markdown",
+    url="https://github.com/eggplantbren/TwinPeaks2018",
+    packages=setuptools.find_packages(),
+    classifiers=(
+        "Programming Language :: Python :: 3",
+        "License :: OSI Approved :: GNU General Public License v3 (GPLv3)",
+        "Operating System :: OS Independent",
+    ),
+    install_requires=["matplotlib", "numpy", "pandas"]
+)
+

### 2018-05-31 python/twinpeaks2018/__init__.py

@@ -1,0 +1,2 @@
+name = "twinpeaks2018"
+

### 2018-05-31 python/twinpeaks2018/canonical.py

@@ -7,7 +7,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.random as rng
 import pandas as pd
-from utils import logsumexp
+from .utils import logsumexp
 
 
 def load_particles_info(filename="../../output/particles_info.csv"):

### 2018-05-31 python/twinpeaks2018/canonical.py
No main - showresults function instead

@@ -10,16 +10,16 @@ import pandas as pd
 from .utils import logsumexp
 
 
-def load_particles_info(filename="../../output/particles_info.csv"):
+def load_particles_info():
     """
     Load all the particles_info file, and return a data frame containing
     only complete runs (unless there aren't any, in which case it just
     returns whatever it's got).
     """
 
-    particles_info = pd.read_csv(filename)
+    particles_info = pd.read_csv("particles_info.csv")
+    completed_reps = np.loadtxt("completed_reps.txt")
 
-    completed_reps = np.loadtxt("../../output/completed_reps.txt")
     if len(completed_reps) == 0:
         print("There are no completed reps.")
         return particles_info
@@ -182,7 +182,10 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.show()
 
 
-if __name__ == "__main__":
+def showresults():
+    """
+    This is what you'll usually want to call.
+    """
 
     # Load the results
     particles_info = load_particles_info()

### 2018-05-31 output/showresults.py
Working on the Python

@@ -1,0 +1,3 @@
+import twinpeaks2018.canonical
+
+twinpeaks2018.canonical.showresults()

### 2018-05-31 python/twinpeaks2018/canonical.py

@@ -7,7 +7,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.random as rng
 import pandas as pd
-from .utils import logsumexp
+from twinpeaks2018.two_scalars_truth import compute_truth
+from twinpeaks2018.utils import logsumexp
 
 
 def load_particles_info():
@@ -57,6 +58,11 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
              ".", alpha=0.2, markersize=1)
     plt.xlabel(names[0])
     plt.ylabel(names[1])
+
+    plt.savefig("particle_scalars.png", dpi=600)
+    print("Saved particle_scalars.png")
+    plt.show()
+
     return h
 
 
@@ -156,8 +162,10 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
             print(".", end="", flush=True)
     print("")
 
+    truth = compute_truth(limits, n)
+
     # Plot the results
-    plt.figure(figsize=(8, 8))
+    plt.figure(1, figsize=(8, 8))
     plt.subplot(2, 2, 1)
     plt.imshow(ln_Z, origin="lower", extent=np.log10(limits))
     plt.ylabel("log10(T_1)")
@@ -169,17 +177,39 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.title("H")
 
     plt.subplot(2, 2, 3)
+    plt.imshow(ln_Z - truth["ln_Z"],
+               origin="lower", extent=np.log10(limits), cmap="coolwarm")
+    plt.xlabel("log10(T_0)")
+    plt.ylabel("log10(T_1)")
+    plt.title("Residuals")
+
+    plt.subplot(2, 2, 4)
+    plt.imshow(H - truth["H"],
+               origin="lower", extent=np.log10(limits), cmap="coolwarm")
+    plt.xlabel("log10(T_0)")
+    plt.ylabel("log10(T_1)")
+    plt.title("Residuals")
+
+    plt.savefig("ln_Z_H.png", dpi=600)
+    print("ln_Z_h.png")
+    plt.show()
+
+    plt.figure(2)
+    plt.subplot(1, 2, 1)
     plt.imshow(S0, origin="lower", extent=np.log10(limits))
     plt.xlabel("log10(T_0)")
     plt.ylabel("log10(T_1)")
     plt.title("<S_0>")
 
-    plt.subplot(2, 2, 4)
+    plt.subplot(1, 2, 2)
[…]

### 2018-05-31 python/twinpeaks2018/two_scalars_truth.py

@@ -1,0 +1,60 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from twinpeaks2018.utils import logsumexp
+
+def compute_truth(limits, n=51, plot=False):
+    T0_min, T0_max, T1_min, T1_max = limits
+
+    # Set up grids
+    ln_Z = np.empty((n, n))
+    H = np.empty((n, n))
+    x = np.linspace(0.0, 1.0, 100001)
+    dx = x[1] - x[0]
+
+    # Temperature grids
+    T0 = 10.0**np.linspace(np.log10(T0_min),
+                                        np.log10(T0_max), ln_Z.shape[0])
+    T1 = 10.0**np.linspace(np.log10(T0_min),
+                                        np.log10(T0_max), ln_Z.shape[1])
+    [T0, T1] = np.meshgrid(T0, T1)
+
+    # Compute over the grid
+    for i in range(ln_Z.shape[0]):
+        for j in range(ln_Z.shape[1]):
+
+            ln_y = -((x - 0.5)/0.1)**2 / T0[i, j] - \
+                        (np.sin(10*np.pi*x))**2 / T1[i, j]
+            ln_Y = ln_y - logsumexp(ln_y)
+            Y = np.exp(ln_Y)
+
+            # Normalisation constant and KL divergence
+            ln_Z[i, j] = 100*logsumexp(ln_y + np.log(dx))
+            H[i, j] = 100*np.sum(Y*ln_Y*dx)
+
+            print(".", end="", flush=True)
+    print("")
+
+    if plot:
+        # Plot the results
+        limits = [0.1, 100.0, 0.1, 100.0]
+        result = compute_truth(limits)
+
+        plt.figure(figsize=(8, 6))
+        plt.subplot(1, 2, 1)
+        plt.imshow(result["ln_Z"], origin="lower", extent=np.log10(limits))
+        plt.xlabel("log10(T_0)")
+        plt.ylabel("log10(T_1)")
+        plt.title("ln_Z")
+
+        plt.subplot(1, 2, 2)
+        plt.imshow(result["H"], origin="lower", extent=np.log10(limits))
+        plt.xlabel("log10(T_0)")
+        plt.ylabel("log10(T_1)")
+        plt.title("H")
+        plt.show()
+
+    return {"ln_Z": ln_Z, "H": H}
+
+
+
+

### 2018-05-31 python/twinpeaks2018/canonical.py
Bugfix and moved some things around

@@ -18,8 +18,8 @@ def load_particles_info():
     returns whatever it's got).
     """
 
-    particles_info = pd.read_csv("particles_info.csv")
-    completed_reps = np.loadtxt("completed_reps.txt")
+    particles_info = pd.read_csv("output/particles_info.csv")
+    completed_reps = np.loadtxt("output/completed_reps.txt")
 
     if len(completed_reps) == 0:
         print("There are no completed reps.")
@@ -59,7 +59,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     plt.xlabel(names[0])
     plt.ylabel(names[1])
 
-    plt.savefig("particle_scalars.png", dpi=600)
+    plt.savefig("output/particle_scalars.png", dpi=600)
     print("Saved particle_scalars.png")
     plt.show()
 
@@ -190,7 +190,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.ylabel("log10(T_1)")
     plt.title("Residuals")
 
-    plt.savefig("ln_Z_H.png", dpi=600)
+    plt.savefig("output/ln_Z_H.png", dpi=600)
     print("ln_Z_h.png")
     plt.show()
 
@@ -206,7 +206,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.xlabel("log10(T_0)")
     plt.ylabel("log10(T_1)")
     plt.title("<S_1>")
-    plt.savefig("expectations_of_scalars.png", dpi=600)
+    plt.savefig("output/expectations_of_scalars.png", dpi=600)
     print("Saved expectations_of_scalars.png")
     plt.show()
 

### 2018-05-31 python/twinpeaks2018/two_scalars_truth.py

@@ -24,7 +24,7 @@ def compute_truth(limits, n=51, plot=False):
 
             ln_y = -((x - 0.5)/0.1)**2 / T0[i, j] - \
                         (np.sin(10*np.pi*x))**2 / T1[i, j]
-            ln_Y = ln_y - logsumexp(ln_y)
+            ln_Y = ln_y - logsumexp(ln_y + np.log(dx))
             Y = np.exp(ln_Y)
 
             # Normalisation constant and KL divergence

### 2018-05-31 python/twinpeaks2018/canonical.py
Improved messages

@@ -60,7 +60,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     plt.ylabel(names[1])
 
     plt.savefig("output/particle_scalars.png", dpi=600)
-    print("Saved particle_scalars.png")
+    print("Saved output/particle_scalars.png")
     plt.show()
 
     return h
@@ -191,7 +191,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.title("Residuals")
 
     plt.savefig("output/ln_Z_H.png", dpi=600)
-    print("ln_Z_h.png")
+    print("Saved output/ln_Z_h.png")
     plt.show()
 
     plt.figure(2)
@@ -207,7 +207,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     plt.ylabel("log10(T_1)")
     plt.title("<S_1>")
     plt.savefig("output/expectations_of_scalars.png", dpi=600)
-    print("Saved expectations_of_scalars.png")
+    print("Saved output/expectations_of_scalars.png")
     plt.show()
 
 

### 2018-05-31 python/twinpeaks2018/canonical.py
Tidied up many plots

@@ -56,15 +56,11 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     plt.plot(particles_info[names[0]][indices],
              particles_info[names[1]][indices],
              ".", alpha=0.2, markersize=1)
-    plt.xlabel(names[0])
-    plt.ylabel(names[1])
+    plt.xlabel("$S_{i}$".format(i=scalars[0]))
+    plt.ylabel("$S_{j}$".format(j=scalars[1]))
 
     plt.savefig("output/particle_scalars.png", dpi=600)
     print("Saved output/particle_scalars.png")
-    plt.show()
-
-    return h
-
 
 def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     """
@@ -123,7 +119,7 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
 #    indices = np.sort(np.array(indices))
 
 
-def evaluate_temperature_grid(particles_info, limits, n=51):
+def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     """
     Evaluate logZ and H on a temperature grid.
     """
@@ -165,47 +161,52 @@ def evaluate_temperature_grid(particles_info, limits, n=51):
     truth = compute_truth(limits, n)
 
     # Plot the results
-    plt.figure(1, figsize=(8, 8))
-    plt.subplot(2, 2, 1)
+    plt.figure(1, figsize=(9, 6))
+    plt.subplot(1, 2, 1)
     plt.imshow(ln_Z, origin="lower", extent=np.log10(limits))
-    plt.ylabel("log10(T_1)")
-    plt.title("ln_Z")
+    plt.xlabel(r"\log_{10}(T_0)")
+    plt.ylabel(r"\log_{10}(T_1)")
+    plt.title(r"$\ln_Z$")
 
-    plt.subplot(2, 2, 2)
+    plt.subplot(1, 2, 2)
     plt.imshow(H, origin="lower", extent=np.log10(limits))
-    plt.ylabel("log10(T_1)")
-    plt.title("H")
-
-    plt.subplot(2, 2, 3)
-    plt.imshow(ln_Z - truth["ln_Z"],
-               origin="lower", extent=np.log10(limits), cmap="coolwarm")
-    plt.xlabel("log10(T_0)")
-    plt.ylabel("log10(T_1)")
-    plt.title("Residuals")
-
[…]

### 2018-05-31 python/twinpeaks2018/canonical.py
More improvements to plotting

@@ -11,6 +11,11 @@ from twinpeaks2018.two_scalars_truth import compute_truth
 from twinpeaks2018.utils import logsumexp
 
 
+# Niceify plots
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.size"] = 16
+plt.rc("text", usetex=True)
+
 def load_particles_info():
     """
     Load all the particles_info file, and return a data frame containing
@@ -164,14 +169,14 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     plt.figure(1, figsize=(9, 6))
     plt.subplot(1, 2, 1)
     plt.imshow(ln_Z, origin="lower", extent=np.log10(limits))
-    plt.xlabel(r"\log_{10}(T_0)")
-    plt.ylabel(r"\log_{10}(T_1)")
-    plt.title(r"$\ln_Z$")
+    plt.xlabel("$\\log_{10}(T_0)$")
+    plt.ylabel("$\\log_{10}(T_1)$")
+    plt.title("$\\ln(Z)$")
 
     plt.subplot(1, 2, 2)
     plt.imshow(H, origin="lower", extent=np.log10(limits))
-    plt.xlabel(r"\log_{10}(T_0)")
-    plt.title(r"$H$")
+    plt.xlabel("$\\log_{10}(T_0)$")
+    plt.title("$H$")
 
     plt.savefig("output/ln_Z_H.png", dpi=600)
     print("Saved output/ln_Z_h.png")
@@ -182,15 +187,15 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
         plt.subplot(1, 2, 1)
         plt.imshow(ln_Z - truth["ln_Z"],
                    origin="lower", extent=np.log10(limits), cmap="coolwarm")
-        plt.xlabel(r"\log_{10}(T_0)")
-        plt.ylabel(r"\log_{10}(T_1)")
-        plt.title("ln(Z) Residuals")
+        plt.xlabel("$\\log_{10}(T_0)$")
+        plt.ylabel("$\\log_{10}(T_1)$")
+        plt.title("$\\ln(Z)$ Residuals")
 
         plt.subplot(1, 2, 2)
         plt.imshow(H - truth["H"],
                    origin="lower", extent=np.log10(limits), cmap="coolwarm")
-        plt.xlabel(r"\log_{10}(T_0)")
-        plt.title("H Residuals")
[…]

### 2018-05-31 include/SwitchSamplerImpl.h
run_id -> rep_id

@@ -313,7 +313,7 @@ void prepare_output_files()
     fout.open("output/particles_info.csv", std::ios::out);
 
     // Column names
-    std::vector<std::string> header = {"run_id", "iteration",
+    std::vector<std::string> header = {"rep_id", "iteration",
                                        "ln_prior_mass"};
     for(size_t i=0; i<T::num_scalars; ++i)
     {

### 2018-05-31 python/twinpeaks2018/canonical.py

@@ -35,7 +35,7 @@ def load_particles_info():
     # Mark completed reps for keeping
     keep = np.zeros(particles_info.shape[0], dtype="bool")
     for r in completed_reps:
-        keep[particles_info["run_id"] == r] = True
+        keep[particles_info["rep_id"] == r] = True
     indices = np.nonzero(keep)[0]
     return particles_info.iloc[keep, :]
 
@@ -71,8 +71,8 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     """
     Obtain the properties of a single canonical distribution.
     """
-    rep_ids = np.arange(min(particles_info["run_id"]),
-                        max(particles_info["run_id"] + 1))
+    rep_ids = np.arange(min(particles_info["rep_id"]),
+                        max(particles_info["rep_id"] + 1))
 
     ln_w = particles_info["ln_prior_mass"]\
                    - logsumexp(particles_info["ln_prior_mass"])

### 2018-05-31 doc/ms.tex
Random writing

@@
 % Full title of the paper (Capitalized)
-\Title{Nested sampling with two objective functions}
+\Title{Nested Sampling with Multiple Objective Functions}
 
@@
 to accurately calculate $Z(\beta_1, \beta_2)$ numerically using non-Monte-Carlo
-methods.
-We show empirically how the accuracy of TwinPeaks
+methods. With this example, we empirically investigate the accuracy of TwinPeaks
 improves as a function of the number of particles used, $N$. We also
 calculate the partition function for a collection of atoms with a potential
-that is `intermediate' between a Lennard-Jones form and a polymer form.
+that is intermediate between a Lennard-Jones form and a `polymer' form.
 Finally, we present a Bayesian image reconstruction example,
 where we can infer the value of a hyperparameter even though its prior
-distribution contains an `intractable' normalizing constant.}
+distribution contains an `intractable' normalizing constant.
+An implementation in C++ is available at
+\url{https://github.com/eggplantbren/TwinPeaks2018}.}
 
 % Keywords: add 3 to 10 keywords
-\keyword{nested sampling; bayesian computation; statistical mechanics}
+\keyword{nested sampling; bayesian computation; statistical mechanics;
+         sequential monte carlo; multi-objective optimization}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setlength{\parskip}{0.7em}
 
@@
 $H$ quantifies how compressed the posterior distribution is with
-respect to the prior. For example, $H = 10$ implies (loosely speaking)
+respect to the prior. For example, $H = 10$ implies, loosely speaking,
 that the posterior occupies a fraction $e^{-10}$ of the prior mass.
 $H$ can be interpreted quite literally as a measure of how much
-the data $\data$ told you about $\xx$.
+the specific data $\data$ resolved the question ``what is the value
+of $\xx$, precisely?''.
 
@@
 based on `annealing' or `tempering', NS
-moves through a sequence of probability distributions beginning from the
-prior. This sequence of distributions is defined by
+moves through a sequence of probability distributions, beginning with the
+prior. It is the specific sequence of distributions used that distinguishes
+NS from annealing. The sequence of distributions used in NS is defined by
 \begin{eqnarray}
@@
 \end{eqnarray}
+\citet{salamone} recently showed how NS can be viewed as an instance of
+Sequential Monte Carlo (SMC), with a particular choice of the sequence of
+distributions.
+
 Throughout this paper we use the popular `overloaded' notation for some
@@
 For example, $L(\xx)$ is the likelihood function, and $L(X)$ is the likelihood
-as a function of the enclosed prior mass $X$. These cannot literally be the
-same function as the inputs typically don't have the same dimensionality
-($\xx$ is usually a collection of quantities and $X$ is a single real number
-in $[0, 1]$).
+as a function of the enclosed prior mass $X$. The inverse, $X(L)$, takes a
+likelihood as input and computes the corresponding enclosed prior mass.
 Therefore the symbol $L$ implies the output of the function is a
@@
 the parameters $\xx$, and $L(X)$ represents a likelihood value that
-corresponds to an amount $X$ of prior mass.
+corresponds to an amount $X$ of prior mass. In more traditional notation,
+$X(L)$ would be written using function composition, $X(L(\xx))$.
 
@@
 
-\section{Properties of Nested sampling}
+\section{Properties of Nested Sampling}
+What is special about the NS sequence of distributions?
+
+Consider the Nested Sampling measure, proportional to the amount of time
+NS spends in each region of the space. Since NS moves at a constant rate
+in terms of $\log(X)$, this measure is
+\begin{align}
+m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.
+\end{align}
 

### 2018-05-31 python/twinpeaks2018/canonical.py
Various improvements to the plots

@@ -163,8 +163,6 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
             print(".", end="", flush=True)
     print("")
 
-    truth = compute_truth(limits, n)
-
     # Plot the results
     plt.figure(1, figsize=(9, 6))
     plt.subplot(1, 2, 1)
@@ -183,6 +181,8 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     plt.show()
 
     if residuals:
+        truth = compute_truth(limits, n)
+
         plt.figure(2, figsize=(9, 6))
         plt.subplot(1, 2, 1)
         plt.imshow(ln_Z - truth["ln_Z"],
@@ -211,14 +211,14 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     plt.subplot(1, 2, 2)
     plt.imshow(S1, origin="lower", extent=np.log10(limits))
     plt.xlabel("$\\log_{10}(T_0)$")
-    plt.title("$<S_1>$")
+    plt.title("$\\left<S_1\\right>$")
     plt.savefig("output/expectations_of_scalars.png", dpi=600)
     print("Saved output/expectations_of_scalars.png")
     plt.show()
 
 
 
-def showresults():
+def showresults(limits=[0.1, 100.0, 0.1, 100.0], residuals=True):
     """
     This is what you'll usually want to call.
     """
@@ -239,6 +239,6 @@ def showresults():
     plot_particle_scalars(particles_info)
     plt.show()
 
-    evaluate_temperature_grid(particles_info, [0.1, 100.0, 0.1, 100.0],
-                              residuals=True)
+    evaluate_temperature_grid(particles_info, limits=limits,
+                              residuals=residuals)
 

### 2018-05-31 python/setup.py
Fixed warning

@@ -7,7 +7,6 @@ setuptools.setup(
     author_email="brendon.brewer@gmail.com",
     description="The Python package accompanying TwinPeaks2018",
     long_description="The Python package accompanying TwinPeaks2018",
-    long_description_content_type="text/markdown",
     url="https://github.com/eggplantbren/TwinPeaks2018",
     packages=setuptools.find_packages(),
     classifiers=(

### 2018-05-31 python/twinpeaks2018/canonical.py
Bugfix

@@ -142,8 +142,8 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     # Temperature grids
     T0 = 10.0**np.linspace(np.log10(T0_min),
                                         np.log10(T0_max), ln_Z.shape[0])
-    T1 = 10.0**np.linspace(np.log10(T0_min),
-                                        np.log10(T0_max), ln_Z.shape[1])
+    T1 = 10.0**np.linspace(np.log10(T1_min),
+                                        np.log10(T1_max), ln_Z.shape[1])
     [T0, T1] = np.meshgrid(T0, T1)
 
     # Compute over the grid

### 2018-05-31 python/twinpeaks2018/two_scalars_truth.py

@@ -14,8 +14,8 @@ def compute_truth(limits, n=51, plot=False):
     # Temperature grids
     T0 = 10.0**np.linspace(np.log10(T0_min),
                                         np.log10(T0_max), ln_Z.shape[0])
-    T1 = 10.0**np.linspace(np.log10(T0_min),
-                                        np.log10(T0_max), ln_Z.shape[1])
+    T1 = 10.0**np.linspace(np.log10(T1_min),
+                                        np.log10(T1_max), ln_Z.shape[1])
     [T0, T1] = np.meshgrid(T0, T1)
 
     # Compute over the grid

### 2018-05-31 python/twinpeaks2018/canonical.py
Nicer expectation symbol

@@ -206,7 +206,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     plt.imshow(S0, origin="lower", extent=np.log10(limits))
     plt.xlabel("$\\log_{10}(T_0)$")
     plt.ylabel("$\\log_{10}(T_1)$")
-    plt.title("$<S_0>$")
+    plt.title("$\\left<S_0\\right>$")
 
     plt.subplot(1, 2, 2)
     plt.imshow(S1, origin="lower", extent=np.log10(limits))

### 2018-05-31 examples/All.h
Rosenbrock

@@ -3,6 +3,7 @@
 
 #include "Atoms.h"
 #include "Potts.h"
+#include "Rosenbrock.h"
 #include "SpikeSlab.h"
 #include "TwoScalars.h"
 

### 2018-05-31 examples/Rosenbrock.cpp

@@ -1,0 +1,79 @@
+#include "Rosenbrock.h"
+#include "Utils.h"
+#include <iostream>
+#include <sstream>
+
+namespace TwinPeaks2018
+{
+
+Rosenbrock::Rosenbrock()
+:xs(N)
+{
+
+}
+
+void Rosenbrock::from_prior(RNG& rng)
+{
+    for(size_t i=0; i<xs.size(); i++)
+        xs[i] = -10.0 + 20.0*rng.rand();
+}
+
+double Rosenbrock::perturb(RNG& rng)
+{
+    int reps = 1;
+    if(rng.rand() < 0.5)
+        reps += static_cast<int>(pow(50.0, rng.rand()));
+
+    int which;
+    for(int i=0; i<reps; ++i)
+    {
+        which = rng.rand_int(xs.size());
+        xs[which] += 20.0*rng.randh();
+        wrap(xs[which], -10.0, 10.0);
+    }
+
+	return 0.0;
+}
+
+double Rosenbrock::log_likelihood() const
+{
+    double logL = 0.0;
+
+    for(size_t i=0; i<(xs.size()-1); ++i)
+    {
+        logL -= 100*pow(xs[i+1] - xs[i]*xs[i], 2);
+        logL -= pow(1.0 - xs[i], 2);
+    }
+
+    logL *= 2;
+
+    return logL;
+}
+
+std::vector<double> Rosenbrock::scalars() const
+{
+    double value = log_likelihood();
+    return {value/num_scalars, value/num_scalars};
+}
+
+
+std::ostream& operator << (std::ostream& out, const Rosenbrock& s)
+{
+    out << render(s.xs, false);
+    return out;
+}
+
+std::string Rosenbrock::description()
+{
+    std::vector<std::string> colnames;
+    for(size_t i=0; i<N; ++i)
+    {
+        std::stringstream ss;
+        ss << "xs[" << i << "]";
+        colnames.emplace_back(ss.str());
+    }
+    return render(colnames, false);
+}
+
+} // namespace TwinPeaks2018
+

### 2018-05-31 examples/Rosenbrock.h

@@ -1,0 +1,60 @@
+#ifndef TwinPeaks2018_Rosenbrock_h
+#define TwinPeaks2018_Rosenbrock_h
+
+#include "RNG.h"
+#include <ostream>
+#include <string>
+#include <vector>
+
+namespace TwinPeaks2018
+{
+
+/*
+* Show that if the two scalars are identical, you can obtain standard NS-SMC.
+* Let all the scalars be (log likelihood)/num_scalars, and use temperatures
+* of 1 for all scalars to get the posterior.
+*/
+class Rosenbrock
+{
+    // Number of scalars
+    public:
+        static constexpr size_t num_scalars = 2;
+
+    private:
+
+        // Dimensionality
+        static constexpr size_t N = 50;
+
+        // The coordinates
+        std::vector<double> xs;
+
+        // The log likelihood
+        double log_likelihood() const;
+
+    public:
+        // Constructor only gives size of params
+        Rosenbrock();
+
+        // Generate the point from the prior
+        void from_prior(TwinPeaks2018::RNG& rng);
+
+        // Metropolis-Hastings proposals
+        double perturb(TwinPeaks2018::RNG& rng);
+
+        // Scalars
+        std::vector<double> scalars() const;
+
+        // Return string with column information
+        static std::string description();
+
+        friend std::ostream& operator << (std::ostream& out,
+                                          const Rosenbrock& s);
+};
+
+std::ostream& operator << (std::ostream& out,
+                           const Rosenbrock& s);
+
+} // namespace TwinPeaks2018
+
+#endif
+

### 2018-05-31 python/twinpeaks2018/canonical.py
Try to improve a figure

@@ -57,15 +57,20 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     names = ["scalars[{i}]".format(i=scalars[0]),
              "scalars[{j}]".format(j=scalars[1])]
 
-    h = plt.figure()
+    plt.figure()
     plt.plot(particles_info[names[0]][indices],
              particles_info[names[1]][indices],
              ".", alpha=0.2, markersize=1)
     plt.xlabel("$S_{i}$".format(i=scalars[0]))
     plt.ylabel("$S_{j}$".format(j=scalars[1]))
+    x = np.sort(particles_info[names[0]][indices])
+    y = np.sort(particles_info[names[1]][indices])
+    plt.xlim([x[int(0.05*len(x))], x[-1]])
+    plt.ylim([y[int(0.05*len(y))], y[-1]])
 
     plt.savefig("output/particle_scalars.png", dpi=600)
     print("Saved output/particle_scalars.png")
+    plt.show()
 
 def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     """
@@ -237,8 +242,6 @@ def showresults(limits=[0.1, 100.0, 0.1, 100.0], residuals=True):
           "-216.865, and H is 129.017 nats.\n")
 
     plot_particle_scalars(particles_info)
-    plt.show()
-
     evaluate_temperature_grid(particles_info, limits=limits,
                               residuals=residuals)
 

### 2018-05-31 examples/SpikeSlab.cpp
Nice plot for one-scalar case

@@ -53,7 +53,7 @@ double SpikeSlab::log_likelihood() const
 std::vector<double> SpikeSlab::scalars() const
 {
     double value = log_likelihood();
-    return {value/num_scalars, value/num_scalars};
+    return { value };
 }
 
 

### 2018-05-31 examples/SpikeSlab.h

@@ -18,7 +18,7 @@ class SpikeSlab
 {
     // Number of scalars
     public:
-        static constexpr size_t num_scalars = 2;
+        static constexpr size_t num_scalars = 1;
 
     private:
 

### 2018-05-31 python/twinpeaks2018/one_scalar.py

@@ -1,0 +1,42 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from twinpeaks2018.canonical import *
+from twinpeaks2018.utils import *
+
+# Niceify plots
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.size"] = 16
+plt.rc("text", usetex=True)
+
+def postprocess_one_scalar(temperature=1.0):
+    """
+    Postprocessing for one scalar
+    """
+    particles_info = load_particles_info()
+    ln_w = particles_info["ln_prior_mass"]
+    ln_l = particles_info["scalars[0]"]
+
+    # Renormalise prior weights, calculate evidence
+    ln_w = ln_w - logsumexp(ln_w)
+    ln_Z = logsumexp(ln_w + ln_l/temperature)
+
+    # Posterior weights and information
+    ln_W = ln_w + ln_l - ln_Z
+    W = np.exp(ln_W)
+    H = np.sum(W*(ln_W - ln_w))
+
+    print("ln(Z) = {ln_Z}".format(ln_Z=ln_Z))
+    print("H = {H}".format(H=H))
+
+    plt.figure(figsize=(9, 7))
+    plt.subplot(2, 1, 1)
+    plt.plot(ln_w, ln_l, ".", markersize=1, alpha=0.3)
+    plt.ylabel("$\\ln(L)$")
+
+    plt.subplot(2,1,2)
+    plt.plot(ln_w, W/W.max(), ".", markersize=1, alpha=0.3)
+    plt.xlabel("$\\ln(w)$")
+    plt.ylabel("$W/W_{\\rm max}$")
+    plt.show()
+

### 2018-05-31 python/twinpeaks2018/__init__.py
Import modules

@@ -1,2 +1,7 @@
 name = "twinpeaks2018"
 
+from .canonical import *
+from .one_scalar import *
+from .two_scalars_truth import *
+from .utils import *
+

### 2018-05-31 python/twinpeaks2018/canonical.py
Handle length 1 case

@@ -24,7 +24,8 @@ def load_particles_info():
     """
 
     particles_info = pd.read_csv("output/particles_info.csv")
-    completed_reps = np.loadtxt("output/completed_reps.txt")
+    completed_reps = np.array([np.loadtxt("output/completed_reps.txt")])
+    completed_reps = completed_reps.flatten()
 
     if len(completed_reps) == 0:
         print("There are no completed reps.")

### 2018-05-31 python/twinpeaks2018/one_scalar.py
Save posterior weights

@@ -28,6 +28,7 @@ def postprocess_one_scalar(temperature=1.0):
 
     print("ln(Z) = {ln_Z}".format(ln_Z=ln_Z))
     print("H = {H}".format(H=H))
+    np.savetxt("output/posterior_weights.txt", W)
 
     plt.figure(figsize=(9, 7))
     plt.subplot(2, 1, 1)

### 2018-05-31 python/twinpeaks2018/__init__.py
Rearranged some of the python files

@@ -1,7 +1,6 @@
 name = "twinpeaks2018"
 
-from .canonical import *
 from .one_scalar import *
-from .two_scalars_truth import *
+from .two_scalars import *
 from .utils import *
 

### 2018-05-31 python/twinpeaks2018/two_scalars.py

@@ -7,38 +7,10 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.random as rng
 import pandas as pd
-from twinpeaks2018.two_scalars_truth import compute_truth
-from twinpeaks2018.utils import logsumexp
+from twinpeaks2018.example_truth import *
+from twinpeaks2018.utils import *
 
 
-# Niceify plots
-plt.rcParams["font.family"] = "serif"
-plt.rcParams["font.size"] = 16
-plt.rc("text", usetex=True)
-
-def load_particles_info():
-    """
-    Load all the particles_info file, and return a data frame containing
-    only complete runs (unless there aren't any, in which case it just
-    returns whatever it's got).
-    """
-
-    particles_info = pd.read_csv("output/particles_info.csv")
-    completed_reps = np.array([np.loadtxt("output/completed_reps.txt")])
-    completed_reps = completed_reps.flatten()
-
-    if len(completed_reps) == 0:
-        print("There are no completed reps.")
-        return particles_info
-
-    print("Found {n} completed reps.\n".format(n=len(completed_reps)))
-
-    # Mark completed reps for keeping
-    keep = np.zeros(particles_info.shape[0], dtype="bool")
-    for r in completed_reps:
-        keep[particles_info["rep_id"] == r] = True
-    indices = np.nonzero(keep)[0]
-    return particles_info.iloc[keep, :]
 
 
 def plot_particle_scalars(particles_info, scalars=[0, 1]):
@@ -224,7 +196,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
 
 
 
-def showresults(limits=[0.1, 100.0, 0.1, 100.0], residuals=True):
+def postprocess_two_scalars(limits=[0.1, 100.0, 0.1, 100.0], residuals=False):
     """
     This is what you'll usually want to call.
     """

### 2018-05-31 python/twinpeaks2018/utils.py

@@ -1,4 +1,6 @@
+import matplotlib.pyplot as plt
 import numpy as np
+import pandas as pd
 
 def logsumexp(values):
 	biggest = np.max(values)
@@ -6,3 +8,35 @@ def logsumexp(values):
 	result = np.log(np.sum(np.exp(x))) + biggest
 	return result
 
+
+def plot_settings():
+    """
+    Niceify plots
+    """
+    plt.rcParams["font.family"] = "serif"
+    plt.rcParams["font.size"] = 16
+    plt.rc("text", usetex=True)
+
+def load_particles_info():
+    """
+    Load all the particles_info file, and return a data frame containing
+    only complete runs (unless there aren't any, in which case it just
+    returns whatever it's got).
+    """
+
+    particles_info = pd.read_csv("output/particles_info.csv")
+    completed_reps = np.array([np.loadtxt("output/completed_reps.txt")])
+    completed_reps = completed_reps.flatten()
+
+    if len(completed_reps) == 0:
+        print("There are no completed reps.")
+        return particles_info
+
+    print("Found {n} completed reps.\n".format(n=len(completed_reps)))
+
+    # Mark completed reps for keeping
+    keep = np.zeros(particles_info.shape[0], dtype="bool")
+    for r in completed_reps:
+        keep[particles_info["rep_id"] == r] = True
+    indices = np.nonzero(keep)[0]
+    return particles_info.iloc[keep, :]

### 2018-05-31 showresults.py

@@ -1,3 +1,3 @@
-import twinpeaks2018.canonical
+import twinpeaks2018
 
-twinpeaks2018.canonical.showresults()
+twinpeaks2018.postprocess_two_scalars()

### 2018-05-31 python/twinpeaks2018/one_scalar.py
Extra work on plotting and saving

@@ -39,5 +39,7 @@ def postprocess_one_scalar(temperature=1.0):
     plt.plot(ln_w, W/W.max(), ".", markersize=1, alpha=0.3)
     plt.xlabel("$\\ln(w)$")
     plt.ylabel("$W/W_{\\rm max}$")
+    plt.savefig("output/likelihood_curve.png", dpi=600)
+    print("Saved output/likelihood_curve.png")
     plt.show()
 

### 2018-05-31 python/twinpeaks2018/two_scalars.py

@@ -45,7 +45,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     print("Saved output/particle_scalars.png")
     plt.show()
 
-def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
+def get_canonical(particles_info, temperatures=[1.0, 1.0], plot_and_save=False):
     """
     Obtain the properties of a single canonical distribution.
     """
@@ -62,44 +62,33 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot=False):
     ln_Z = logsumexp(ln_prod)
     ln_W = ln_prod - ln_Z
     W = np.exp(ln_W)
+    H = np.sum(W*(ln_s - ln_Z))
 
     result = {}
     result["ln_Z"] = ln_Z
     result["ln_W"] = ln_W
-    result["H"] = np.sum(W*(ln_s - ln_Z))
+    result["H"] = H
     result["ESS"] = np.exp(-np.sum(W*ln_W))
 
-    if plot:
-        plt.plot(logW)
+    if plot_and_save:
+        print("ln(Z) = {ln_Z}".format(ln_Z=ln_Z))
+        print("H = {H}".format(H=H))
+        np.savetxt("output/canonical_weights.txt", W)
+
+        plt.figure(figsize=(9, 7))
+        plt.subplot(2, 1, 1)
+        plt.plot(ln_w, ln_s, ".", markersize=1, alpha=0.2)
+        plt.ylabel("$\\ln(L)$")
+
+        plt.subplot(2,1,2)
+        plt.plot(ln_w, W/W.max(), ".", markersize=1, alpha=0.2)
+        plt.xlabel("$\\ln(w)$")
+        plt.ylabel("$W/W_{\\rm max}$")
+        plt.savefig("output/likelihood_curve.png", dpi=600)
+        print("Saved output/likelihood_curve.png")
         plt.show()
 
     return result
-
-
-#def create_canonical(particles_info,
-#                     result, outfile="../../output/canonical_particles.csv"):
-#    """
-#    Create and save samples from the canonical distribution.
-#    Argument: a dictionary as output by get_canonical().
-#    """
-#    ln_W = result["ln_W"]
-#    max_ln_W = np.max(ln_W)
-
-#    # Indices of particles
-#    indices = []
-#    attempts = 0
-#    while True:
-#        attempts += 1
-#        print(attempts)
-
[…]

### 2018-05-31 examples/All.h
Renamed example model to Demo

@@ -2,10 +2,10 @@
 #define TwinPeaks2018_All_h
 
 #include "Atoms.h"
+#include "Demo.h"
 #include "Potts.h"
 #include "Rosenbrock.h"
 #include "SpikeSlab.h"
-#include "TwoScalars.h"
 
 #endif
 

### 2018-05-31 examples/Demo.cpp

@@ -1,23 +1,23 @@
-#include "TwoScalars.h"
+#include "Demo.h"
 #include "Utils.h"
 #include <sstream>
 
 namespace TwinPeaks2018
 {
 
-TwoScalars::TwoScalars()
+Demo::Demo()
 :xs(N)
 {
 
 }
 
-void TwoScalars::from_prior(RNG& rng)
+void Demo::from_prior(RNG& rng)
 {
     for(size_t i=0; i<xs.size(); i++)
         xs[i] = rng.rand();
 }
 
-double TwoScalars::perturb(RNG& rng)
+double Demo::perturb(RNG& rng)
 {
     int which;
 
@@ -36,7 +36,7 @@ double TwoScalars::perturb(RNG& rng)
     return 0.0;
 }
 
-double TwoScalars::f() const
+double Demo::f() const
 {
     double result = 0.0;
     for(double x: xs)
@@ -44,7 +44,7 @@ double TwoScalars::f() const
     return result;
 }
 
-double TwoScalars::g() const
+double Demo::g() const
 {
     double result = 0.0;
     for(double x: xs)
@@ -52,19 +52,19 @@ double TwoScalars::g() const
     return result;
 }
 
-std::vector<double> TwoScalars::scalars() const
+std::vector<double> Demo::scalars() const
 {
     return {f(), g()};
 }
 
 
-std::ostream& operator << (std::ostream& out, const TwoScalars& s)
+std::ostream& operator << (std::ostream& out, const Demo& s)
 {
     out << render(s.xs, false);
     return out;
 }
 
-std::string TwoScalars::description()
+std::string Demo::description()
 {
     std::vector<std::string> colnames;
     for(size_t i=0; i<N; ++i)

### 2018-05-31 examples/Demo.h

@@ -1,5 +1,5 @@
-#ifndef TwinPeaks2018_TwoScalars_h
-#define TwinPeaks2018_TwoScalars_h
+#ifndef TwinPeaks2018_Demo_h
+#define TwinPeaks2018_Demo_h
 
 #include "RNG.h"
 #include <ostream>
@@ -9,7 +9,7 @@
 namespace TwinPeaks2018
 {
 
-class TwoScalars
+class Demo
 {
     // Number of scalars
     public:
@@ -29,7 +29,7 @@ class TwoScalars
 
     public:
         // Constructor only gives size of params
-        TwoScalars();
+        Demo();
 
         // Generate the point from the prior
         void from_prior(TwinPeaks2018::RNG& rng);
@@ -44,11 +44,11 @@ class TwoScalars
         static std::string description();
 
         friend std::ostream& operator << (std::ostream& out,
-                                          const TwoScalars& s);
+                                          const Demo& s);
 };
 
 std::ostream& operator << (std::ostream& out,
-                           const TwoScalars& s);
+                           const Demo& s);
 
 } // namespace TwinPeaks2018
 

### 2018-05-31 src/main.cpp

@@ -11,7 +11,7 @@ using namespace TwinPeaks2018;
 int main()
 {
     // Which example?
-    using Example = TwoScalars;
+    using Example = Demo;
 
     // Load the configuration
     Config::global_config.load("config.yaml");

### 2018-05-31 showresults.py
Helpful comments

@@ -1,3 +1,10 @@
 import twinpeaks2018
 
-twinpeaks2018.postprocess_two_scalars()
+# demo=True makes extra plots based on the ground truth of the demo model.
+# If you leave it in while using another model, you'll get some additional
+# output that will be spurious. You can just ignore it, though.
+twinpeaks2018.postprocess_two_scalars(demo=True)
+
+# One-scalar version
+# twinpeaks2018.postprocess_one_scalar()
+

### 2018-05-31 examples/Rosenbrock.cpp
Convert Rosenbrock to one-scalar model, which it is of course

@@ -53,7 +53,7 @@ double Rosenbrock::log_likelihood() const
 std::vector<double> Rosenbrock::scalars() const
 {
     double value = log_likelihood();
-    return {value/num_scalars, value/num_scalars};
+    return { value };
 }
 
 

### 2018-06-02 doc/ms.tex
Pose the question about the NS measure

@@
 
-\section{Properties of Nested Sampling}
+\section{Unique Properties of Nested Sampling}
 What is special about the NS sequence of distributions?
@@
 NS spends in each region of the space. Since NS moves at a constant rate
-in terms of $\log(X)$, this measure is
+in terms of $\log(X)$, this measure is proportional to
 \begin{align}
-m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.
+m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.\label{eqn:measure}
 \end{align}
+The sequence of dead particles emitted by NS is then used to compute properties
+of the posterior distribution, or other canonical distributions for temperatures
+other than 1. Why does this work? Why does the NS measure of
+Equation~\ref{eqn:ns_measure} allow the user to get a reasonable number of
+samples for {\em any} canonical distribution?
 

### 2018-06-02 doc/ms.tex
Partitoin functions keyword
Working on the abstract

@@
 \newcommand{\dx}{d\boldsymbol{\theta}}
-\newcommand{\data}{\boldsymbol{D}}
-\newcommand{\II}{\boldsymbol{I}}
+\newcommand{\data}{D}
+\newcommand{\II}{I}
 
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{We present a generalization of the Nested Sampling algorithm
+\abstract{We present a generalization of Skilling's Nested Sampling algorithm
 that estimates
@@
 occasionally in Bayesian inference.
-We demonstrate the algorithm on three example problems.
-The first is a toy problem whose structure allows us
+The algorithm is based on an interpretation of Nested Sampling in terms of
+Sequential Monte Carlo, which produces unbiased estimates of $Z$ and therefore
+allows parallel runs to be trivially combined.
+We demonstrate the algorithm on three example problems:
+(i)
+a toy problem whose structure allows us
 to accurately calculate $Z(\beta_1, \beta_2)$ numerically using non-Monte-Carlo
-methods. With this example, we empirically investigate the accuracy of TwinPeaks
-improves as a function of the number of particles used, $N$. We also
-calculate the partition function for a collection of atoms with a potential
-that is intermediate between a Lennard-Jones form and a `polymer' form.
-Finally, we present a Bayesian image reconstruction example,
-where we can infer the value of a hyperparameter even though its prior
-distribution contains an `intractable' normalizing constant.
-An implementation in C++ is available at
+methods, so we can compute the actual error in the reconstructed function
+$Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
+that is intermediate between a Lennard-Jones form and a `polymer' form; and
+(iii) A Bayesian image reconstruction example where the prior for the image
+is defined conditionally on a hyperparameter, but where this prior contains
+an intractable normalizing constant.
+A free software implementation in C++ and Python is available at
 \url{https://github.com/eggplantbren/TwinPeaks2018}.}
@@
 \keyword{nested sampling; bayesian computation; statistical mechanics;
+         partition functions;
          sequential monte carlo; multi-objective optimization}
@@
 by a vector $\xx$, the
-posterior distribution for the parameters given data $\data$ (and prior
+posterior distribution for the parameters given a data proposition $\data$ and
+a `prior information' proposition $\II$ is
 information $\II$) is:

### 2018-06-03 doc/template.tex
MDPI template update

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g. \documentclass[preprints,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, dairy, diseases, diversity, drones, econometrics, economies, education, electrochem, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medsci, medicina, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neonatalscreening, neuroglia, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, polysaccharides, proceedings, processes, proteomes, publications, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, sinusitis, smartcities, socsci, societies, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{1}
\pubyear{2018}
\copyrightyear{2018}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}

%\updates{yes} % If there is an update available, un-comment this line

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
%\simplesumm{}

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g. the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}. Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\begin{quote}
This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}

\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
\item	First item 
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=2 cm]{Definitions/logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
a + b = c
\end{equation}
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}
This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y. and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing—Original Draft Preparation, X.X.; Writing—Review \& Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.'', please turn to the \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Please add: ``This research received no external funding'' or ``This research was funded by [name of funder] grant number [xxx].'' Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g. materials used for experiments).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\reftitle{References}
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149, DOI.
% Reference 2
\bibitem[Author2(year)]{ref-book}
Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58, ISBN.
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2018-06-03 doc/template.tex
Moving stuff into the newer template

@@
 %=================================================================
-\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
+\documentclass[entropy,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Title}
+\Title{Nested Sampling with Multiple Objective Functions}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+\Author{Brendon J. Brewer$^{1,}$*,
+        Robert J. N. Baldock$^2$ and
+        Ewan Cameron$^3$}
 
 % Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+\AuthorNames{Brendon J. Brewer, Robert J. N. Baldock and Ewan Cameron}
 
@@
 \address{%
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+$^{1}$ \quad Department of Statistics, The University of Auckland, Private Bag 92019,
+Auckland 1142, New Zealand \\
+$^{2}$ \quad TBD \\
+$^{3}$ \quad TBD }
 
 % Contact information of the corresponding author
-\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}
+\corres{Correspondence: bj.brewer@auckland.ac.nz}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3} 
-\secondnote{These authors contributed equally to this work.}
+%\firstnote{Current address: Affiliation 3} 
+%\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+\abstract{We present a generalization of Skilling's Nested Sampling algorithm
+that estimates
+the partition function $Z(\beta_1, \beta_2)$ for a family of
+probability distributions indexed by two hyperparameters, $\beta_1$ and
+$\beta_2$. Problems like this arise frequently in statistical mechanics and
+occasionally in Bayesian inference.
+The algorithm is based on an interpretation of Nested Sampling in terms of
+Sequential Monte Carlo, which produces unbiased estimates of $Z$ and therefore
+allows parallel runs to be trivially combined.
+We demonstrate the algorithm on three example problems:
+(i)
+a toy problem whose structure allows us
+to accurately calculate $Z(\beta_1, \beta_2)$ numerically using non-Monte-Carlo
+methods, so we can compute the actual error in the reconstructed function
+$Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
+that is intermediate between a Lennard-Jones form and a `polymer' form; and
+(iii) A Bayesian image reconstruction example where the prior for the image
+is defined conditionally on a hyperparameter, but where this prior contains
+an intractable normalizing constant.
+A free software implementation in C++ and Python is available at
+\url{https://github.com/eggplantbren/TwinPeaks2018}.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}
+\keyword{nested sampling; bayesian computation; statistical mechanics;
+         partition functions;
+         sequential monte carlo; multi-objective optimization}
 

### 2018-06-03 doc/ms.tex
Moved to ms.tex

@@
 %  LaTeX support: latex@mdpi.com 
-%  In case you need support, please attach any log files that you could have, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+
+% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
 
 %=================================================================
+\documentclass[entropy,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
 
-% LaTeX Class File and Rendering Mode (choose one)
-% You will need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+\usepackage{dsfont}
 
-%=================================================================
+% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
+The document class line would be, e.g.
+\documentclass[preprints,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
 
-\documentclass[journal,article,accept,moreauthors,pdftex,12pt,a4paper]{mdpi}
+%
 %--------------------
@@
 % Choose between the following MDPI journals:
-% actuators, administrativesciences, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, appliedsciences, arts, atmosphere, atoms, axioms, batteries, behavioralsciences, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsciences, buildings, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, cosmetics, crystals, data, dentistryjournal, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, inorganics, insects, ijerph, ijfs, ijms, ijns, ijgi, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, joi, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, lubricants, machines, marinedrugs, materials, mathematics, medicalsciences, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, nanomaterials, ncrna, nutrients, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, sinusitis, socialsciences, societies, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, vaccines, veterinarysciences, viruses, water
+% acoustics, actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, dairy, diseases, diversity, drones, econometrics, economies, education, electrochem, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medsci, medicina, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neonatalscreening, neuroglia, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, polysaccharides, proceedings, processes, proteomes, publications, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, sinusitis, smartcities, socsci, societies, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj
 %---------
@@
 %---------
-% The default type of manuscript is article, but could be replaced by using one of the class options:
-% article, review, communication, commentary, bookreview, correction, addendum, editorial, changes, supfile, casereport, comment, conceptpaper, conferencereport, meetingreport, discussion, essay, letter, newbookreceived, opinion, projectreport, reply, retraction, shortnote, technicalnote, creative, datadescriptor (for journal Data), briefreport, hypothesis, interestingimage
+% The default type of manuscript is article, but can be replaced by: 
+% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
 %----------
@@
 the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
 Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-% Please insert a blank line is before and after all equation and eqnarray environments to ensure proper line numbering when option submit is chosen
 %------------------
@@
 %---------
-% The option "pdftex" is for use with pdfLaTeX only. If eps figure are used, use the optioin "dvipdfm", with LaTeX and dvi2pdf only.
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
 %=================================================================
-\setcounter{page}{1}
-\lastpage{x}
-\doinum{10.3390/------}
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
 \pubvolume{xx}
-\pubyear{2016}
-%\externaleditor{Academic Editor: xx}
-\history{Received: xx / Accepted: xx / Published: xx}
+\issuenum{1}
+\articlenumber{1}
+\pubyear{2018}
+\copyrightyear{2018}
+\externaleditor{Academic Editor: name}
+\history{Received: date; Accepted: date; Published: date}
 
-\usepackage[utf8]{inputenc}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{natbib}
-
-\DeclareUnicodeCharacter{00A0}{ }
-\newcommand{\xx}{\boldsymbol{\theta}}
-\newcommand{\dx}{d\boldsymbol{\theta}}
-\newcommand{\data}{D}
-\newcommand{\II}{I}
+%\updates{yes} % If there is an update available, un-comment this line
 
@@
 %=================================================================
-
-% Add packages and commands to include here
-% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are loaded by the MDPI class.
-%\usepackage{graphicx}
-%\usepackage{subfigure,psfig}
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
 
 %=================================================================
-%% Please use the following mathematics environments:
-% \theoremstyle{mdpi}
-% \newcounter{thm}
-% \setcounter{thm}{0}
-% \newcounter{ex}
-% \setcounter{ex}{0}
-% \newcounter{re}
-% \setcounter{re}{0}
-%
-% \newtheorem{Theorem}[thm]{Theorem}
-% \newtheorem{Lemma}[thm]{Lemma}
-% \newtheorem{Corollary}[thm]{Corollary}
-% \newtheorem{Proposition}[thm]{Proposition}
-%
-% \theoremstyle{mdpidefinition}
-% \newtheorem{Characterization}[thm]{Characterization}
-% \newtheorem{Property}[thm]{Property}
-% \newtheorem{Problem}[thm]{Problem}
-% \newtheorem{Example}[ex]{Example}
-% \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
-% \newtheorem{Remark}[re]{Remark}
-% \newtheorem{Definition}[thm]{Definition}
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
 %% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
@@
 %=================================================================
-
 % Full title of the paper (Capitalized)
@@
 
-% Authors (Add full first names)
+% Author Orchid ID: enter ID or remove command
+\newcommand{\xx}{\boldsymbol{\theta}}
+\newcommand{\dx}{d\boldsymbol{\theta}}
+\newcommand{\data}{D}
+\newcommand{\II}{I}
+
+%\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
 \Author{Brendon J. Brewer$^{1,}$*,
-        Robert J. N. Baldock$^{2}$,
-        Ewan Cameron$^{3}$}
+        Robert J. N. Baldock$^2$ and
+        Ewan Cameron$^3$}
+
+% Authors, for metadata in PDF
+\AuthorNames{Brendon J. Brewer, Robert J. N. Baldock and Ewan Cameron}
 
@@
 \address{%
-$^{1}$ Department of Statistics, The University of Auckland, Private Bag 92019,
+$^{1}$ \quad Department of Statistics, The University of Auckland, Private Bag 92019,
 Auckland 1142, New Zealand \\
-$^{2}$ Cavendish, University of Cambridge, Cambridge, UK \\
-$^{3}$ Spatial Ecology and Epidemiology Group, Tinbergen Building, Department
-of Zoology, University of Oxford, South Parks Road, Oxford, UK\\}
+$^{2}$ \quad TBD \\
+$^{3}$ \quad TBD }
 
-%\contributed{$^\dagger$ These authors contributed equally to this work.}
+% Contact information of the corresponding author
+\corres{Correspondence: bj.brewer@auckland.ac.nz}
 
-% Contact information of the corresponding author (Add [2] after \corres if there are more than one corresponding author.)
-\corres{{\tt bj.brewer@auckland.ac.nz}}
+% Current address and/or shared authorship
+%\firstnote{Current address: Affiliation 3} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
 
-% Abstract (Do not use inserted blank lines, i.e. \\)
+% Simple summary
+%\simplesumm{}
+
+% Abstract (Do not insert blank lines, i.e. \\) 
 \abstract{We present a generalization of Skilling's Nested Sampling algorithm
@@
 
-% Keywords: add 3 to 10 keywords
+% Keywords
 \keyword{nested sampling; bayesian computation; statistical mechanics;
@@
 % The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{}
+%\PACS{J0101}
 %\MSC{}
@@
 
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
-%\conference{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences:
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% For journal Data:
-
+% Only for the journal Data:
 %\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
@@
 In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+
 %\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
 
+%\setcounter{secnumdepth}{4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\setlength{\parskip}{0.7em}
+%\setcounter{section}{-1} %% Remove this when starting to work on the template.
+%\section{How to Use this Template}
+%The template details the sections that can be used in a manuscript.
+Note that the order and names of article sections may differ from the requirements of the journal (e.g.
+the positioning of the Materials and Methods section).
+Please check the instructions for authors page of the journal to verify the correct order and names.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
+%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
 
@@
 
-%\section{Rationale}\label{sec:rationale}
+%The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the principal conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+And now citing a book reference \cite{ref-book}.
+Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
+% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
 
-%Consider the following proposal, which we label the `turn-the-corner idea'.
-%Imagine running standard NS with $N$ particles
-%using the objective function $L_1(\xx)$.
-%After $M_1$ iterations, we'd be able to approximate
-%the function $X(\ell_1) = \int \pi(\xx) \, d\xx$
-%from $X\approx e^{-M_1/N}$ to $X=1$. Defining $Y=-\ln(X)$, we could also
-%construct an approximation to the function
-%$L_1(Y)$, a non-decreasing function of $Y$, from $Y=0$ to $Y\approx M_1/N$.
-%After $M$ iterations, we keep the last value of $L_1(\xx)$ obtained
-%(call it $L_1^*$), and continue to impose the constraint $L_1(\xx) > L_1^*$.
-
-%Subject to the constraint $L_1(\xx) > L_1^*$, standard NS can continue but
-%attempting to increase $L_2$ instead of $L_1$. This is what we mean by
-%`turning the corner'. After $M_2$ such iterations,
-%the algorithm would have compressed the prior by a factor
-%$e^{(M_1 + M_2)/N}$ and therefore ended at a point in the $(L_1, L_2)$ plane
-%where $X(L_1, L_2) \approx e^{-(M_1 + M_2)/N}$. Any such run consisting of
-%$M_1 + M_2$ iterations will therefore appoximately finish on a contour line
-%of the function $X(L_1, L_2)$.
-%We have explored the idea of using multiple turn-the-corner runs, with
-%the corner being turned at different times (i.e. using different values of
-%$M_1$), and combining the results using biased sampling
-%\citep{vardi, cameron} in order to estimate $Z(\beta_1, \beta_2)$. However,
-%this was very computationally intensive. We presented the turn-the-corner idea
-%here in order to provide an intuitive rationale for our actual algorithm given in
-%Section~\ref{sec:algorithm}.
-
-%Figure~\ref{fig:contours} shows the contour lines of $X(L_1, L_2)$ for the
-%prior in Figure~\ref{fig:joint1}. Each contour line encloses half of the
-%prior mass of the previous one. The fact that contours of $X(L_1, L_2)$ are
-%relevant suggests that a standard NS run with objective function
-%$X(L_1(\xx), L_2(\xx))$ would achieve a similar effect to the turn-the-corner
-%idea.
-
-%%\begin{figure}[ht!]
-%%\centering
-%%\includegraphics[scale=0.5]{figures/contours.pdf}
-%%\caption{\it The joint prior for the objective functions, and fifteen
-%%contours of the cumulative distribution $X(L_1, L_2)$, each enclosing half
-%%the prior mass of the previous one. \label{fig:contours}}
-%%\end{figure}
-
-%{\bf Try to relate this to \citet{vertical}}.
-
-%\section{Proposed algorithm}\label{sec:algorithm}
-
-%The basic idea of our algorithm is to try to mimic a standard NS run, where the
-%objective function being increased is
-%\begin{eqnarray}
-%Y(\xx) &=& 1/X\left(L_1(\xx), L_2(\xx)\right).
-%\end{eqnarray}
-%Standard NS cannot be applied simply because we cannot evaluate $X(L_1, L_2)$ and
-%therefore cannot restrict the parameter space based on the value of $X$ (or
-%equivalently, $Y$). However, given a number of Monte Carlo samples, we
-%can {\em approximate} $X$ by $\hat{X}(L_1, L_2)$, and restrict the parameter
-%space based on a contour of that approximation.
-%The algorithm is presented in detail below.
-
-%\begin{algorithm}[ht!]
-%\begin{algorithmic}
-%\State 1) Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
-%$N$ should quite large (typically 1000 or greater), and the algorithm is
-%slightly more elegant if $N$ is odd.
-%\State 2) Initialise the {\em remaining prior mass} to be $M=1$.
-%\State 3) Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
-%$\emptyset$.
-%\While{more iterations desired}
-%	\State i) Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
-%			and sort the $\hat{X}$ values observed.
-%	\State ii) Find the median $\hat{X}$ value, $\hat{X}_{(k)}$.
-%	\State iii) Classify all particles as either ``interior'', ``boundary'', or
-%			``exterior'', based on whether their $\hat{X}$ values are
-%			greater than, equal to, or less than $\hat{X}_{(k)}$ respectively.
-%	\State iv) If the number of interior particles $n_{\rm interior}$ or the number
-%			of exterior particles $n_{\rm exterior}$ is zero, replace $k$ by
-%			$(k-1)$ (to try a percentile other than the median)
-%			and go to step iii) (if $k=1$ then set $k=N$ instead of zero).
-%	\State v) Save all ``interior'' particles to disk, assigning each a prior weight of $n_{\rm interior}/(n_{\rm interior} + n_{\rm exterior})$.
-%	\State vi) Exclude the region in the $L_1$-$L_2$ plane where
-%$\hat{X} \geq \hat{X}_{(k)}$. That is, set
-%	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
-%	\State vii) Update the remaining prior mass to $M \leftarrow M n_{\rm exterior}/N$.
-%	\State viii) Replace all interior and boundary particles by new
-%			particles generated from $\pi(\xx)$, subject to the constraint
-%			of not being in the excluded region.
-%\EndWhile
-%\end{algorithmic}
-%\caption{\label{alg:algorithm}}
-%\end{algorithm}
-
-%Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=0.5]{figures/joint2.pdf}
-%\caption{\it The joint prior for the objective functions, and Monte Carlo
-%samples, as in Figure~\ref{fig:joint1}. The shaded region imposes a
-%constraint on the value of $\hat{X}$. Its boundary approximates a contour
-%of $X(L_1, L_2)$.
-%\label{fig:joint2}}
-%\end{figure}
-
-\section{Example 1: Known solution}
-We tested the algorithm on a simple 20-dimensional example, where the
-prior is a uniform distribution between 0 and 1 for each coordinate:
-\begin{eqnarray}
-\pi(\xx) &=& \prod_{i=1}^{20}
-\left\{
-\begin{array}{lr}
-1, & x_i \in [0, 1]\\
-0, & \textnormal{otherwise.}
-\end{array}
-\right.
-\end{eqnarray}
-The first objective function is quadratic in form, such that the canonical
-distribution is an iid gaussian centered at $(0.5, 0.5, ..., 0.5)$:
-\begin{eqnarray}
-L_1(\xx) &=& -\frac{1}{2} \sum_{i=1}^{20} \left(\frac{x_i - 0.5}{0.01}\right)^2.
-\end{eqnarray}
-
-The second objective function upweights states where coordinates $\{x_i\}$
-are close to 0, 0.25, 0.5, 0.75, or 1:
-\begin{eqnarray} 
-L_2(\xx) &=& -\sum_{i=1}^{100} \sin^2(4\pi x_i)
-\end{eqnarray}
-
-The true partition function (computed numerically) and the Kullback-Leibler
-divergence from the prior to the canonical distribution are shown in
-Figure~\ref{fig:truth} as a function of two temperatures.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=0.75]{figures/truth.pdf}
-%\caption{The true partition function and KL divergence (from the prior to
-%the canonical distribution) as a function of two temperatures for the
-%test problem.\label{fig:truth}}
-%\end{figure}
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=1]{figures/output.png}
-%\caption{The sequence of discarded particles (yellow) and
-%points representing the canonical distribution at temperatures
-%$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
-%\end{figure}
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=0.5]{figures/results.pdf}
-%\caption{Numerical results for the test problem. These compare well with the
-%true partition function and KL divergence given in Figure~\ref{fig:truth}.
-%\label{fig:results}}
-%\end{figure}
-
-\section{Example 2: Lennard-Jones/Polymer Example}
-
-Consider $n$ Lennard-Jones atoms confined to the unit cube $[0, 1]^3$.
-The position of each atom is given by a vector
-$\boldsymbol{r}_i = (x_i, y_i, z_i)$.
-The potential energy of any configuration of the atoms is given by
-a sum over all pairs of atoms:
-\begin{eqnarray}
-U_{\rm LJ} &=& \sum_{i=1}^n\sum_{j=(i+1)}^n U_{\rm LJ}
-(\boldsymbol{r}_i, \boldsymbol{r}_j)
-\end{eqnarray}
-where the inter-atomic potential energy is given by:
-
-\begin{eqnarray}
-U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)
-&=& 4\epsilon
-\left[
-\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^12 -
-\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^6
-\right].
-\end{eqnarray}
-We adopted the Lennard Jones units by setting $\epsilon=1$ and $\sigma=1$.
-
-In terms of the Lennard Jones parameters $\epsilon$ and $\sigma$, the
-``polymer'' potential is
-\begin{eqnarray}
-U_{\rm polymer} &=&
-\sum_{i=1}^{n-1} \phi^{(1)}_{i,i+1} + \sum_{i=2}^{n-1} \phi^{(2)}_{i-1, i, i+1}
-\end{eqnarray}
-where
-
-\begin{eqnarray}
-\phi^{(1)}_{i,i+1} &=& \frac{k}{2}\left(|\boldsymbol{r}_i - \boldsymbol{r}_{i+1}|- 2^{1/6}\sigma\right)^2,\\
-\phi^{(2)}_{i-1, i, i+1} &=& \frac{k}{2}
-\left((\boldsymbol{r}_i - \boldsymbol{r}_{i-1})\cdot(\boldsymbol{r}_{i-1} - \boldsymbol{r}_{i}) - 1\right)^2,
-\end{eqnarray}
-and $k=\frac{36 \times 2^{2/3}\epsilon}{\sigma^2}$ has been chosen to match
-the curvature of $U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)$.
-
-\section{Example 3: ``MaxEnt'' image deconvolution example}
-
-Problems with more than one objective function can also arise in data
-analysis. Consider, for example, the problem of deblurring a noisy
-image. A common approach to these problems is regularized inversion,
-such as the ``maximum entropy'' technique of \citet{gull}. It is important
-to distinguish between this method and the maximum entropy principle used
-to update or assign probabilities \citep{caticha}.
-
-The unknown parameters are a set of pixel intensities
-$\{x_i\}_{i=1}^n$ where $n$ is the number of pixels and $x_i \geq 0$.
-The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
-The prior for the dataset given the parameters is a normal distribution
-with mean given by the underlying image $\{xi\}$ convolved by
-a point spread function. The standard deviation of each pixel is
-$\sigma$, assumed known. This is usually written as
-
-\begin{eqnarray}
-\boldsymbol{D} = \boldsymbol{M}\boldsymbol{x} + \boldsymbol{n}
-\end{eqnarray}
-where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{M}$ is
-the blurring operator written in matrix form.
-
-The prior for the pixel intensities $\{x_i\}$ has an ``entropic'' form,
-where images are upweighted (relative to a uniform prior) if the pixel
-intensities have a low dynamic range. The prior density is defined conditional
-on a hyperparameter $\lambda$:
-\begin{eqnarray}
-p(\boldsymbol{x} | \lambda) &=&
-\frac{\exp\left[\lambda S(\xx)\right]}{\int \exp\left[\lambda S(\xx)\right] \, d\xx}
-\label{eq:entropy_prior}
-\end{eqnarray}
-where
-\begin{eqnarray}
-S(\xx) &=& -\sum_{i=1}^n x_i \ln x_i
-\end{eqnarray}
-is the ``configurational entropy'' of the image (crucially, this is a function of
-an image, and not a function of a probability distribution).
-The denominator in Equation~\ref{eq:entropy_prior} ensures the conditional prior
-is normalized.
-
-In the 1980s, this prior was thought to have a fundamental status, but this
-is no longer the case \citep{massinf}, although the function $S(\xx)$ does
-have special properties when its argument is a measure \citep{knuth_skilling}.
-However, it is still a prior whose
-consequences we might be interested in.
-
-Instead, we can consider the configurational
-entropy $S(\xx)$ as simply a function of an image that may
-be relevant somehow, and that we are uncertain about. The joint posterior
-for $\xx$ and $\lambda$ is:
-\begin{eqnarray}
-p(\lambda, \xx | \data) &=&
-\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
-{p(\data)}\\
-&=&
-\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
-{p(\data)}
-\end{eqnarray}
-
-The posterior for the underlying image given the data is
-\begin{eqnarray}
-p(\boldsymbol{x} | \boldsymbol{D}, \lambda)
-&=& \frac{p(\boldsymbol{x} | \lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda)}
-{\int p(\boldsymbol{x}|\lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda) \,d^n\boldsymbol{m}}\\
-&=& \frac{\exp\left[-\lambda \sum_i x_i\ln x_i
--\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]}
-{\int \exp\left[-\lambda \sum_i x_i\ln x_i
--\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]\, d^n\boldsymbol{m}}
-\end{eqnarray}
-
-This is a `doubly intractable' problem \citep{murray}, since an integral, whose
-result is a function of the parameters, appears in the {\em denominator} of the
-target density. However, in our case the integral in the
-denominator arises from the prior for the parameters, rather than from the
-likelihood function.
-
-\section{What kind of accuracy can we expect?}
-
-Imagine computing $Z(\beta_1, \beta_2)$ by looping over a grid of $\beta_2$
-values and doing an NS run with respect to $L_1$ for each. For each
-value of $\beta_1$ and $\beta_2$ that we're interested in, we can expect
-a (marginal) `one-sigma' accuracy in
-$\ln\left[Z(\beta_1, \beta_2)\right]$ of $\pm \sqrt{H(\beta_1, \beta_2)/N}$,
-for a computational cost proportional to...
-
-\section{What kind of accuracy do we need?}
-
-The following argument is due to John Skilling. Consider Bayesian model selection
-between two models $M_1$ and $M_2$. The Bayes Factor is the ratio of the
-two marginal likelihoods:
-\begin{eqnarray}
-B = \frac{P(D | M_1)}{P(D | M_2)} = \frac{Z_1}{Z_2}
-\end{eqnarray}
-where $Z_1 = \int \pi(\xx_1)L(\xx_1) \, d\xx_1$ and
-$Z_2 = \int \pi(\xx_2)L(\xx_2) \, d\xx_2$.
-In large problems, the log of the Bayes Factor is usually more convenient:
-\begin{eqnarray}
-\Delta := \ln B = \ln Z_1 - \ln Z_2.
-\end{eqnarray}
-Naively, we want $\Delta$ to an accuracy of about 0.1, so that we can reliably
-quantify the strength of the evidence when the two models are similarly
-supported by the data. But is this a realistic situation?
-
-Prior to knowing the data $D$, we don't know how much information we will get
-about the question of $M_1$ vs. $M_2$, quantified by the KL divergence:
-\begin{eqnarray}
-H &=& \sum_{i=1}^2 P(M_i | D)
-\ln\left[
-\frac{P(M_i | D)}{P(M_i)}
-\right].
-\end{eqnarray}
-
-The expected value of $H$ (with respect to the prior over datasets)
-is the mutual information:
-\begin{eqnarray}
-\mathcal{I} &=& \mathds{E}\left[H\right]\\
-&=&
-\sum_{i=1}^2 \int P(M_i, D)
-\ln\left[
-\frac{P(M_i, D)}{P(M_i)P(D)}
-\right] \, dD.
-\end{eqnarray}
-
-\section{Failure modes}\label{sec:failure_modes}
-
-If $L_1(\xx)$ and $L_2(\xx)$ are inversely and strongly dependent...
-
-%Use Skilling's argument about the prior distribution of a log Bayes factor.
-%Even though the performance of this algorithm won't be great for high $H$, it
-%will be good enough. I think the probability it won't give enough accuracy will
-%be ``exponentially small''.
-
-\acknowledgments{Acknowledgements}
-
-It is a pleasure to thank Rob Salamone (QUT),
-Gábor Csányi (Cambridge), Livia B. Pártay (Cambridge),
-and Will Handley (Cambridge) for valuable conversations.
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\begin{quote}
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\end{quote}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Subsection}
 
-\authorcontributions{Author Contributions}
+\subsubsection{Subsubsection}
 
-BJB initiated the project and explored various ideas which did not work.
-EC worked on the biased sampling suggestion in Section~\ref{sec:rationale},
-discovered the failure mode in Section~\ref{sec:failure_modes}, and was involved
-in many other discussions about the project. RB suggested the statistical
-mechanics example and helped BJB to get it working and to interpret the results.
+Bulleted lists look like this:
+\begin{itemize}[leftmargin=*,labelsep=5.8mm]
+\item	First bullet
+\item	Second bullet
+\item	Third bullet
+\end{itemize}
+
+Numbered lists can be added as follows:
+\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
+\item	First item 
+\item	Second item
+\item	Third item
+\end{enumerate}
+
+The text continues here.
+
+\subsection{Figures, Tables and Schemes}
+
+All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=2 cm]{Definitions/logo-mdpi}
+\caption{This is a figure, Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.}
+\end{figure}
+
+\begin{table}[H]
+\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
+\centering
+%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
+\begin{tabular}{ccc}
+\toprule
+\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+\midrule
+entry 1		& data			& data\\
+entry 2		& data			& data\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Formatting of Mathematical Components}
+
+This is an example of an equation:
+
+\begin{equation}
+a + b = c
+\end{equation}
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+
+Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%% Example of a theorem:
+\begin{Theorem}
+Example text of a theorem.
+\end{Theorem}
+
+The text continues here. Proofs must be formatted as follows:
+
+%% Example of a proof:
+\begin{proof}[Proof of Theorem 1]
+Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
+\end{proof}
+The text continues here.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
 
-\conflictofinterests{Conflicts of Interest}
-The authors declare no conflict of interest.
+Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 
-%=================================================================
-% References: Variant A
-%=================================================================
-% Back Matter (References and Notes)
-%----------------------------------------------------------
-% Style and layout of the references
-\bibliographystyle{mdpi}
-\makeatletter
-\renewcommand\@biblabel[1]{#1. }
-\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Materials and Methods}
+
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+
+Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
+
+Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Patents}
+This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following are available at \linksupplementary, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
+The following statements should be used ``Conceptualization, X.X.
+and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y.
+and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing—Original Draft Preparation, X.X.; Writing—Review \& Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.'', please turn to the \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
+Authorship must be limited to those who have contributed substantially to the work reported.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\funding{Please add: ``This research received no external funding'' or ``This research was funded by [name of funder] grant number [xxx].'' Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
+This may include administrative and technical support, or donations in kind (e.g.
+materials used for experiments).}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
+Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
+If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\abbreviations{The following abbreviations are used in this manuscript:\\
+
+\noindent 
+\begin{tabular}{@{}ll}
+MDPI & Multidisciplinary Digital Publishing Institute\\
+DOAJ & Directory of open access journals\\
+TLA & Three letter acronym\\
+LD & linear dichroism
+\end{tabular}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections.
+Then a counter is printed ("Appendix A").
+If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
+\appendix
+\section{}
+\subsection{}
+The appendix is an optional section that can contain details and data supplemental to the main text.
+For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
+Mathematical proofs of results not central to the paper can be added as an appendix.
+
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%=====================================
+% References, variant A: internal bibliography
+%=====================================
+\reftitle{References}
 
@@
 
-%=================================================================
-% References:  Variant B
-%=================================================================
-% Use the following option to include external BibTeX files:
-%\bibliography{lite}
-%\bibliographystyle{mdpi}
+% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%=====================================
+% References, variant B: external bibliography
+%=====================================
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\sampleavailability{Samples of the compounds ...... are available from the authors.}
 
-%\abbreviations{Abbreviations/Nomenclature}
-%
-%Main text.
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\appendix
-%\section{Appendix 1: Fast computation of upper corner counts}
-%The upper corner count of particle $i$ is defined as the value of
-%$\hat{X}$ at the position of particle $i$. Less formally, it is the number
-%of other particles that are `up and to the right' of particle $i$ in
-%a plot like Figure~\ref{fig:joint1}, plus one.
-
-%\begin{eqnarray}
-%C_i &=& \sum_{j=1}^N
-%\mathds{1}\left[L_1(\xx_j) \geq L_1(\xx_i), L_2(\xx_j) \geq L_2(\xx_i)\right]\\
-%&=& \sum_{j=1}^N
-%\mathds{1}\left[L_1(\xx_j) \geq L_1(\xx_i)\right]
-%\mathds{1}\left[L_2(\xx_j) \geq L_2(\xx_i)\right]
-%\end{eqnarray}
-
 \end{document}

### 2018-06-03 doc/ms.tex
References

@@
 
-Nested Sampling \citep[NS][]{skilling} is popular general
+Nested Sampling \citep[NS][]{skilling} is general
 Monte Carlo algorithm that can solve a wide range of problems in Bayesian
@@
 \citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
-Its key strength its ability to cope with phase transitions which cause
-problems for many other methods \citep{skilling}.
+Its key strength its ability to cope with phase transitions and other
+features which cause
+problems for many other methods.
 In a Bayesian inference problem with unknown parameters denoted collectively
@@
 posterior distribution for the parameters given a data proposition $\data$ and
-a `prior information' proposition $\II$ is
-information $\II$) is:
+a `prior information' proposition $\II$ is:
 \begin{eqnarray}
@@
 where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
-function, and $Z$ is the normalising constant, usually known as the
-`marginal likelihood' or the `evidence':
+function, and $Z$ is the normalising constant, known as the
+`marginal likelihood' or `evidence':
 \begin{eqnarray}
@@
 
-$Z$ is useful because it is the (prior) probability of the data given that
-$\xx$ is {\em one of}
-the possibilities in the space being integrated over, and thus plays the role
-of a likelihood for the parameter space as a whole.
-The main goal of NS is to approximate $Z$, but it can also be used to make
+$Z$ is useful because it is the prior probability of the data conditional on
+the hypothesis that $\xx$ is {\em one of}
+the possibilities in the space being integrated over, along with
+whatever additional assumptions were made. $Z$ thus plays the role
+of a likelihood for the parameter space as a whole, and is a key input in
+calculating the posterior probabilities of competing `models' (mutually
+exclusive choices of $\II$).
+
+The main goal of NS is to compute $Z$, but it can also be used to make
 Monte Carlo approximations of the posterior distribution, and to
@@
 \begin{eqnarray}
-H &=& \int p(\xx | \data, \II) \ln
-\left[\frac{p(\xx | \data, \II)}{p(\xx | \II)}\right] \, d\xx \\
-&=& \int \frac{\pi(\xx) L(\xx)}{Z} \ln
-\left[\frac{L(\xx)}{Z}\right] \, d\xx.
+H &=& \int p(\xx | \data, \II) \log
+\left(\frac{p(\xx | \data, \II)}{p(\xx | \II)}\right) \, d\xx \\
+&=& \int \frac{\pi(\xx) L(\xx)}{Z} \log
+\left(\frac{L(\xx)}{Z}\right) \, d\xx.
 \end{eqnarray}
 $H$ quantifies how compressed the posterior distribution is with
-respect to the prior. For example, $H = 10$ implies, loosely speaking,
-that the posterior occupies a fraction $e^{-10}$ of the prior mass.
+respect to the prior. For example, $H = 100$ nats (the units obtained when
+the logarithm is the natural logarithm) implies, loosely speaking,
+that the posterior occupies a fraction $e^{-100}$ of the prior mass.
 $H$ can be interpreted quite literally as a measure of how much
 the specific data $\data$ resolved the question ``what is the value
-of $\xx$, precisely?''.
+of $\xx$, precisely?'' \citep{knuth, van_erp}.
 
@@
 
-\begin{thebibliography}{999} % if there are less than 10 entries, enter a one digit number
-
-\bibitem[Baldock et al.(2015)]{2015arXiv150303404B} Baldock, R.~J.~N., 
-P{\'a}rtay, L.~v.~B., Bart{\'o}k, A.~P., Payne, M.~C., Cs{\'a}nyi, G.\ 
-2015.\ Determining pressure-temperature phase diagrams of materials.\ ArXiv 
-e-prints arXiv: 1503.03404.
-
-\bibitem[Brewer and Donovan(2015)]{exoplanet} Brewer, B.~J., 
-Donovan, C.~P.\ 2015.\ Fast Bayesian inference for exoplanet discovery in 
-radial velocity data.\ Monthly Notices of the Royal Astronomical Society 
-448, 3206-3214.
-
-\bibitem[Brewer(2014)]{rjobject} Brewer, B.~J.\ 2014.\ Inference 
-for Trans-dimensional Bayesian Models with Diffusive Nested Sampling.\ 
-ArXiv e-prints arXiv:1411.3921.
-
-\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
-\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
-Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
-
-\bibitem[Cameron and Pettitt(2014)]{cameron} Cameron, E., and Pettitt, A., 2014,
-``Recursive pathways to marginal likelihood estimation with
-prior-sensitivity analysis.'' Statistical Science 29.3 (2014): 397-419.
-
-\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
-on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
-arXiv:0808.0012.
-
-\bibitem[\protect\citeauthoryear{Gregory}{2005}]{gregory}
-Gregory, Phil. Bayesian Logical Data Analysis for the Physical Sciences: A Comparative Approach with Mathematica® Support. Cambridge University Press, 2005.
-
-\bibitem[Gull and Daniell(1978)]{gull} Gull, Stephen F., and Daniell, G., 1978
-Image reconstruction from incomplete and noisy data. Nature (1978): 686-690.
-
-\bibitem[Hansmann(1997)]{pt} Hansmann, Ulrich HE., 1997, ``Parallel tempering algorithm for conformational studies of biological molecules.'', Chemical Physics Letters 281, no. 1 (1997): 140-150.
-
-\bibitem[Knuth and Skilling(2010)]{knuth_skilling} Knuth, K.~H., 
-Skilling, J.\ 2010.\ Foundations of Inference.\
-Axioms 1.1 (2012): 38-73.\
-ArXiv e-prints arXiv:1008.4831.
-
-\bibitem[Murray(2012)]{murray} Murray, Iain, Ghahramani, Zoubin, and MacKay, David.
-``MCMC for doubly-intractable distributions.'' arXiv preprint arXiv:1206.6848 (2012).
-
-\bibitem[P{\'a}rtay et al.(2014)]{2014PhRvE..89b2302P} P{\'a}rtay, L.~B., 
-Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2014.\ Nested sampling for materials: 
-The case of hard spheres.\ Physical Review E 89, 022302.
-
-\bibitem[P{\'a}rtay et al.(2009)]{2009arXiv0906.3544P} P{\'a}rtay, L.~B., 
-Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2009.\ Efficient sampling of atomic 
-configurational spaces.\ ArXiv e-prints arXiv: 0906.3544.
-
-\bibitem[Polson and Scott(2014)]{vertical}
-Polson, Nicholas G., and James G. Scott. ``Vertical-likelihood Monte Carlo
-Integration.'' arXiv preprint arXiv:1409.3601 (2014).
-
-\bibitem[\protect\citeauthoryear{Skilling}{1998}]{massinf}
-Skilling J., 1998, Massive Inference and Maximum Entropy, in Maximum Entropy
-and Bayesian Methods, Kluwer Academic Publishers, Dordrecht/Boston/London p.14
-
-\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, J., 2006, Nested Sampling for General Bayesian Computation, Bayesian Analysis 4, pp. 833-860.
-
-\bibitem[Vardi (1985)]{vardi}
-Vardi, Yehuda. ``Empirical distributions in selection bias models.'', The Annals of Statistics (1985): 178-203.
-
-\bibitem[Walter(2015)]{walter}
-Walter, C.\ Point Process-based Monte Carlo estimation.\ arXiv: 1412.6368.
-%% Reference 1
-%\bibitem{ref-journal}
-%Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-
-%% Reference 2
-%\bibitem{ref-book}
-%Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-
-\end{thebibliography}
+\bibliographystyle{mdpi}
+\bibliography{references/references}
 

### 2018-06-03 doc/ms.tex
putting citations in

@@
 \newcommand{\II}{I}
+\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
 
@@
 
-Nested Sampling \citep[NS][]{skilling} is general
+Nested Sampling \citep[NS][]{skilling2006nested} is general
 Monte Carlo algorithm that can solve a wide range of problems in Bayesian
 computation and statistical mechanics
-\citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
+\citep[e.g.][]{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
 Its key strength its ability to cope with phase transitions and other
@@
 the specific data $\data$ resolved the question ``what is the value
-of $\xx$, precisely?'' \citep{knuth, van_erp}.
+of $\xx$, precisely?'' \citep{knuth_questions, van_erp}.
 
@@
 single objective function. The same is true of variants such as
-Diffusive Nested Sampling \citep{dnest}.
+Diffusive Nested Sampling \citep{dns, dnest4}.
 
@@
 
-\bibliographystyle{mdpi}
-\bibliography{references/references}
+%\bibliographystyle{mdpi}
+\bibliography{references.bib/references}
 

### 2018-06-03 doc/ms.tex
van erp

@@
 
-Nested Sampling \citep[NS][]{skilling2006nested} is general
+Nested Sampling (NS) \citep{skilling2006nested} is general
 Monte Carlo algorithm that can solve a wide range of problems in Bayesian
@@
 the specific data $\data$ resolved the question ``what is the value
-of $\xx$, precisely?'' \citep{knuth_questions, van_erp}.
+of $\xx$, precisely?'' \citep{knuth_questions, van2017inquiry}.
 

### 2018-06-03 doc/ms.tex
Salomone
fix

@@
 \end{eqnarray}
-\citet{salamone} recently showed how NS can be viewed as an instance of
+\citet{salomone2018unbiased}
+recently showed how NS can be viewed as an instance of
 Sequential Monte Carlo (SMC), with a particular choice of the sequence of
@@
 Diffusive Nested Sampling \citep{dns, dnest4}.
+
+Sequential Monte Carlo \citep{salomone2018unbiased}
 

### 2018-06-03 doc/ms.tex
Fixed a few references
Working on the intro

@@
 
+\setlength{\parskip}{0.6em}
+
 \section{Introduction}
@@
 Monte Carlo algorithm that can solve a wide range of problems in Bayesian
-computation and statistical mechanics
-\citep[e.g.][]{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
+computation, statistical mechanics, and information theory
+\citep[e.g.][]{partay2010efficient, exoplanet, baldock2016determining,
+brewer2017computing}.
 Its key strength its ability to cope with phase transitions and other
-features which cause
-problems for many other methods.
+features which cause problems for many other methods such as those based
+on `annealing' \citep{neal2001annealed}. These methods all fall into that half
+of the Monte Carlo landscape that addresses {\em what distribution to sample}
+rather than how to sample it.
+
 In a Bayesian inference problem with unknown parameters denoted collectively
@@
 exclusive choices of $\II$).
+Naively, Equation~\ref{eqn:evidence} appears straightforward to compute because
+it is a simple expectation of $L$ with respect to the distribution $\pi$.
+However,
+NS is required because Equation~\ref{eqn:evidence}
+is the expected value of $L$ with respect to a very heavy-tailed distribution
+(the distribution of $L$-values implied by $\pi(\xx)$). This means a very
+large number of samples would be required.
+Hence, there is a strong
+connection between NS and ideas from rare event simulation.
+\citet{walter2017point} has explicitly explored this connection.
+Another way of thinking about this
+challenge is that the $Z$ integral is dominated by a region with very
+high values of $L$ but very low probability according to $\pi$ (and usually
+very low volume according to $d\xx$, as well).
 
@@
 of $\xx$, precisely?'' \citep{knuth_questions, van2017inquiry}.
+\citet{brewer2017computing} introduced a variant of NS that computes
+Shannon entropies.
 
@@
 $X(L)$ would be written using function composition, $X(L(\xx))$.
-
-Naively, Equation~\ref{eqn:evidence} appears straightforward to compute because
-it is a simple expectation of $L$ with respect to the distribution $\pi$.
-However,
-NS is required because Equation~\ref{eqn:evidence}
-is the expected value of $L$ with respect to a very heavy-tailed distribution
-(the prior for the $L$ value implied by $\pi(\xx)$). Hence, there is a strong
-connection between NS and ideas from rare event simulation. \citet{walter} has
-explicitly explored this connection.
 

### 2018-06-03 doc/ms.tex
More work

@@
 
-\section{Introduction}
+\section{Nested Sampling}
 
@@
 \citet{brewer2017computing} introduced a variant of NS that computes
-Shannon entropies.
+Shannon entropies, including entropies of marginal distributions (whereas
+standard NS can only compute divergences for full joint distributions).
 
@@
 \end{eqnarray}
-and the marginal likelihood can be computed by numerically integrating the
+where $X(\ell) = \int \pi(\xx)\mathds{1}\left(L(\xx) > \ell\right)$ is the
+normalising constant of the distribution constrained by the condition
+$L(\xx) > \ell)$. $X$ is also the quantile function of the likelihoods.
+
+The marginal likelihood can be computed by numerically integrating the
 function $L(X)$:
@@
 Sequential Monte Carlo (SMC), with a particular choice of the sequence of
-distributions.
+distributions. By weighting the sequence of discarded points differently from
+Skilling, the estimates of $Z$ are unbiased.
 
-Throughout this paper we use the popular `overloaded' notation for some
-functions and probability distributions.
-For example, $L(\xx)$ is the likelihood function, and $L(X)$ is the likelihood
-as a function of the enclosed prior mass $X$. The inverse, $X(L)$, takes a
-likelihood as input and computes the corresponding enclosed prior mass.
-Therefore the symbol $L$ implies the output of the function is a
-likelihood value; so $L(\xx)$ represents a likelihood value computed from
-the parameters $\xx$, and $L(X)$ represents a likelihood value that
-corresponds to an amount $X$ of prior mass. In more traditional notation,
-$X(L)$ would be written using function composition, $X(L(\xx))$.
+%Throughout this paper we use the popular `overloaded' notation for some
+%functions and probability distributions.
+%For example, $L(\xx)$ is the likelihood function, and $L(X)$ is the likelihood
+%as a function of the enclosed prior mass $X$. The inverse, $X(L)$, takes a
+%likelihood as input and computes the corresponding enclosed prior mass.
+%Therefore the symbol $L$ implies the output of the function is a
+%likelihood value; so $L(\xx)$ represents a likelihood value computed from
+%the parameters $\xx$, and $L(X)$ represents a likelihood value that
+%corresponds to an amount $X$ of prior mass. In more traditional notation,
+%$X(L)$ would be written using function composition, $X(L(\xx))$.
 
-Using a single NS run, we can also calculate the properties of any other distribution that
+\section{Accessing distributions other than the posterior}
+Using a single NS run, we can also calculate the properties of any
+distribution that
 is (in some sense which we do not make precise) {\em intermediate}
@@
 \begin{eqnarray}
-p(\xx; \beta) &=& \frac{\pi(\xx)L(\xx)^\beta}{Z(\beta)}\label{eqn:power_posterior}
+p(\xx; \beta) &=& \frac{\pi(\xx)L(\xx)^\beta}
+                       {Z(\beta)}\label{eqn:power_posterior}
 \end{eqnarray}
@@
 compute $Z(\beta)$ as a function of $\beta$, which is called the
-{\it partition function}. The quantity $\mathcal{I}(\beta)$ is, up to a sign
-change and an additive constant, the Gibbs entropy.
-NS can achieve this, allowing the study of
+{\it partition function}. When the full phase space of positions and momenta
+is included, the KL-divergence as a function of temperature,
+$H(\beta)$, is the Gibbs entropy (up to a sign change and a constant factor).
+A single run of NS can be used to reconstruct $Z(\beta)$ and $H(\beta)$,
+allowing the study of
 the properties of materials from first principles, based on hypotheses about
-the atoms or molecules that make them up \citep[e.g.][]{2009arXiv0906.3544P,
-2014PhRvE..89b2302P, 2015arXiv150303404B}. The NS algorithm is invariant under
+the atoms or molecules that make them up
+\citep[e.g.][]{partay2010efficient, baldock2016determining}.
+The NS exploration algorithm is invariant under
 monotonic transformations of $L$ or $E$ and therefore there we can discuss the
@@
 
+\section{Multiple objective functions}
 In some inference and

### 2018-06-03 doc/ms.tex
Working my way through the introduction still

@@
 we obtain information that fixes the expected values of two scalar
-functions of $\xx$, $L_1(\xx)$ and $L_2(\xx)$.
-It is well known that the
+``likelihood'' functions of $\xx$, $L_1(\xx)$ and $L_2(\xx)$
+(or equivalently, ``energy'' functions $E_1(\xx) = -\ln L_1(\xx)$ and
+$E_2 = -\ln L_2(\xx)$). The
 updated probability distribution that takes into account the constraints is
-of the canonical form:
-\begin{eqnarray}
-p(\xx; \beta_1, \beta_2) &=& \frac{\pi(\xx)\exp\left[\beta_1L_1(\xx)+\beta_2L_2(\xx)\right]}
+of the canonical form \citep{jaynes1957information}:
+\begin{align}
+p(\xx; \beta_1, \beta_2) &=
+    \frac{\pi(\xx)L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}}
+         {Z(\beta_1, \beta_2)} \\
+    &=
+    \frac{\pi(\xx)\exp\left[-\beta_1E_1(\xx) - \beta_2E_2(\xx)\right]}
          {Z(\beta_1, \beta_2)}
-\end{eqnarray}
+\end{align}
 where $\beta_1$ and $\beta_2$ are two `inverse temperatures' (the temperatures
@@
 given two datasets, where $L_1$ and $L_2$ are the
-likelihood functions for each dataset. In statistical mechanics, $L_1$ might
-be $\exp\left(-\textnormal{energy}\right)$ and $L_2$ might be the total
-angular momentum, or be a term depending on an external field (so $\beta_2$
+likelihood functions for each dataset. In statistical mechanics, $E_1$ might
+be the total energy and $E_2$ might be the total
+angular momentum, or perhaps a term depending on an external field (so $\beta_2$
 would then describe the strength of the external field).
@@
 constant and by running standard Nested Sampling with objective function
-$L(\xx) = \exp\left[0.3L_1(\xx) + 0.7L_2(\xx)\right]$. However, usually we
+$L(\xx) = L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}$. However, usually we
 are interested in a range of values for $\beta_1$ and $\beta_2$, and we
@@
 of Nested Sampling, such as the ability to cope with first-order phase
-transitions. The algorithm is designed for problems with two objective
-functions, but may generalize to problems with more than two (though perhaps
-not more than a few).
+transitions. The algorithm is presented here for problems with two objective
+functions, but the implementation allows for more than two (though the
+performance is those cases is likely to be poor).
+
+\
 

### 2018-06-03 doc/ms.tex
Pasted example text in, edited example 1

@@
 
+\section{Example 1: Known solution}
+In the software repository, this example is implemented in
+{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
+We tested the algorithm on a simple 100-dimensional example, where the
+prior is a uniform distribution between 0 and 1 for each coordinate:
+\begin{eqnarray}
+\pi(\xx) &=& \prod_{i=1}^{100}
+\left\{
+\begin{array}{lr}
+1, & x_i \in [0, 1]\\
+0, & \textnormal{otherwise.}
+\end{array}
+\right.
+\end{eqnarray}
+The first objective function is quadratic in form, such that the canonical
+distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
+\begin{eqnarray}
+E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
+\end{eqnarray}
+The second objective function, given by
+\begin{eqnarray} 
+E_2(\xx) &=& \sin^2(10 \pi x_i),
+\end{eqnarray}
+upweights states where coordinates $\{x_i\}$
+are close to 0, 0.1, 0.2, ..., 0.9 and 1.
+The canonical distributions for this system should draw the coordinates
+towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
+relative importance of these effects determined by the values of the
+inverse temperatures $\beta_1$ and $\beta_2$.
+
+The true partition function (computed numerically) and the Kullback-Leibler
+divergence from the prior to the canonical distribution are shown in
+Figure~\ref{fig:truth} as a function of two temperatures.
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.75]{figures/truth.pdf}
+%\caption{The true partition function and KL divergence (from the prior to
+%the canonical distribution) as a function of two temperatures for the
+%test problem.\label{fig:truth}}
+%\end{figure}
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{figures/output.png}
+%\caption{The sequence of discarded particles (yellow) and
+%points representing the canonical distribution at temperatures
+%$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
+%\end{figure}
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.5]{figures/results.pdf}
+%\caption{Numerical results for the test problem. These compare well with the
+%true partition function and KL divergence given in Figure~\ref{fig:truth}.
+%\label{fig:results}}
+%\end{figure}
+
+\section{Example 2: Lennard-Jones/Polymer Example}
+
+Consider $n$ Lennard-Jones atoms confined to the unit cube $[0, 1]^3$.
+The position of each atom is given by a vector
+$\boldsymbol{r}_i = (x_i, y_i, z_i)$.
+The potential energy of any configuration of the atoms is given by
+a sum over all pairs of atoms:
+\begin{eqnarray}
+U_{\rm LJ} &=& \sum_{i=1}^n\sum_{j=(i+1)}^n U_{\rm LJ}
+(\boldsymbol{r}_i, \boldsymbol{r}_j)
+\end{eqnarray}
+where the inter-atomic potential energy is given by:
+
+\begin{eqnarray}
+U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)
+&=& 4\epsilon
+\left[
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^12 -
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^6
+\right].
+\end{eqnarray}
+We adopted the Lennard Jones units by setting $\epsilon=1$ and $\sigma=1$.
+
+In terms of the Lennard Jones parameters $\epsilon$ and $\sigma$, the
+``polymer'' potential is
+\begin{eqnarray}
+U_{\rm polymer} &=&
+\sum_{i=1}^{n-1} \phi^{(1)}_{i,i+1} + \sum_{i=2}^{n-1} \phi^{(2)}_{i-1, i, i+1}
+\end{eqnarray}
+where
+
+\begin{eqnarray}
+\phi^{(1)}_{i,i+1} &=& \frac{k}{2}\left(|\boldsymbol{r}_i - \boldsymbol{r}_{i+1}|- 2^{1/6}\sigma\right)^2,\\
+\phi^{(2)}_{i-1, i, i+1} &=& \frac{k}{2}
+\left((\boldsymbol{r}_i - \boldsymbol{r}_{i-1})\cdot(\boldsymbol{r}_{i-1} - \boldsymbol{r}_{i}) - 1\right)^2,
+\end{eqnarray}
+and $k=\frac{36 \times 2^{2/3}\epsilon}{\sigma^2}$ has been chosen to match
+the curvature of $U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)$.
+
+\section{Example 3: ``MaxEnt'' image deconvolution example}
+
+Problems with more than one objective function can also arise in data
+analysis. Consider, for example, the problem of deblurring a noisy
+image. A common approach to these problems is regularized inversion,
+such as the ``maximum entropy'' technique of \citet{gull}. It is important
+to distinguish between this method and the maximum entropy principle used
+to update or assign probabilities \citep{caticha}.
+
+The unknown parameters are a set of pixel intensities
+$\{x_i\}_{i=1}^n$ where $n$ is the number of pixels and $x_i \geq 0$.
+The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
+The prior for the dataset given the parameters is a normal distribution
+with mean given by the underlying image $\{xi\}$ convolved by
+a point spread function. The standard deviation of each pixel is
+$\sigma$, assumed known. This is usually written as
+
+\begin{eqnarray}
+\boldsymbol{D} = \boldsymbol{M}\boldsymbol{x} + \boldsymbol{n}
+\end{eqnarray}
+where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{M}$ is
+the blurring operator written in matrix form.
+
+The prior for the pixel intensities $\{x_i\}$ has an ``entropic'' form,
+where images are upweighted (relative to a uniform prior) if the pixel
+intensities have a low dynamic range. The prior density is defined conditional
+on a hyperparameter $\lambda$:
+\begin{eqnarray}
+p(\boldsymbol{x} | \lambda) &=&
+\frac{\exp\left[\lambda S(\xx)\right]}{\int \exp\left[\lambda S(\xx)\right] \, d\xx}
+\label{eq:entropy_prior}
+\end{eqnarray}
+where
+\begin{eqnarray}
+S(\xx) &=& -\sum_{i=1}^n x_i \ln x_i
+\end{eqnarray}
+is the ``configurational entropy'' of the image (crucially, this is a function of
+an image, and not a function of a probability distribution).
+The denominator in Equation~\ref{eq:entropy_prior} ensures the conditional prior
+is normalized.
+
+In the 1980s, this prior was thought to have a fundamental status, but this
+is no longer the case \citep{massinf}, although the function $S(\xx)$ does
+have special properties when its argument is a measure \citep{knuth_skilling}.
+However, it is still a prior whose
+consequences we might be interested in.
+
+Instead, we can consider the configurational
+entropy $S(\xx)$ as simply a function of an image that may
+be relevant somehow, and that we are uncertain about. The joint posterior
+for $\xx$ and $\lambda$ is:
+\begin{eqnarray}
+p(\lambda, \xx | \data) &=&
+\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+{p(\data)}\\
+&=&
+\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+{p(\data)}
+\end{eqnarray}
+
+The posterior for the underlying image given the data is
+\begin{eqnarray}
+p(\boldsymbol{x} | \boldsymbol{D}, \lambda)
+&=& \frac{p(\boldsymbol{x} | \lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda)}
+{\int p(\boldsymbol{x}|\lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda) \,d^n\boldsymbol{m}}\\
+&=& \frac{\exp\left[-\lambda \sum_i x_i\ln x_i
+-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]}
+{\int \exp\left[-\lambda \sum_i x_i\ln x_i
+-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]\, d^n\boldsymbol{m}}
+\end{eqnarray}
+
+This is a `doubly intractable' problem \citep{murray}, since an integral, whose
+result is a function of the parameters, appears in the {\em denominator} of the
+target density. However, in our case the integral in the
+denominator arises from the prior for the parameters, rather than from the
+likelihood function.
+
 %The introduction should briefly place the study in a broad context and highlight why it is important.

### 2018-06-04 python/twinpeaks2018/example_truth.py
set up the fonts

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
-from twinpeaks2018.utils import logsumexp
+from twinpeaks2018.utils import *
+
+plot_settings()
 
 def compute_truth(limits, n=51, plot=False):
     T0_min, T0_max, T1_min, T1_max = limits

### 2018-06-04 python/twinpeaks2018/example_truth.py
removed plot

@@ -4,7 +4,7 @@ from twinpeaks2018.utils import *
 
 plot_settings()
 
-def compute_truth(limits, n=51, plot=False):
+def compute_truth(limits, n=51):
     T0_min, T0_max, T1_min, T1_max = limits
 
     # Set up grids
@@ -35,25 +35,6 @@ def compute_truth(limits, n=51, plot=False):
 
             print(".", end="", flush=True)
     print("")
-
-    if plot:
-        # Plot the results
-        limits = [0.1, 100.0, 0.1, 100.0]
-        result = compute_truth(limits)
-
-        plt.figure(figsize=(8, 6))
-        plt.subplot(1, 2, 1)
-        plt.imshow(result["ln_Z"], origin="lower", extent=np.log10(limits))
-        plt.xlabel("log10(T_0)")
-        plt.ylabel("log10(T_1)")
-        plt.title("ln_Z")
-
-        plt.subplot(1, 2, 2)
-        plt.imshow(result["H"], origin="lower", extent=np.log10(limits))
-        plt.xlabel("log10(T_0)")
-        plt.ylabel("log10(T_1)")
-        plt.title("H")
-        plt.show()
 
     return {"ln_Z": ln_Z, "H": H}
 

### 2018-06-04 doc/figures.py
Figures for the paper

@@ -1,0 +1,24 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import twinpeaks2018 as tp
+
+# Compute the true partition function
+limits = [1E-3, 1E3, 1E-3, 1E3]
+truth = tp.example_truth.compute_truth(limits=limits, n=101)
+
+# Plot the results
+plt.figure(1, figsize=(9, 6))
+plt.subplot(1, 2, 1)
+plt.imshow(truth["ln_Z"], origin="lower", extent=np.log10(limits))
+plt.xlabel("$\\log_{10}(T_1)$")
+plt.ylabel("$\\log_{10}(T_2)$")
+plt.title("$\\ln(Z)$")
+
+plt.subplot(1, 2, 2)
+plt.imshow(truth["H"], origin="lower", extent=np.log10(limits))
+plt.xlabel("$\\log_{10}(T_1)$")
+plt.title("$H$")
+
+plt.savefig("figures/demo_truth.pdf")
+print("Saved figures/demo_truth.pdf")
+

### 2018-06-04 doc/figures.py
example_truth -> demo_truth

@@ -4,7 +4,7 @@ import twinpeaks2018 as tp
 
 # Compute the true partition function
 limits = [1E-3, 1E3, 1E-3, 1E3]
-truth = tp.example_truth.compute_truth(limits=limits, n=101)
+truth = tp.demo_truth.compute_truth(limits=limits, n=101)
 
 # Plot the results
 plt.figure(1, figsize=(9, 6))

### 2018-06-04 python/twinpeaks2018/two_scalars.py

@@ -7,7 +7,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.random as rng
 import pandas as pd
-from twinpeaks2018.example_truth import *
+from twinpeaks2018.demo_truth import *
 from twinpeaks2018.utils import *
 
 plot_settings()

### 2018-06-04 examples/Atoms.cpp
Bugfix to header

@@ -113,19 +113,19 @@ std::string Atoms::description()
     for(size_t i=0; i<num_atoms; ++i)
     {
         s.str("");
-        s << "x[" << i << "],";
+        s << "x[" << i << "]";
         parts.emplace_back(s.str());
     }
     for(size_t i=0; i<num_atoms; ++i)
     {
         s.str("");
-        s << "y[" << i << "],";
+        s << "y[" << i << "]";
         parts.emplace_back(s.str());
     }
     for(size_t i=0; i<num_atoms; ++i)
     {
         s.str("");
-        s << "z[" << i << "],";
+        s << "z[" << i << "]";
         parts.emplace_back(s.str());
     }
 

### 2018-06-04 python/twinpeaks2018/__init__.py
display_atoms

@@ -1,5 +1,7 @@
 name = "twinpeaks2018"
 
+from .demo_truth import *
+from .display_atoms import *
 from .one_scalar import *
 from .two_scalars import *
 from .utils import *

### 2018-06-04 python/twinpeaks2018/display_atoms.py

@@ -1,0 +1,32 @@
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import numpy as np
+import numpy.random as rng
+import pandas as pd
+import os
+
+def display_atoms(num=100):
+
+    # Remove old figures
+    os.system("rm output/atoms*.png")
+
+    # Load the particles
+    particles = pd.read_csv("output/particles.csv")
+    particle_xs = np.array(particles.iloc[:, 0:30])
+    particle_ys = np.array(particles.iloc[:, 30:60])
+    particle_zs = np.array(particles.iloc[:, 60:90])
+
+    # Set up 3D axes
+    fig = plt.figure(figsize=(8, 8))
+    for i in range(num):
+        k = rng.randint(particles.shape[0])
+
+        plt.clf()
+        ax = fig.add_subplot(111, projection="3d")
+        ax.scatter(particle_xs[k, :], particle_ys[k, :], particle_zs[k, :])
+        ax.set_xlim([0.0, 100.0])
+        ax.set_ylim([0.0, 100.0])
+        ax.set_zlim([0.0, 100.0])
+        plt.savefig("output/atoms" + "%0.6d"%(i+1) + ".png")
+        print("Saved " + "output/atoms" + "%0.6d"%(i+1) + ".png")
+

### 2018-06-05 doc/ms.tex
Figures for the paper
SMC reference
New refs and writing

@@
 Hence, there is a strong
-connection between NS and ideas from rare event simulation.
-\citet{walter2017point} has explicitly explored this connection.
+connection between NS and ideas from rare event simulation
+(\citet{walter2017point} has explicitly explored this connection).
 Another way of thinking about this
@@
 the logarithm is the natural logarithm) implies, loosely speaking,
-that the posterior occupies a fraction $e^{-100}$ of the prior mass.
+that the posterior is to be found in a tiny region of the space that
+has a prior probability of only $e^{-100}$.
 $H$ can be interpreted quite literally as a measure of how much
@@
 of $\xx$, precisely?'' \citep{knuth_questions, van2017inquiry}.
-\citet{brewer2017computing} introduced a variant of NS that computes
+\citet{brewer2017computing} introduced a version of NS that computes
 Shannon entropies, including entropies of marginal distributions (whereas
@@
 There are many different methods based on this idea, such as the popular
-parallel tempering method \citep{pt, gregory}.
+parallel tempering \citep{hansmann1997parallel, gregory2005bayesian},
+simulated tempering \citep{marinari1992simulated},
+annealed importance sampling \citep{neal2001annealed}, and
+steppingstone sampling \citep{xie2010improving}.
 However, unlike annealing methods, NS requires only a small number of
@@
 $-E(\xx)$ as `objective functions',
-by analogy with the terminology used when
-discussing optimization methods. Although we are interested in sampling rather
+by analogy with the terminology used in optimization.
+Although we are interested in sampling rather
 than optimization, we still want to increase the values of $L$ or decrease
-the values of $E$ relative to what is typical of the prior.
+the values of $E$ relative to what is typical of the prior --- just in
+a controlled manner, so we can quantify prior mass as we ascend.
 
@@
 constant and by running standard Nested Sampling with objective function
-$L(\xx) = L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}$. However, usually we
+$L(\xx) = L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}$. However, what if we
 are interested in a range of values for $\beta_1$ and $\beta_2$, and we
-want to know the entire partition function $Z(\beta_1, \beta_2)$.
+want to know the entire partition function $Z(\beta_1, \beta_2)$?
 This work describes
 progress towards solving this class of problems while maintaining the benefits
-of Nested Sampling, such as the ability to cope with first-order phase
+of Nested Sampling, such as the ability to cope with phase
 transitions. The algorithm is presented here for problems with two objective
@@
 
-\
-
+\section{Algorithm requirements}
 The prior $\pi(\xx)$ implies a certain prior for $L_1$ and $L_2$, which we
-denote $\pi(L_1, L_2)$. An example of a prior is shown as the
+denote $\pi(L_1, L_2)$, overloading the $\pi$ symbol.
+An example of a prior is shown as the
 probability density in Figure~\ref{fig:joint1}. The partition function
 $Z(\beta_1, \beta_2)$ is a set of expected values with respect to this density.
-Simple Monte Carlo sampling from $\pi$ will not work except for values of
-$(\beta_1, \beta_2)$ where the canonical distribution remains similar to $\pi$.
-We need a sampler that explores regions where $L_1$ and $L_2$ are high in order
-to accurately estimate $Z(\beta_1, \beta_2)$.
+By analogy with the standard case of one objective function,
+simple Monte Carlo sampling from $\pi$ will not work except for values of
+$(\beta_1, \beta_2)$ where the canonical distributions of interest are
+not too different from $\pi$.
+We need a sampler that explores regions where $L_1$ and $L_2$ are increased
+(relative to what's typical of $\pi$) in order
+to accurately estimate $Z(\beta_1, \beta_2)$. The specific way of increasing
+$L_1$ and $L_2$ should follow the requirements listed in the following
+subsection, which are unique to NS.
+
 %\begin{figure}[ht!]
@@
 
-\section{Unique Properties of Nested Sampling}
+\subsection{Unique Properties of Nested Sampling}
 What is special about the NS sequence of distributions?
+Intuitively, the fact they are chosen adaptively provides a practical advantage
+over annealing-based methods (and reduces the number of tuning parameters
+substantially --- no `annealing schedule' is needed). While adaptive methods
+for generating annealing schedules exist \citep{salomone2018unbiased}, these
+are of no use in some phase change problems where a single temperature implies
+a mixture of two or more phases.
 
 Consider the Nested Sampling measure, proportional to the amount of time
-NS spends in each region of the space. Since NS moves at a constant rate
+NS spends in each region of the space (see \citet{polson2014vertical}
+for further discussion of this concept, and a derivation of it from some
+desiderata).
+Since NS moves at a constant rate
 in terms of $\log(X)$, this measure is proportional to
@@
 single objective function. The same is true of variants such as
-Diffusive Nested Sampling \citep{dns, dnest4}.
+Diffusive Nested Sampling \citep{dns, dnest4} and PolyChord
+\citep{handley2015polychord}.
 
-Sequential Monte Carlo \citep{salomone2018unbiased}
+Sequential Monte Carlo \citep{doucet2001introduction, salomone2018unbiased}
 
@@
 
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=0.75]{figures/truth.pdf}
-%\caption{The true partition function and KL divergence (from the prior to
-%the canonical distribution) as a function of two temperatures for the
-%test problem.\label{fig:truth}}
-%\end{figure}
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.75]{figures/demo_truth.pdf}
+\caption{The true partition function and KL divergence (from the prior to
+the canonical distribution) as a function of two temperatures for the
+test problem.\label{fig:truth}}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+%\section{Results}
 
-This section may be divided by subheadings.
+%This section may be divided by subheadings.
 It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\begin{quote}
-This section may be divided by subheadings.
+%\begin{quote}
+%This section may be divided by subheadings.
 It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\end{quote}
+%\end{quote}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Subsection}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Subsection}
 
-\subsubsection{Subsubsection}
+%\subsubsection{Subsubsection}
 
-Bulleted lists look like this:
-\begin{itemize}[leftmargin=*,labelsep=5.8mm]
-\item	First bullet
-\item	Second bullet
-\item	Third bullet
-\end{itemize}
+%Bulleted lists look like this:
+%\begin{itemize}[leftmargin=*,labelsep=5.8mm]
+%\item	First bullet
+%\item	Second bullet
+%\item	Third bullet
+%\end{itemize}
 
-Numbered lists can be added as follows:
-\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
-\item	First item 
-\item	Second item
-\item	Third item
-\end{enumerate}
+%Numbered lists can be added as follows:
+%\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
+%\item	First item 
+%\item	Second item
+%\item	Third item
+%\end{enumerate}
 
-The text continues here.
+%The text continues here.
 
-\subsection{Figures, Tables and Schemes}
+%\subsection{Figures, Tables and Schemes}
 
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
+%All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=2 cm]{Definitions/logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=2 cm]{Definitions/logo-mdpi}
+%\caption{This is a figure, Schemes follow the same formatting.
 If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
@@
 A caption on a single line should be centered.}
-\end{figure}
+%\end{figure}
 
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-entry 1		& data			& data\\
-entry 2		& data			& data\\
-\bottomrule
-\end{tabular}
-\end{table}
+%\begin{table}[H]
+%\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
+%\centering
+%%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
+%\begin{tabular}{ccc}
+%\toprule
+%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+%\midrule
+%entry 1		& data			& data\\
+%entry 2		& data			& data\\
+%\bottomrule
+%\end{tabular}
+%\end{table}
 
-\subsection{Formatting of Mathematical Components}
+%\subsection{Formatting of Mathematical Components}
 
-This is an example of an equation:
+%This is an example of an equation:
 
-\begin{equation}
-a + b = c
-\end{equation}
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+%\begin{equation}
+%a + b = c
+%\end{equation}
+%%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
 This ensures correct linenumbering.
@@
 
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%%% Example of a theorem:
+%\begin{Theorem}
+%Example text of a theorem.
+%\end{Theorem}
 
-The text continues here. Proofs must be formatted as follows:
+%The text continues here. Proofs must be formatted as follows:
 
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+%%% Example of a proof:
+%\begin{proof}[Proof of Theorem 1]
+%Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
+%\end{proof}
+%The text continues here.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Discussion}
 
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
+%Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
 The findings and their implications should be discussed in the broadest context possible.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Materials and Methods}
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+%Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
 Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
@@
 
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
 If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
@@
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+%Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Conclusions}
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Patents}
+%This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 

### 2018-06-05 doc/ms.tex
Memorylessness omg

@@
 \subsection{Unique Properties of Nested Sampling}
-What is special about the NS sequence of distributions?
-Intuitively, the fact they are chosen adaptively provides a practical advantage
+What is special about the NS sequence of distributions (the constrained priors)?
+Intuitively, the fact they are chosen adaptively (i.e., the likelihood values
+observed
+at one iteration determine the likelihood threshold for the next constrained
+distribution)
+provides a practical advantage
 over annealing-based methods (and reduces the number of tuning parameters
@@
 
-Consider the Nested Sampling measure, proportional to the amount of time
+Another feature of NS is that its output can be used to reconstruct
+any constrained prior. Consider the Nested Sampling measure, proportional
+to the amount of time
 NS spends in each region of the space (see \citet{polson2014vertical}
@@
 \end{align}
-The sequence of dead particles emitted by NS is then used to compute properties
-of the posterior distribution, or other canonical distributions for temperatures
-other than 1. Why does this work? Why does the NS measure of
-Equation~\ref{eqn:ns_measure} allow the user to get a reasonable number of
-samples for {\em any} canonical distribution?
+and is improper if we imagine an NS run that does not terminate.
+Consider using $m_{NS}$ as an importance sampling-type distribution to
+estimate properties of a constrained prior
+$p(\xx ; \ell) = \pi(\xx)\mathds{1}(L(\xx) > \ell)/X(\ell)$.
+How useful $m_{\rm NS}$ is for determining properties of $p(\xx ; \ell)$
+may be indicated by the KL-divergence from the former to the latter:
+\begin{align}
+D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
+    &= \int p(\xx ; \ell)
+                \log \left(\frac{p(\xx ; \ell)}{m_{\rm NS}(\xx)}\right)
+                \, d\xx \\
+    &= \textnormal{const} + \int_{L(\xx) > \ell} \frac{\pi(\xx)}{X(\ell)}
+                \log \left(\frac{X(L(\xx))}{X(\ell)}\right) \, d\xx
+\end{align}
+Rewriting the integral to be with respect to $X$, and taking advantage of the
+fact that the implied prior for $X$ is uniform (since $X$ is the complementary
+CDF of the likelihood values under $\pi$) gives:
+\begin{align}
+D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
+    &= \textnormal{const} + \int_0^{X(\ell)} \frac{1}{X(\ell)}
+                \log \left(\frac{1}{X(\ell)}\right) \, dX
+\end{align}
 
-We seek an algorithm for computing the partition function
-$Z(\beta_1, \beta_2)$ for a range of values of the $\beta$s, from a single
-run. To be a variant of Nested Sampling, the algorithm should satisfy
-the following properties:
+Remarkably, this does not depend on $\ell$. This means that every constrained
+prior, no matter the value of its threshold $\ell$, is equally `distant'
+from $m_{\rm NS}$. This can be seen intuitively using a standard
+$\log L$-$\log X$ plot from NS. On these plots, the prior is a reflected
+exponential distribution with scale 1, and the likelihood constraints
+merely truncate the exponential distribution (by the memorylessness property
+of the exponential, truncation is equivalent to shifting). The NS measure
+is uniform in terms of $\log(X)$, so we have essentially shown that the KL
+divergence from a wide uniform measure to a narrow shifted
+exponential (of unit width) contained within it does not depend on the
+position of the exponential.
+
+Unfortunately, this property breaks down with more than
+one objective function, and (as far as we know) the algorithm given in this
+paper does not satisfy an analogous property.
+
+\subsection{Desiderata}
+While we could not see how to satisfy the property in the above subsection,
+the algorithm of this paper does satisfy the following other NS properties:
 \begin{enumerate}
-\item It should begin with $N$ points drawn from the prior $\pi(\xx)$.
-\item It should seek to explore regions where the values of
+\item It begins with $N$ points drawn from the prior $\pi(\xx)$.
+\item It seeks to explore regions where the values of
 $L_1(\xx)$ and $L_2(\xx)$ are higher than the prior $\pi(L_1, L_2)$
 would typically imply.
-\item The algorithm should consider a sequence of probability
+\item It considers a sequence of probability
 distributions proportional to $\pi$, but restricted to smaller and smaller
@@
 known factor at each iteration.
-\item The algorithm should be invariant to monotonic transformations of
+\item It is invariant to monotonic transformations of
 $L_1$ and $L_2$, i.e. it should only depend on rankings of $L_1$ and $L_2$

### 2018-06-05 doc/ms.tex
Fixed derivation

@@
 \begin{align}
-m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.\label{eqn:measure}
+m_{\rm NS} &\propto \frac{\pi(\xx)}{X(L(\xx))}.\label{eqn:measure}
 \end{align}
@@
 \end{align}
-Rewriting the integral to be with respect to $X$, and taking advantage of the
-fact that the implied prior for $X$ is uniform (since $X$ is the complementary
-CDF of the likelihood values under $\pi$) gives:
+Rewriting the integral to be with respect to $X$,
+and taking advantage of the
+fact the implied prior for $X$ is uniform (since $X$ is the complementary
+CDF of the likelihood values under $\pi$), gives:
 \begin{align}
 D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
-    &= \textnormal{const} + \int_0^{X(\ell)} \frac{1}{X(\ell)}
-                \log \left(\frac{1}{X(\ell)}\right) \, dX
+    &= \textnormal{const} + \frac{1}{X(\ell)}\int_0^{X(\ell)} 
+                \log \left(\frac{X}{X(\ell)}\right) \, dX\\
+    &= \textnormal{const} + \frac{1}{X(\ell)}\left(
+                    X(\ell)\log \left(\frac{X(\ell)}{X(\ell)}\right) - X(\ell)\right)\\
+    &= \textnormal{const} -1 = \textnormal{const}'.
 \end{align}

### 2018-06-12 src/Config.cpp
Put rng_seed.out in output/

@@ -33,7 +33,7 @@ void Config::load(const char* filename)
         rng_seed = file["rng_seed"].as<unsigned int>();
 
     // Save the rng seed to a file
-    std::fstream fout("rng_seed.out", std::ios::out);
+    std::fstream fout("output/rng_seed.out", std::ios::out);
     fout << rng_seed;
     fout.close();
 

### 2018-06-12 python/twinpeaks2018/__init__.py
display_potts()

@@ -2,6 +2,7 @@ name = "twinpeaks2018"
 
 from .demo_truth import *
 from .display_atoms import *
+from .display_potts import *
 from .one_scalar import *
 from .two_scalars import *
 from .utils import *

### 2018-06-12 python/twinpeaks2018/display_potts.py

@@ -1,0 +1,24 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import numpy.random as rng
+import pandas as pd
+import os
+
+def display_potts(num=100):
+
+    # Remove old figures
+    os.system("rm output/potts*.png")
+
+    # Load the particles
+    particles = pd.read_csv("output/particles.csv")
+    n = int(np.sqrt(particles.shape[1]))
+
+    for i in range(num):
+        k = rng.randint(particles.shape[0])
+
+        plt.clf()
+        img = np.array(particles.iloc[k, :]).reshape((n, n))
+        plt.imshow(img)
+        plt.savefig("output/potts" + "%0.6d"%(i+1) + ".png")
+        print("Saved " + "output/potts" + "%0.6d"%(i+1) + ".png")
+

### 2018-06-12 src/main.cpp

@@ -11,7 +11,7 @@ using namespace TwinPeaks2018;
 int main()
 {
     // Which example?
-    using Example = Demo;
+    using Example = Potts;
 
     // Load the configuration
     Config::global_config.load("config.yaml");

### 2018-06-12 src/main.cpp
Do Demo...

@@ -11,7 +11,7 @@ using namespace TwinPeaks2018;
 int main()
 {
     // Which example?
-    using Example = Potts;
+    using Example = Demo;
 
     // Load the configuration
     Config::global_config.load("config.yaml");

### 2018-06-12 python/twinpeaks2018/demo_truth.py
Smaller grid for truth calculation

@@ -10,7 +10,7 @@ def compute_truth(limits, n=51):
     # Set up grids
     ln_Z = np.empty((n, n))
     H = np.empty((n, n))
-    x = np.linspace(0.0, 1.0, 100001)
+    x = np.linspace(0.0, 1.0, 10001)
     dx = x[1] - x[0]
 
     # Temperature grids

### 2018-06-12 doc/figures.py
Changed temperature limits

@@ -3,8 +3,8 @@ import numpy as np
 import twinpeaks2018 as tp
 
 # Compute the true partition function
-limits = [1E-3, 1E3, 1E-3, 1E3]
-truth = tp.demo_truth.compute_truth(limits=limits, n=101)
+limits = [1E-1, 1E2, 1E-1, 1E2]
+truth = tp.demo_truth.compute_truth(limits=limits, n=51)
 
 # Plot the results
 plt.figure(1, figsize=(9, 6))
@@ -22,3 +22,5 @@ plt.title("$H$")
 plt.savefig("figures/demo_truth.pdf")
 print("Saved figures/demo_truth.pdf")
 
+#plt.figure(2)
+#x = np.linspace(0.0, 1.0, 

### 2018-06-12 doc/figures.py
New figures

@@ -2,6 +2,9 @@ import matplotlib.pyplot as plt
 import numpy as np
 import twinpeaks2018 as tp
 
+# Set up the fonts
+tp.plot_settings()
+
 # Compute the true partition function
 limits = [1E-1, 1E2, 1E-1, 1E2]
 truth = tp.demo_truth.compute_truth(limits=limits, n=51)
@@ -22,5 +25,24 @@ plt.title("$H$")
 plt.savefig("figures/demo_truth.pdf")
 print("Saved figures/demo_truth.pdf")
 
-#plt.figure(2)
-#x = np.linspace(0.0, 1.0, 
+x = np.linspace(0.0, 1.0, 1001)
+def s(x, T1, T2):
+    s = -((x - 0.5)/0.1)**2/T1 - np.sin(10.0*np.pi*x)**2/T2
+    return np.exp(s)
+
+plt.figure(2, figsize=(7, 6))
+S = s(x, 10.0, 10.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (1, 1)$")
+S = s(x, 10.0, 1.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (10, 1)$")
+S = s(x, 1.0, 10.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (1, 10)$")
+plt.xlabel("$x$", fontsize=20)
+plt.ylabel("$p(x; T_1, T_2)$", fontsize=20)
+plt.legend()
+plt.savefig("figures/demo_canonical.pdf")
+print("Saved figures/demo_canonical.pdf")
+

### 2018-06-13 doc/ms.tex
Include the new figures

@@
 relative importance of these effects determined by the values of the
-inverse temperatures $\beta_1$ and $\beta_2$.
+inverse temperatures $\beta_1$ and $\beta_2$. Three example canonical
+distributions are shown in Figure~\ref{fig:demo_canonical}.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.75]{figures/demo_canonical.pdf}
+\caption{Three canonical distributions for different values of the two
+temperatures $T_1$ and $T_2$. These are for the one-dimensional case, but
+in this example, the 100 dimensional canonical distributions are independent
+and have these distributions as their marginals.\label{fig:demo_canonical}}
+\end{figure}
 
@@
 divergence from the prior to the canonical distribution are shown in
-Figure~\ref{fig:truth} as a function of two temperatures.
+Figure~\ref{fig:demo_truth} as a function of two temperatures.
 
-\begin{figure}[ht!]
+\begin{figure}[!ht]
 \centering
@@
 the canonical distribution) as a function of two temperatures for the
-test problem.\label{fig:truth}}
+test problem.\label{fig:demo_truth}}
 \end{figure}

### 2018-06-15 doc/ms.tex
Bunch of work on the paper

@@
 distributions are shown in Figure~\ref{fig:demo_canonical}.
+The true partition function (computed numerically) and the Kullback-Leibler
+divergence from the prior to the canonical distribution are shown in
+Figure~\ref{fig:demo_truth} as a function of two temperatures. These show the
+common behaviour where lower temperatures correspond to lower values
+of the normalising constant $\log Z$ and higher values of the KL divergence
+$H$. There are no phase changes, which would result in discontinuities.
 
@@
 \centering
-\includegraphics[scale=0.75]{figures/demo_canonical.pdf}
+\includegraphics[scale=0.6]{figures/demo_canonical.pdf}
 \caption{Three canonical distributions for different values of the two
-temperatures $T_1$ and $T_2$. These are for the one-dimensional case, but
-in this example, the 100 dimensional canonical distributions are independent
-and have these distributions as their marginals.\label{fig:demo_canonical}}
+temperatures $T_1$ and $T_2$, in the simple demo problem.
+These are for the one-dimensional case, but
+in this example, the 100 dimensional canonical distributions are `independent
+and identically distributed' version of this distribution.
+Low values of $T_1$ bring
+more probability towards the centre of the domain, and low values of $T_2$
+bring out the oscillatory structure in the probability density function.
+\label{fig:demo_canonical}}
 \end{figure}
-
-The true partition function (computed numerically) and the Kullback-Leibler
-divergence from the prior to the canonical distribution are shown in
-Figure~\ref{fig:demo_truth} as a function of two temperatures.
 
@@
 \centering
-\includegraphics[scale=0.75]{figures/demo_truth.pdf}
+\includegraphics[scale=0.6]{figures/demo_truth.pdf}
 \caption{The true partition function and KL divergence (from the prior to
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y.
-and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing—Original Draft Preparation, X.X.; Writing—Review \& Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.'', please turn to the \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work reported.
-}
+\authorcontributions{BJB conceived the problem and worked on various ideas
+over the years that nearly worked. RJNB suggested and worked on the polymer
+example.
+EC discussed the problem and worked on
+several attempts at solutions with BJB over the years.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by [name of funder] grant number [xxx].'' Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{This research received no external funding.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g.
-materials used for experiments).}
+\acknowledgments{BJB acknowledges research and study leave funding from the
+University of Auckland. We would like to thank Gabor Csanyi, Livia B. Partay,
+Rob Salomone, John Skilling, etc etc.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}
+\conflictsofinterest{The authors declare no conflict of interest.}
 
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & linear dichroism
+MCMC & Markov Chain Monte Carlo \\
+NS & Nested Sampling \\
+SMC & Sequential Monte Carlo
 \end{tabular}}
@@
 %% optional
-\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections.
+\appendixtitles{yes} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendixsections{one} %Leave argument "multiple" if there are multiple sections.
 Then a counter is printed ("Appendix A").
@@
 \appendix
-\section{}
-\subsection{}
-The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
+\section{Using the TwinPeaks2018 software}
 
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+%\section{}
+%All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
 
@@
 %% optional
-\sampleavailability{Samples of the compounds ...... are available from the authors.}
+%\sampleavailability{Samples of the compounds ...... are available from the authors.}
 

### 2018-06-15 doc/ms.tex
More writing

@@
 \newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
+\newcommand{\todo}{\color{blue}{\bf TODO}:~}
 
@@
 $L_1$ and $L_2$ should follow the requirements listed in the following
-subsection, which are unique to NS.
+subsection, which are unique to NS. Another unique property of NS which our
+algorithm {\em does not} satisfy is discussed in Appendix~\ref{sec:property}.
 
@@
 
-\subsection{Unique Properties of Nested Sampling}
-What is special about the NS sequence of distributions (the constrained priors)?
-Intuitively, the fact they are chosen adaptively (i.e., the likelihood values
-observed
-at one iteration determine the likelihood threshold for the next constrained
-distribution)
-provides a practical advantage
-over annealing-based methods (and reduces the number of tuning parameters
-substantially --- no `annealing schedule' is needed). While adaptive methods
-for generating annealing schedules exist \citep{salomone2018unbiased}, these
-are of no use in some phase change problems where a single temperature implies
-a mixture of two or more phases.
-
-Another feature of NS is that its output can be used to reconstruct
-any constrained prior. Consider the Nested Sampling measure, proportional
-to the amount of time
-NS spends in each region of the space (see \citet{polson2014vertical}
-for further discussion of this concept, and a derivation of it from some
-desiderata).
-Since NS moves at a constant rate
-in terms of $\log(X)$, this measure is proportional to
-\begin{align}
-m_{\rm NS} &\propto \frac{\pi(\xx)}{X(L(\xx))}.\label{eqn:measure}
-\end{align}
-and is improper if we imagine an NS run that does not terminate.
-Consider using $m_{NS}$ as an importance sampling-type distribution to
-estimate properties of a constrained prior
-$p(\xx ; \ell) = \pi(\xx)\mathds{1}(L(\xx) > \ell)/X(\ell)$.
-How useful $m_{\rm NS}$ is for determining properties of $p(\xx ; \ell)$
-may be indicated by the KL-divergence from the former to the latter:
-\begin{align}
-D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
-    &= \int p(\xx ; \ell)
-                \log \left(\frac{p(\xx ; \ell)}{m_{\rm NS}(\xx)}\right)
-                \, d\xx \\
-    &= \textnormal{const} + \int_{L(\xx) > \ell} \frac{\pi(\xx)}{X(\ell)}
-                \log \left(\frac{X(L(\xx))}{X(\ell)}\right) \, d\xx
-\end{align}
-Rewriting the integral to be with respect to $X$,
-and taking advantage of the
-fact the implied prior for $X$ is uniform (since $X$ is the complementary
-CDF of the likelihood values under $\pi$), gives:
-\begin{align}
-D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
-    &= \textnormal{const} + \frac{1}{X(\ell)}\int_0^{X(\ell)} 
-                \log \left(\frac{X}{X(\ell)}\right) \, dX\\
-    &= \textnormal{const} + \frac{1}{X(\ell)}\left(
-                    X(\ell)\log \left(\frac{X(\ell)}{X(\ell)}\right) - X(\ell)\right)\\
-    &= \textnormal{const} -1 = \textnormal{const}'.
-\end{align}
-
-Remarkably, this does not depend on $\ell$. This means that every constrained
-prior, no matter the value of its threshold $\ell$, is equally `distant'
-from $m_{\rm NS}$. This can be seen intuitively using a standard
-$\log L$-$\log X$ plot from NS. On these plots, the prior is a reflected
-exponential distribution with scale 1, and the likelihood constraints
-merely truncate the exponential distribution (by the memorylessness property
-of the exponential, truncation is equivalent to shifting). The NS measure
-is uniform in terms of $\log(X)$, so we have essentially shown that the KL
-divergence from a wide uniform measure to a narrow shifted
-exponential (of unit width) contained within it does not depend on the
-position of the exponential.
-
-Unfortunately, this property breaks down with more than
-one objective function, and (as far as we know) the algorithm given in this
-paper does not satisfy an analogous property.
-
 \subsection{Desiderata}
-While we could not see how to satisfy the property in the above subsection,
+While we could not see how to satisfy the property in
+Appendix~\ref{sec:property},
 the algorithm of this paper does satisfy the following other NS properties:
@@
 known factor at each iteration.
-\item It is invariant to monotonic transformations of
+\item The exploration procedure is invariant under monotonic transformations of
 $L_1$ and $L_2$, i.e. it should only depend on rankings of $L_1$ and $L_2$
-values and not the values themselves.
+values and not on the numeric values themselves.
 \end{enumerate}
@@
 
-Sequential Monte Carlo \citep{doucet2001introduction, salomone2018unbiased}
+\subsection{The algorithm}
+The algorithm itself is rather simple. It consists of a collection of
+{\em reps} (short for repetitions) of Nested Sampling, each of which ascends
+a different compromise between $L_1$ and $L_2$. The output of the reps can then
+be used, with appropriate weights, to represent canonical distributions at
+any temperature.
+
+The combination of the reps makes use of the (approximate?) unbiasedness
+property of Nested Sampling when the prior weights of the dead particles are
+assigned proportional to
+$[(N-1)/N]^i$ at iteration $i$, instead of being based on
+Skilling's geometric sequence of $X$-values given by $\exp(-i/N)$.
+\citet{walter} demonstrated that the Nested Sampling estimator of $Z$
+is unbiased with these weights, but assuming perfect sampling of the replacement
+particles at each iteration. Additionally, using the framework of
+Sequential Monte Carlo \citep{doucet2001introduction},
+\citet{salomone2018unbiased} showed that this remains true even if imperfect
+MCMC is used to generate new particles. Technically, this property is
+lost if the sequence of distributions is chosen adaptively (a key feature of NS)
+rather than being fixed in advanced. However, this paper demonstrates that the
+algorithm works well in practice despite this limitation.
+
+The fact that $Z$ estimates can be made unbiased means that separate $Z$
+estimates can be averaged together and the properties of the averaged estimator
+will be easily understood and satisfactory ({\todo probably need to be more
+technical here.}). {\todo The following statement is based on intuition}
+Runs that ascend the `wrong' objective function are still unbiased
+estimates of $Z$ for the `right' objective function. Some of the reps will
+be well-positioned to represent some canonical distributions but inappropriate
+for others. When this happens, the particles from the rep will just have very
+low weights with respect to some canonical distributions.
+
+{\todo A description of the algorithm for a single rep follows}.
+A probability distribution over the objective functions is set up. If there
+are only two objective functions, there is just a probability $p_1$ for
+objective function 1, and $1-p_1$ for objective function 2.
+
+The first distribution is the prior $\pi(\xx)$. Objective function thresholds
+$(\ell_1, \ell_2)_0 = (-\inf, -\inf)$ are assigned.
+$N$ particles are generated
+from the prior. Then, an objective function is selected according to the
+probabilities $\{p_k\}$. Suppose the objective function chosen is number $k$.
+Then the worst particle wrt that criteron is written to disk and replaced,
+and the threshold is updated in the $k$th position only.
+
+Essentially, a `rep' is just Nested Sampling, but where a threshold is
+maintained for all objective functions. At each iteration, the space is
+restricted by only one of the objective functions.
+
+The probability distribution over the objective functions influences the
+proportion of the compressions that are done using each objective function.
+Different reps ought to have different values for the probability distribution.
+Some reps will mostly increase $L_1$, some will mostly increase $L_2$, and
+some will be in between.
 
@@
 \appendixtitles{yes} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixsections{one} %Leave argument "multiple" if there are multiple sections.
+\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections.
 Then a counter is printed ("Appendix A").
@@
 \appendix
+\section{A Unique Property of Nested Sampling}\label{sec:property}
+What is special about the NS sequence of distributions (the constrained priors)?
+Intuitively, the fact they are chosen adaptively (i.e., the likelihood values
+observed
+at one iteration determine the likelihood threshold for the next constrained
+distribution)
+provides a practical advantage
+over annealing-based methods (and reduces the number of tuning parameters
+substantially --- no `annealing schedule' is needed). While adaptive methods
+for generating annealing schedules exist \citep{salomone2018unbiased}, these
+are of no use in some phase change problems where a single temperature implies
+a mixture of two or more phases.
+
+Another feature of NS is that its output can be used to reconstruct
+any constrained prior. Consider the Nested Sampling measure, proportional
+to the amount of time
+NS spends in each region of the space (see \citet{polson2014vertical}
+for further discussion of this concept, and a derivation of it from some
+desiderata).
+Since NS moves at a constant rate
+in terms of $\log(X)$, this measure is proportional to
+\begin{align}
+m_{\rm NS} &\propto \frac{\pi(\xx)}{X(L(\xx))}.\label{eqn:measure}
+\end{align}
+and is improper if we imagine an NS run that does not terminate.
+Consider using $m_{NS}$ as an importance sampling-type distribution to
+estimate properties of a constrained prior
+$p(\xx ; \ell) = \pi(\xx)\mathds{1}(L(\xx) > \ell)/X(\ell)$.
+How useful $m_{\rm NS}$ is for determining properties of $p(\xx ; \ell)$
+may be indicated by the KL-divergence from the former to the latter:
+\begin{align}
+D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
+    &= \int p(\xx ; \ell)
+                \log \left(\frac{p(\xx ; \ell)}{m_{\rm NS}(\xx)}\right)
+                \, d\xx \\
+    &= \textnormal{const} + \int_{L(\xx) > \ell} \frac{\pi(\xx)}{X(\ell)}
+                \log \left(\frac{X(L(\xx))}{X(\ell)}\right) \, d\xx
+\end{align}
+Rewriting the integral to be with respect to $X$,
+and taking advantage of the
+fact the implied prior for $X$ is uniform (since $X$ is the complementary
+CDF of the likelihood values under $\pi$), gives:
+\begin{align}
+D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
+    &= \textnormal{const} + \frac{1}{X(\ell)}\int_0^{X(\ell)} 
+                \log \left(\frac{X}{X(\ell)}\right) \, dX\\
+    &= \textnormal{const} + \frac{1}{X(\ell)}\left(
+                    X(\ell)\log \left(\frac{X(\ell)}{X(\ell)}\right) - X(\ell)\right)\\
+    &= \textnormal{const} -1 = \textnormal{const}'.
+\end{align}
+
+Remarkably, this does not depend on $\ell$. This means that every constrained
+prior, no matter the value of its threshold $\ell$, is equally `distant'
+from $m_{\rm NS}$. This can be seen intuitively using a standard
+$\log L$-$\log X$ plot from NS. On these plots, the prior is a reflected
+exponential distribution with scale 1, and the likelihood constraints
+merely truncate the exponential distribution (by the memorylessness property
+of the exponential, truncation is equivalent to shifting). The NS measure
+is uniform in terms of $\log(X)$, so we have essentially shown that the KL
+divergence from a wide uniform measure to a narrow shifted
+exponential (of unit width) contained within it does not depend on the
+position of the exponential.
+
+Unfortunately, this property breaks down with more than
+one objective function, and (as far as we know) the algorithm given in this
+paper does not satisfy an analogous property.
+
 \section{Using the TwinPeaks2018 software}

### 2018-06-15 doc/ms.tex
Infinity
Fixed walter reference

@@
 Skilling's geometric sequence of $X$-values given by $\exp(-i/N)$.
-\citet{walter} demonstrated that the Nested Sampling estimator of $Z$
+\citet{walter2017point} demonstrated that the Nested Sampling estimator of $Z$
 is unbiased with these weights, but assuming perfect sampling of the replacement
@@
 The first distribution is the prior $\pi(\xx)$. Objective function thresholds
-$(\ell_1, \ell_2)_0 = (-\inf, -\inf)$ are assigned.
+$(\ell_1, \ell_2)_0 = (-\infty, -\infty)$ are assigned.
 $N$ particles are generated
@@
 maintained for all objective functions. At each iteration, the space is
-restricted by only one of the objective functions.
+restricted by the value of only one of the objective functions.
 

### 2018-06-16 doc/ms.tex
A bit of writing on a Saturday afternoon

@@
 algorithm works well in practice despite this limitation.
+{\todo Verify/prove statement about bias, and that it means I can average
+reps the way I'm doing it. Also check this remains the case with the random
+thinning that I'm using.}
 
@@
 {\todo A description of the algorithm for a single rep follows}.
-A probability distribution over the objective functions is set up. If there
+For each rep, we set up a probability distribution over the objective functions,
+given by probabilities $\boldsymbol{p} = \{p_1, ..., p_n\}$,
+where $n$ is the number of
+objective functions. If there
 are only two objective functions, there is just a probability $p_1$ for
-objective function 1, and $1-p_1$ for objective function 2.
+objective function 1, and $p_2 = 1-p_1$ for objective function 2.
 
@@
 from the prior. Then, an objective function is selected according to the
-probabilities $\{p_k\}$. Suppose the objective function chosen is number $k$.
+probability distribution $\boldsymbol{p}$.
+Suppose the objective function chosen is number $k$.
 Then the worst particle wrt that criteron is written to disk and replaced,
@@
 
-The probability distribution over the objective functions influences the
+The probability distribution $\boldsymbol{p}$ influences the
 proportion of the compressions that are done using each objective function.
@@
 Some reps will mostly increase $L_1$, some will mostly increase $L_2$, and
-some will be in between.
+some will be in between. In the reference implementation
+(Appendix~\ref{sec:software}), the log-probabilities are chosen from a $t$
+distribution with 2 degrees of freedom, exponentiated, and then normalized.
 
@@
 The second objective function, given by
-\begin{eqnarray} 
-E_2(\xx) &=& \sin^2(10 \pi x_i),
+\begin{eqnarr \sum_{i=1}^{100}\sin^2(10 \pi x_i),
 \end{eqnarray}
@@
 are close to 0, 0.1, 0.2, ..., 0.9 and 1.
+Since both of the objective functions are simple sums over the coordinates,
+the canonical distributions are products of independent distributions for
+each coordinate.
+
 The canonical distributions for this system should draw the coordinates
@@
 
-\section{Using the TwinPeaks2018 software}
+\section{Using the TwinPeaks2018 software}\label{sec:software}
 

### 2018-06-16 doc/ms.tex
A few edits

@@
 The second objective function, given by
-\begin{eqnarr \sum_{i=1}^{100}\sin^2(10 \pi x_i),
+\begin{eqnarray}
+E_2(\xx) &=& \sum_{i=1}^{100}\sin^2(10 \pi x_i),
 \end{eqnarray}
@@
 
-\section{Example 3: ``MaxEnt'' image deconvolution example}
-
-Problems with more than one objective function can also arise in data
-analysis. Consider, for example, the problem of deblurring a noisy
-image. A common approach to these problems is regularized inversion,
-such as the ``maximum entropy'' technique of \citet{gull}. It is important
-to distinguish between this method and the maximum entropy principle used
-to update or assign probabilities \citep{caticha}.
-
-The unknown parameters are a set of pixel intensities
-$\{x_i\}_{i=1}^n$ where $n$ is the number of pixels and $x_i \geq 0$.
-The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
-The prior for the dataset given the parameters is a normal distribution
-with mean given by the underlying image $\{xi\}$ convolved by
-a point spread function. The standard deviation of each pixel is
-$\sigma$, assumed known. This is usually written as
-
-\begin{eqnarray}
-\boldsymbol{D} = \boldsymbol{M}\boldsymbol{x} + \boldsymbol{n}
-\end{eqnarray}
-where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{M}$ is
-the blurring operator written in matrix form.
-
-The prior for the pixel intensities $\{x_i\}$ has an ``entropic'' form,
-where images are upweighted (relative to a uniform prior) if the pixel
-intensities have a low dynamic range. The prior density is defined conditional
-on a hyperparameter $\lambda$:
-\begin{eqnarray}
-p(\boldsymbol{x} | \lambda) &=&
-\frac{\exp\left[\lambda S(\xx)\right]}{\int \exp\left[\lambda S(\xx)\right] \, d\xx}
-\label{eq:entropy_prior}
-\end{eqnarray}
-where
-\begin{eqnarray}
-S(\xx) &=& -\sum_{i=1}^n x_i \ln x_i
-\end{eqnarray}
-is the ``configurational entropy'' of the image (crucially, this is a function of
-an image, and not a function of a probability distribution).
-The denominator in Equation~\ref{eq:entropy_prior} ensures the conditional prior
-is normalized.
-
-In the 1980s, this prior was thought to have a fundamental status, but this
-is no longer the case \citep{massinf}, although the function $S(\xx)$ does
-have special properties when its argument is a measure \citep{knuth_skilling}.
-However, it is still a prior whose
-consequences we might be interested in.
-
-Instead, we can consider the configurational
-entropy $S(\xx)$ as simply a function of an image that may
-be relevant somehow, and that we are uncertain about. The joint posterior
-for $\xx$ and $\lambda$ is:
-\begin{eqnarray}
-p(\lambda, \xx | \data) &=&
-\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
-{p(\data)}\\
-&=&
-\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
-{p(\data)}
-\end{eqnarray}
-
-The posterior for the underlying image given the data is
-\begin{eqnarray}
-p(\boldsymbol{x} | \boldsymbol{D}, \lambda)
-&=& \frac{p(\boldsymbol{x} | \lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda)}
-{\int p(\boldsymbol{x}|\lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda) \,d^n\boldsymbol{m}}\\
-&=& \frac{\exp\left[-\lambda \sum_i x_i\ln x_i
--\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]}
-{\int \exp\left[-\lambda \sum_i x_i\ln x_i
--\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]\, d^n\boldsymbol{m}}
-\end{eqnarray}
-
-This is a `doubly intractable' problem \citep{murray}, since an integral, whose
-result is a function of the parameters, appears in the {\em denominator} of the
-target density. However, in our case the integral in the
-denominator arises from the prior for the parameters, rather than from the
-likelihood function.
+%\section{Example 3: ``MaxEnt'' image deconvolution example}
+
+%Problems with more than one objective function can also arise in data
+%analysis. Consider, for example, the problem of deblurring a noisy
+%image. A common approach to these problems is regularized inversion,
+%such as the ``maximum entropy'' technique of \citet{gull}. It is important
+%to distinguish between this method and the maximum entropy principle used
+%to update or assign probabilities \citep{caticha}.
+
+%The unknown parameters are a set of pixel intensities
+%$\{x_i\}_{i=1}^n$ where $n$ is the number of pixels and $x_i \geq 0$.
+%The dataset is also a collection of pixel intensities $\{D_i\}_{i=1}^n$.
+%The prior for the dataset given the parameters is a normal distribution
+%with mean given by the underlying image $\{xi\}$ convolved by
+%a point spread function. The standard deviation of each pixel is
+%$\sigma$, assumed known. This is usually written as
+
+%\begin{eqnarray}
+%\boldsymbol{D} = \boldsymbol{M}\boldsymbol{x} + \boldsymbol{n}
+%\end{eqnarray}
+%where $\boldsymbol{n}$ is the noise in each pixel and $\boldsymbol{M}$ is
+%the blurring operator written in matrix form.
+
+%The prior for the pixel intensities $\{x_i\}$ has an ``entropic'' form,
+%where images are upweighted (relative to a uniform prior) if the pixel
+%intensities have a low dynamic range. The prior density is defined conditional
+%on a hyperparameter $\lambda$:
+%\begin{eqnarray}
+%p(\boldsymbol{x} | \lambda) &=&
+%\frac{\exp\left[\lambda S(\xx)\right]}{\int \exp\left[\lambda S(\xx)\right] \, d\xx}
+%\label{eq:entropy_prior}
+%\end{eqnarray}
+%where
+%\begin{eqnarray}
+%S(\xx) &=& -\sum_{i=1}^n x_i \ln x_i
+%\end{eqnarray}
+%is the ``configurational entropy'' of the image (crucially, this is a function of
+%an image, and not a function of a probability distribution).
+%The denominator in Equation~\ref{eq:entropy_prior} ensures the conditional prior
+%is normalized.
+
+%In the 1980s, this prior was thought to have a fundamental status, but this
+%is no longer the case \citep{massinf}, although the function $S(\xx)$ does
+%have special properties when its argument is a measure \citep{knuth_skilling}.
+%However, it is still a prior whose
+%consequences we might be interested in.
+
+%Instead, we can consider the configurational
+%entropy $S(\xx)$ as simply a function of an image that may
+%be relevant somehow, and that we are uncertain about. The joint posterior
+%for $\xx$ and $\lambda$ is:
+%\begin{eqnarray}
+%p(\lambda, \xx | \data) &=&
+%\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+%{p(\data)}\\
+%&=&
+%\frac{p(\lambda)p(\xx | \lambda)p(\data | \xx)}
+%{p(\data)}
+%\end{eqnarray}
+
+%The posterior for the underlying image given the data is
+%\begin{eqnarray}
+%p(\boldsymbol{x} | \boldsymbol{D}, \lambda)
+%&=& \frac{p(\boldsymbol{x} | \lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda)}
+%{\int p(\boldsymbol{x}|\lambda)p(\boldsymbol{D}|\boldsymbol{x}, \lambda) \,d^n\boldsymbol{m}}\\
+%&=& \frac{\exp\left[-\lambda \sum_i x_i\ln x_i
+%-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]}
+%{\int \exp\left[-\lambda \sum_i x_i\ln x_i
+%-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}x_{j}\right)^2\right]\, d^n\boldsymbol{m}}
+%\end{eqnarray}
+
+%This is a `doubly intractable' problem \citep{murray}, since an integral, whose
+%result is a function of the parameters, appears in the {\em denominator} of the
+%target density. However, in our case the integral in the
+%denominator arises from the prior for the parameters, rather than from the
+%likelihood function.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
+\section{Conclusions}
 
@@
 \acknowledgments{BJB acknowledges research and study leave funding from the
-University of Auckland. We would like to thank Gabor Csanyi, Livia B. Partay,
+University of Auckland. We would like to thank Gábor Csányi,
+Livia Bartók-Pártay,
 Rob Salomone, John Skilling, etc etc.}

### 2018-06-16 doc/ms.tex
Todo: decide 3rd example

@@
 that is intermediate between a Lennard-Jones form and a `polymer' form; and
-(iii) A Bayesian image reconstruction example where the prior for the image
-is defined conditionally on a hyperparameter, but where this prior contains
-an intractable normalizing constant.
+(iii) {\todo decide between a few options: image reconstruction with an
+intractable normalizing constant in the prior, or perhaps the `Potts' example
+which is a compromize between a 2D potts model and a product of many 1D
+Potts models.
+%(iii) A Bayesian image reconstruction example where the prior for the image
+%is defined conditionally on a hyperparameter, but where this prior contains
+%an intractable normalizing constant.
 A free software implementation in C++ and Python is available at

### 2018-06-16 doc/ms.tex
Brace

@@
 which is a compromize between a 2D potts model and a product of many 1D
-Potts models.
+Potts models.}
 %(iii) A Bayesian image reconstruction example where the prior for the image

### 2018-06-16 doc/ms.tex
Results figures for demo problem

@@
 test problem.\label{fig:demo_truth}}
+\end{figure}
+
+The algorithm was run for 1000 reps, to a `depth' of 500 nats,
+with 100 particles and 1000 MCMC steps per NS iteration per rep.
+Results are given in
+Figures~\ref{fig:demo_logZ_H},~\ref{fig:demo_residuals},
+and~\ref{fig:demo_N_eff}.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_logZ_H.pdf}
+\caption{The partition function $\ln(Z)$ and information $H$ as a function
+of the two temperatures, reconstructed using the algorithm. Compare with
+Figure~\ref{fig:demo_truth}.
+\label{fig:demo_logZ_H}}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_residuals.pdf}
+\caption{The residuals, i.e., the difference between
+Figures~\ref{fig:demo_logZ_H} and~\ref{fig:demo_truth}.
+\label{fig:demo_residuals}}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_N_eff.pdf}
+\caption{The error in $\ln(Z)$, expressed in terms of an
+`effective number of particles' in a standard NS run that would lead to
+the same error at 1 sigma. No values are below $N_{\rm eff} = 1$.
+\label{fig:demo_N_eff}}
 \end{figure}

### 2018-06-17 doc/ms.tex
Notational discussion

@@
 particles) or configuration space (the set of possible positions of a collection
-of particles). In this context we usually want to
+of particles).
+
+In this context we usually want to
 compute $Z(\beta)$ as a function of $\beta$, which is called the
@@
 
+\subsection{Notation for Objective Functions}
 Throughout this paper we will refer to $L(\xx)$ or
@@
 a controlled manner, so we can quantify prior mass as we ascend.
+
+Throughout this paper and the software, there are three
+conventions used to define the objective functions. $L()$ is named by analogy
+with likelihood, and appears multiplicatively as in
+Equation~\ref{eqn:power_posterior}. $E() = -\ln L()$ is named by analogy with
+`energy'. Finally, in the software,
+$S() = \ln L() = -E()$ is often used (the $S$ stands for a
+`{\em S}calar function of $\xx$'). The algorithm ascends $L$ and $S$, but
+descends $E$.
 

### 2018-06-17 python/twinpeaks2018/one_scalar.py
markersize=3

@@ -30,13 +30,13 @@ def postprocess_one_scalar(temperature=1.0):
 
     plt.figure(figsize=(9, 7))
     plt.subplot(2, 1, 1)
-    plt.plot(ln_w, ln_l, ".", markersize=1, alpha=0.3)
+    plt.plot(ln_w, ln_l, ".", markersize=3, alpha=0.3)
     ln_l_sorted = np.sort(ln_l)
     plt.ylim([ln_l_sorted[int(0.05*len(ln_l_sorted))], ln_l_sorted[-1]])
     plt.ylabel("$\\ln(L)$")
 
     plt.subplot(2,1,2)
-    plt.plot(ln_w, W/W.max(), ".", markersize=1, alpha=0.5)
+    plt.plot(ln_w, W/W.max(), ".", markersize=3, alpha=0.5)
     plt.xlabel("$\\ln(w)$")
     plt.ylabel("$W/W_{\\rm max}$")
     plt.savefig("output/likelihood_curve.png", dpi=600)

### 2018-06-17 python/twinpeaks2018/two_scalars.py

@@ -32,7 +32,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     plt.figure()
     plt.plot(particles_info[names[0]][indices],
              particles_info[names[1]][indices],
-             ".", alpha=0.2, markersize=1)
+             ".", alpha=0.2, markersize=2)
     plt.xlabel("$S_{i}$".format(i=scalars[0]))
     plt.ylabel("$S_{j}$".format(j=scalars[1]))
     x = np.sort(particles_info[names[0]][indices])
@@ -80,13 +80,13 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot_and_save=False):
 
         plt.figure(figsize=(9, 7))
         plt.subplot(2, 1, 1)
-        plt.plot(ln_w, ln_s, ".", markersize=1, alpha=0.5)
+        plt.plot(ln_w, ln_s, ".", markersize=3, alpha=0.5)
         ln_s_sorted = np.sort(ln_s)
         plt.ylim([ln_s_sorted[int(0.05*len(ln_s_sorted))], ln_s_sorted[-1]])
         plt.ylabel("$\\ln(L)$")
 
         plt.subplot(2,1,2)
-        plt.plot(ln_w, W/W.max(), ".", markersize=1, alpha=0.5)
+        plt.plot(ln_w, W/W.max(), ".", markersize=3, alpha=0.5)
         plt.xlabel("$\\ln(w)$")
         plt.ylabel("$W/W_{\\rm max}$")
         plt.savefig("output/likelihood_curve.png", dpi=600)

### 2018-06-17 include/Version.h
Version file

@@ -1,0 +1,9 @@
+#ifndef TwinPeaks2018_Version_h
+#define TwinPeaks2018_Version_h
+
+#define TWINPEAKS2018_MAJOR_VERSION 0
+#define TWINPEAKS2018_MINOR_VERSION 2
+#define TWINPEAKS2018_PATCH_VERSION 1
+
+#endif
+

### 2018-06-17 python/setup.py
Version

@@ -2,7 +2,7 @@ import setuptools
 
 setuptools.setup(
     name="twinpeaks2018",
-    version="0.0.1",
+    version="0.1.0",
     author="Brendon J. Brewer",
     author_email="brendon.brewer@gmail.com",
     description="The Python package accompanying TwinPeaks2018",

### 2018-06-19 python/twinpeaks2018/two_scalars.py
Compute effective number of runs

@@ -23,7 +23,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     if particles_info.shape[0] > 30000:
         thin = particles_info.shape[0] // 30000
 
-    # Use random thinning to avoid putting artifacts into the plot
+    # Use random thinning to avoid putting aliasing artifacts into the plot
     indices = rng.randint(particles_info.shape[0], size=30000)
 
     names = ["scalars[{i}]".format(i=scalars[0]),
@@ -72,10 +72,21 @@ def get_canonical(particles_info, temperatures=[1.0, 1.0], plot_and_save=False):
     result["H"] = H
     result["ESS"] = np.exp(-np.sum(W*ln_W))
 
+    # Calculate effective number of reps
+    ln_W_rep = np.empty(len(rep_ids))
+    k = 0
+    for rep_id in rep_ids:
+        subset = ln_W[particles_info["rep_id"] == rep_id]
+        ln_W_rep[k] = logsumexp(subset)
+        k += 1
+    W_rep = np.exp(ln_W_rep)
+    result["ENR"] = np.exp(-np.sum(W_rep*ln_W_rep))
+
     if plot_and_save:
         print("ln(Z) = {ln_Z}".format(ln_Z=ln_Z))
         print("H = {H} nats".format(H=H))
         print("Effective sample size = {ESS}".format(ESS=result["ESS"]))
+        print("Effective number of reps = {ENR}".format(ENR=result["ENR"]))
         np.savetxt("output/canonical_weights.txt", W)
 
         plt.figure(figsize=(9, 7))

### 2018-06-19 python/twinpeaks2018/two_scalars.py
Plot ENR

@@ -118,6 +118,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     H = np.empty((n, n))
     S0 = np.empty((n, n))
     S1 = np.empty((n, n))
+    ENR = np.empty((n, n))
 
     print("Computing temperature grid. It takes a while (one dot=one pixel)",
           end="", flush=True)
@@ -138,6 +139,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
             # Retrieve normalisation constant and KL divergence
             ln_Z[i, j] = results["ln_Z"]
             H[i, j] = results["H"]
+            ENR[i, j] = results["ENR"]
 
             # Compute expectations
             W = np.exp(results["ln_W"])
@@ -161,6 +163,12 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
 
     plt.savefig("output/ln_Z_H.png", dpi=600)
     print("Saved output/ln_Z_h.png")
+
+    plt.figure(2)
+    plt.imshow(ENR, origin="lower", extent=np.log10(limits))
+    plt.xlabel("$\\log_{10}(T_0)$")
+    plt.ylabel("$\\log_{10}(T_1)$")
+    plt.title("Effective number of contributing reps")
     plt.show()
 
     if residuals:
@@ -198,7 +206,7 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
         plt.imshow(np.log10(Neff), origin="lower", extent=np.log10(limits))
         plt.xlabel("$\\log_{10}(T_0)$")
         plt.ylabel("$\\log_{10}(T_1)$")
-        plt.title("$\\log_{10} N_{\\rm eff}$ based on $\\ln(Z)$ Residuals")
+        plt.title("$\\log_{10}(N_{\\rm eff})$ based on $\\ln(Z)$ Residuals")
 
 #        plt.subplot(1, 2, 2)
 #        resid = H - truth["H"]

### 2018-06-19 python/twinpeaks2018/two_scalars.py
Save ENR plot

@@ -169,6 +169,8 @@ def evaluate_temperature_grid(particles_info, limits, n=51, residuals=False):
     plt.xlabel("$\\log_{10}(T_0)$")
     plt.ylabel("$\\log_{10}(T_1)$")
     plt.title("Effective number of contributing reps")
+    plt.savefig("output/ENR.png", dpi=600)
+    print("Saved output/ENR.png")
     plt.show()
 
     if residuals:

### 2018-06-19 python/twinpeaks2018/two_scalars.py
markersize=3

@@ -32,7 +32,7 @@ def plot_particle_scalars(particles_info, scalars=[0, 1]):
     plt.figure()
     plt.plot(particles_info[names[0]][indices],
              particles_info[names[1]][indices],
-             ".", alpha=0.2, markersize=2)
+             ".", alpha=0.2, markersize=3)
     plt.xlabel("$S_{i}$".format(i=scalars[0]))
     plt.ylabel("$S_{j}$".format(j=scalars[1]))
     x = np.sort(particles_info[names[0]][indices])

### 2018-06-20 python/twinpeaks2018/display_potts.py
Use uint8

@@ -10,7 +10,7 @@ def display_potts(num=100):
     os.system("rm output/potts*.png")
 
     # Load the particles
-    particles = pd.read_csv("output/particles.csv")
+    particles = pd.read_csv("output/particles.csv", dtype="uint8")
     n = int(np.sqrt(particles.shape[1]))
 
     for i in range(num):

### 2018-06-20 examples/Potts.h
32 x 32 potts model

@@ -15,7 +15,7 @@ class Potts
 
 	private:
 		static constexpr size_t num_colors = 5;
-        static constexpr size_t n = 50;
+        static constexpr size_t n = 32;
 
         // State
 		std::vector<std::vector<int>> x;

### 2018-06-20 doc/ms.tex
algorithm

@@
 
+\usepackage{algorithm2e}
 \usepackage{dsfont}
+\usepackage{setspace}
 
@@
 distribution with 2 degrees of freedom, exponentiated, and then normalized.
+
+\begin{algorithm}[!ht]
+    \setstretch{1.35}
+    Set $N$, the number of particles \\
+    Set $M$, the number of reps \\
+    Set $d$, the target depth in nats \\
+    Compute $J = Nd$, the number of NS iterations per rep \\
+    \For{i in 1:$M$}{
+      Set initial threshold $(\ell_1^*, \ell_2^*) = (0, 0)$ \\
+      Generate initial particles $(\xx_1, ..., \xx_N)$ from prior $\pi$ \\
+      Generate a `direction' (probability distribution over objective functions) $\boldsymbol{p}$ \\
+      \For{j in 1:$J$}{
+          Choose an objective function $k$ according to $\boldsymbol{p}$ \\
+          Find $c = \textnormal{argmin}(\lambda C \to L_k(\xx_C))$, the index of the worst particle \\
+          Write out $\xx_c$ to disk as $\xx_{ij}$ with prior weight $w_{ij}$ proportional to $(1 - 1/N)^j$ \\
+          Replace threshold element $\ell_c^*$ with $L_k(\xx_C)$ \\
+          Replace particle $c$ with new particle generated from
+            $\pi\times\mathds{1}(L_1 > \ell_1^*, L_2 > \ell_2^*)$          
+      }
+    }
+
+    Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
+    Compute $\hat{Z}(T_1, T_2) \leftarrow \sum_{ij} w_{ij}\left(L_1(\xx_{ij})/T_1 + L_2(\xx_{ij})/T_2\right) / \sum_{ij} w_{ij}$\\
+  \vspace*{0.5em}
+  \caption{The `Switch Sampling' algorithm.}
+\end{algorithm}
 

### 2018-06-20 doc/ms.tex
Minor fix

@@
           Write out $\xx_c$ to disk as $\xx_{ij}$ with prior weight $w_{ij}$ proportional to $(1 - 1/N)^j$ \\
-          Replace threshold element $\ell_c^*$ with $L_k(\xx_C)$ \\
+          Replace threshold element $\ell_c^*$ with $L_k(\xx_c)$ \\
           Replace particle $c$ with new particle generated from

### 2018-06-20 doc/ms.tex
Fixes

@@
     Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
-    Compute $\hat{Z}(T_1, T_2) \leftarrow \sum_{ij} w_{ij}\left(L_1(\xx_{ij})/T_1 + L_2(\xx_{ij})/T_2\right) / \sum_{ij} w_{ij}$\\
+    Compute $\hat{Z}(T_1, T_2) \leftarrow \left(\sum_{ij} w_{ij}L_1(\xx_{ij})^{1/T_1}L_2(\xx_{ij})^{1/T_2}\right) / \sum_{ij} w_{ij}$\\
   \vspace*{0.5em}
